---
title: "Cluster Definitions"
author: "Stefan Boeing"
date: 'Compiled: `r format(Sys.Date(), "%B %d, %Y")`'

output: 
    html_document:
        code_folding: hide
        df_print: tibble
        highlight: default
        theme: paper
        toc: true
        toc_depth: 5
        toc_float: true
        css:

always_allow_html: yes

---


```{r setup, include=FALSE}
knitr::opts_chunk$set(
    tidy = TRUE,
    tidy.opts = list(width.cutoff = 120),
    message = FALSE,
    warning = FALSE
)
```

```{bash init, eval=F, echo=T}
## R version for this analysis 
# module purge;source /camp/stp/babs/working/software/modulepath_new_software_tree_2018-08-13;module load pandoc/2.2.3.2-foss-2016b;ml R/4.0.3-foss-2020a

```

## Prepare Data



```{r, eval=TRUE, echo=F, results=F}

## libraries ##
#library(tidyverse)

#library(scales)

VersionPdfExt <- paste0(".V", gsub("-", "", Sys.Date()), ".pdf")

if (dir.exists("/Volumes/babs/working/boeings/")){
    hpc.mount <- "/Volumes/babs/working/boeings/"
} else if (dir.exists("Y:/working/boeings/")){
    hpc.mount <- "Y:/working/boeings/"
} else if (dir.exists("/camp/stp/babs/working/boeings/")){
    hpc.mount <- "/camp/stp/babs/working/boeings/"
} else {
    hpc.mount <- ""
}

## Loading the BABS password ##
#if (upload.results.to.database){
    FN <- paste0(hpc.mount, "Projects/reference_data/pwd_folder/babs.txt")
    dbTable <- read.delim(
      FN,
      header = F,
      sep = "\t",
      stringsAsFactors = F
    )
#}
db.pwd <- as.vector(dbTable[1,1])

###############################################################################
##                                                                           ##
# if (!requireNamespace("remotes")){
#     install.packages("remotes")
# }



if (file.exists("renv.lock")){
    renv::restore(prompt = FALSE)
} else {
    renv::init()
}

# remotes::install_github("rstudio/renv")
# renv::install("rstudio/renv")
## Done                                                                      ##
###############################################################################

#install.packages("remotes")
# renv::install("decusInLabore/biologicSeqTools2")
# renv::install("decusInLabore/biologicToolsSC")
# renv::install("decusinlabore/biologicViewerSC")

library(Seurat)
library(tidyverse)
library(biologicSeqTools2)
library(biologicToolsSC)


# source("assets/R/scTools.r")
# source("assets/R/SBwebtools.pckg.r")

ObioFN <- paste0("../", list.files("..")[grep(".bioLOGIC.Robj", list.files(".."))])

if (file.exists(ObioFN)){
    load(paste0(ObioFN))
    print(paste0("Obio object ", Obio@parameterList$localWorkDir, ObioFN, " exists and is loaded."))
} else {
    exit()
}

## Reset paths to local environment
Obio <- Obio %>% 
    biologicSeqTools2::setMountingPoint()  %>% 
    biologicSeqTools2::setAnalysisPaths() %>% 
    biologicSeqTools2::setCrickGenomeAndGeneNameTable() %>% 
    biologicSeqTools2::createAnalysisFolders() %>% 
    biologicSeqTools2::setDataBaseParameters()




## Load Seurat object
SeuratFN <- paste0(Obio@parameterList$localWorkDir,list.files(Obio@parameterList$localWorkDir)[grep(".Seurat.Robj", list.files(Obio@parameterList$localWorkDir))])


if (file.exists(SeuratFN)){
    load(SeuratFN)
    print(paste0("Obio object ", Obio@parameterList$localWorkDir,SeuratFN, " exists and is loaded."))
    
} else {
    exit()
}

figureCount <- 1

## Rename Seurat object
OsC_CF <- OsC


```


## Do Dimensionality Reduction 
```{r, echo=TRUE, eval=TRUE, warning=FALSE, results=FALSE} 
###############################################################################
## Perform integrated analysis                                               ##

if (length(Obio@sampleDetailList) > 1){
    DefaultAssay(OsC_CF) <- "integrated"
} else {
    Obio@parameterList$singleCellClusterString <- gsub("integrated", "RNA", Obio@parameterList$singleCellClusterString)
    DefaultAssay(OsC_CF) <- "RNA"
}

OsC_CF <- FindVariableFeatures(
    object = OsC_CF,
    selection.method = 'vst', 
    nfeatures = Obio@parameterList$NtopGenes
)
# Run the standard workflow for visualization and clustering
## This will scale on the most variable features only
OsC_CF <- ScaleData(OsC_CF, verbose = FALSE)


redVec <- names(OsC_CF@reductions)


if (!("pca" %in% redVec )){
    OsC_CF <- RunPCA(
        OsC_CF, 
        npcs = Obio@parameterList$singleCellSeuratNpcs4PCA, verbose = FALSE
    )
}
# t-SNE and Clustering

## Add PCA clusters to data collection ##

if (!("umap" %in% redVec )){
    OsC_CF <- RunUMAP(OsC_CF, reduction = "pca", dims = 1:Obio@parameterList$singleCellSeuratNpcs4PCA)
}

# if (!("tsne" %in% redVec )){
# OsC_CF <- RunTSNE(OsC_CF, reduction = "pca", dims = 1:Obio@parameterList$singleCellSeuratNpcs4PCA)
# }


OsC_CF <- FindNeighbors(OsC_CF, reduction = "pca", dims = 1:Obio@parameterList$singleCellSeuratNpcs4PCA)
```


```{r, echo=TRUE, eval=TRUE, warning=FALSE, results=FALSE} 
OsC_CF2 <- OsC_CF

clusterOptionVec <- c(0.2,0.3,0.4, 0.5,0.7,0.9, 1,1,1.3,1.5, 1.7,1.9, 2.1,2.3,2.5)



# Find clusters using a range of resolutions
OsC_CF2 <- Seurat::FindClusters(object = OsC_CF2, resolution = clusterOptionVec)


## Make plot 


tag <- "Clustertree"

plotList <- list()
chnkVec <- as.vector(NULL, mode = "character")

## Calling the package is essental for the clustree function to work. 
library(clustree)

plotList[[tag]] <- clustree::clustree(
    OsC_CF2, 
    edge_width = 0.5,
    node_label_size  = 1.5,
    node_size_range  = c(1, 8)) + 
  ggplot2::theme_bw()  +  
  ggplot2::theme(
    axis.text.y   = ggplot2::element_blank(),
    axis.text.x   = ggplot2::element_blank(),
    axis.title.y  = ggplot2::element_blank(),
    axis.title.x  = ggplot2::element_blank(),
    axis.ticks.x= ggplot2::element_blank(),
    axis.ticks.y= ggplot2::element_blank(),
    axis.line = ggplot2::element_line(colour = "black"),
    panel.border = ggplot2::element_rect(colour = "black", fill=NA, size=1),
    plot.title = ggplot2::element_text(hjust = 0.5, size = 12),
    legend.title = ggplot2::element_blank()
)

## Save to file ##
FNbase <- paste0("clusterplot.", tag,".", VersionPdfExt)
FN <- paste0(Obio@parameterList$reportFigDir, FNbase)
FNrel <- paste0("report_figures/", FNbase)

pdf(FN)
    print(plotList[[tag]])
dev.off()

figLegend <- paste0(
    "**Figure ", 
    figureCount, 
    ":** ",
    "Cells per cluster at various cluster resolutions. Download a pdf of this figure [here](", FNrel,")."
)

figureCount <- figureCount + 1

NewChnk <- paste0(
    "### ",tag,
    "\n```{r D_",tag,", results='asis', echo=F, eval=TRUE, warning=FALSE, fig.cap='",
    figLegend,"'}\n",
    "\n",
    "\n print(plotList[['",tag,"']])",
    "\n cat(  '\n')",
    "\n\n\n```\n"   
)

chnkVec <- c(
    chnkVec,
    NewChnk
)



rm(OsC_CF2)

if (length(plotList) > 3){
    tabVar <- ".tabset .tabset-fade .tabset-dropdown"
} else {
    tabVar <- ".tabset .tabset-fade .tabset-pills"
}

```


## Clustertree{`r tabVar`}

```{r, echo=TRUE, eval=TRUE, warning=FALSE, results="asis"} 

cat(paste(knitr::knit(text = chnkVec, quiet = T), collapse = '\n'))

```


```{r populate_expr_database_1, eval=TRUE, echo=F, results=F}
if (length(Obio@sampleDetailList) > 1){
    DefaultAssay(OsC_CF) <- "integrated"
    tagString <- "integrated"
} else {
    Obio@parameterList$singleCellClusterString <- gsub("integrated", "RNA", pattern = Obio@parameterList$singleCellClusterString)
    DefaultAssay(OsC_CF) <- "RNA"
    tagString <- "RNA"
}




plotList <- list()
chnkVec <- as.vector(NULL, mode = "character")
# reductionVec <- c("umap", "tsne")
reductionVec <- c("umap")
j =1

for (i in 1:length(clusterOptionVec)){
    OsC_CF <- FindClusters(OsC_CF, resolution = clusterOptionVec[i])
    names(OsC_CF@meta.data) <- gsub("\\.", "_", names(OsC_CF@meta.data))
## Rational: Run PCA on variable features, then scale data for heatmaps and other applications
    allGenes <- rownames(x = OsC_CF@assays$RNA)
    OsC_CF <- ScaleData(OsC_CF, verbose = FALSE, features=allGenes)
    
    tag <- paste0("Clusterplot_all", "_",i,"_",gsub("[.]", "_", clusterOptionVec[i]))
    
    # Temporarily switched off 
    plotList[[tag]] <- DimPlot(OsC_CF, reduction = reductionVec[j], group.by = "seurat_clusters",label = TRUE)
    
    
    ## Save to file ##
    FNbase <- paste0("clusterplot.", tag,".", VersionPdfExt)
    FN <- paste0(Obio@parameterList$reportFigDir, FNbase)
    FNrel <- paste0("report_figures/", FNbase)
    
    pdf(FN)
        print(plotList[[tag]])
    dev.off()
    
    figLegend <- paste0(
        "**Figure ", 
        figureCount, 
        "A:** ",
        reductionVec[j],
        " Clusterplot with parameter ",clusterOptionVec[i]," [here](", FNrel,")."
    )
    
    
    NewChnk <- paste0(
        "### ",tag,
        "\n```{r D_",tag,", results='asis', echo=F, eval=TRUE, warning=FALSE, fig.cap='",
        figLegend,"'}\n",
        "\n",
        "\n print(plotList[['",tag,"']])",
        "\n cat(  '\n')",
        "\n\n\n```\n"   
    )
    
    chnkVec <- c(
        chnkVec,
        NewChnk
    )
    
    ## with split by sample ##
    # tag <- paste0("Clusterplot_by_sample",  "_",i,"_", gsub("[.]", "_", clusterOptionVec[i]))
    # 
    # plotList[[tag]] <- DimPlot(OsC_CF, reduction = reductionVec[j], group.by = gsub("\\.", "_", paste0(tagString , "_snn_res.", clusterOptionVec[i])),label = TRUE, split.by = "sampleID")
    # 
    # 
    # ## Save to file ##
    # FNbase <- paste0(tag,".", VersionPdfExt)
    # FN <- paste0(Obio@parameterList$reportFigDir, FNbase)
    # FNrel <- paste0("report_figures/", FNbase)
    # 
    # pdf(FN)
    #     print(plotList[[tag]])
    # dev.off()
    # 
    # figLegend <- paste0(
    #     "**Figure ", 
    #     figureCount, 
    #     "B:** ",
    #     reductionVec[j],
    #     " Clusterplot with parameter ",clusterOptionVec[j]," [here](", FNrel,")."
    # )
    # 
    # 
    # NewChnk <- paste0(
    #     "\n```{r Dimplot_by_sample_",tag,", results='asis', echo=F, eval=TRUE, warning=FALSE, fig.cap='",
    #     figLegend,"'}\n",
    #     "\n",
    #     "\n print(plotList[['",tag,"']])",
    #     "\n cat(  '\n')",
    #     "\n\n\n```\n"   
    # )
    # 
    # chnkVec <- c(
    #     chnkVec,
    #     NewChnk
    # )
    # 
    ## Add cluster dendrogram ##
    
    
  #   tag <- paste0("Cluster_dendrogram" , "_",i,"_",gsub("[.]", "_", clusterOptionVec[i]))
  #   
  #   Idents(OsC_CF) <- "seurat_clusters"
  #   OsC_CF <- BuildClusterTree(OsC_CF)
  #   OsC_CF@tools$BuildClusterTree$tip.label <- OsC_CF@tools$BuildClusterTree$tip.label
  #   
  #   library(ggtree)
  #   plotList[[tag]]  <- ggplot(OsC_CF@tools$BuildClusterTree) + geom_tree() + theme_tree() + labs(title=tag
  #   ) +  theme(
  #     panel.border = element_rect(colour = "black", fill=NA, size=1),
  #     axis.title.x=element_blank(),
  #     plot.title = element_text(hjust = 0.5, size = 12)
  #   ) 
  #   ## Color by cluster ##
  #   plotList[[tag]] <- plotList[[tag]] + geom_tiplab()   
  #   
  # ## Done ##
  #   
  #   
  #   
  #   #+ xlim(-1,1.2*max(OsC_CF@tools$BuildClusterTree$edge)) 
  #   
  #   
  #   ## Save to file ##
  #   FNbase <- paste0("clusterdendro.", tag,".", VersionPdfExt)
  #   FN <- paste0(Obio@parameterList$reportFigDir, FNbase)
  #   FNrel <- paste0("report_figures/", FNbase)
  #   
  #   pdf(FN)
  #       print(plotList[[tag]])
  #   dev.off()
  #   
  #   figLegend <- paste0(
  #       "**Figure ", 
  #       figureCount, 
  #       "A:** ",
  #       reductionVec[j],
  #       " Clusterplot dendrogram with parameter ",clusterOptionVec[i]," [here](", FNrel,")."
  #   )
  #   
  #   
  #   NewChnk <- paste0(
  #       "### ",tag,
  #       "\n```{r Clusterdendro_",tag,", results='asis', echo=F, eval=TRUE, warning=FALSE, fig.cap='",
  #       figLegend,"'}\n",
  #       "\n",
  #       "\n print(plotList[['",tag,"']])",
  #       "\n cat(  '\n')",
  #       "\n\n\n```\n"   
  #   )
  #   
  #   chnkVec <- c(
  #       chnkVec,
  #       NewChnk
  #   )
    
    
    figureCount <- figureCount + 1
    
}

## Save cluster patterns for featureView ##
dfMeta <- OsC_CF@meta.data

selVec <- c(
    "cellID",
    names(dfMeta)[grep("_res_", names(dfMeta))]
)

dfMeta <- dfMeta[,selVec]

selVec2 <- c(
    names(dfMeta)[grep("_res_", names(dfMeta))]
)

for (i in 1:length(selVec2)){
    dfMeta[,selVec2[i]] <- paste0("C", dfMeta[,selVec2[i]] )
}


names(dfMeta) <- gsub(paste0(tagString, "_snn_res_"), "ClusterTestRes_",names(dfMeta))
names(dfMeta) <- gsub(paste0(tagString, "_rnn_res_"), "ClusterTestRes_",names(dfMeta))

tempDir <- paste0(Obio@parameterList$localWorkDir,"temp")
            if(!dir.exists(tempDir)){
                dir.create(tempDir)
            }

FN <- paste0(Obio@parameterList$localWorkDir, "temp/ClusterFinder.output.txt")
write.table(
    dfMeta,
    FN,
    row.names = F, 
    sep = "\t"
)

if (length(plotList) > 3){
    tabVar <- ".tabset .tabset-fade .tabset-dropdown"
} else {
    tabVar <- ".tabset .tabset-fade .tabset-pills"
}

```




```{r Plot_tsne_data_plotting, echo=TRUE, eval=TRUE, warning=FALSE, results="asis"} 
# Temporarily not used
# cat(paste(knit(text = chnkVec, quiet = T), collapse = '\n'))

```




## Documentation
```{r documentation, eval=TRUE, echo=T, results=T}

sessionInfo()
```
