---
title: "Label Transfer"
author: "Stefan Boeing"
date: 'Compiled: `r format(Sys.Date(), "%B %d, %Y")`'

output: 
    html_document:
        code_folding: hide
        df_print: tibble
        toc: true
        toc_depth: 3
        toc_float: true
        css:
    
always_allow_html: yes

---
    
    
```{r setup, include=FALSE}
knitr::opts_chunk$set(
    tidy = TRUE,
    tidy.opts = list(width.cutoff = 120),
    message = FALSE,
    warning = FALSE
)
```


## Part B Database


```{r hpc_notes, include=FALSE}

# Make sure that variable Features are set in OsC

# module purge;source /camp/stp/babs/working/software/modulepath_new_software_tree_2018-08-13;module load pandoc/2.2.3.2-foss-2016b;ml R/3.6.0-foss-2016b-BABS;R;

## Get interactive session ##
#  srun --time=08:00:00 --mem=40G -p int --pty bash

# module purge;source /camp/stp/babs/working/software/modulepath_new_software_tree_2018-08-13;module load pandoc/2.2.3.2-foss-2016b;ml R/3.6.0-foss-2016b-BABS;R;

# sbatch --time=12:00:00 --wrap "module purge;source /camp/stp/babs/working/software/modulepath_new_software_tree_2018-08-13;module load pandoc/2.2.3.2-foss-2016b;ml R/3.6.0-foss-2016b-BABS;Rscript runD.r" --job-name="rD" -p hmem --mem=300G -o rD.slurm >> commands.txt

# --mem-per-cpu=14G -p hmem --pty bash

```


```{r populate_meta_data_database, eval=TRUE, echo=F, results=F}
## libraries ##
library(tidyverse)
library(Seurat)

VersionPdfExt <- paste0(".V", gsub("-", "", Sys.Date()), ".pdf")

if (dir.exists("/Volumes/babs/working/boeings/")){
    hpc.mount <- "/Volumes/babs/working/boeings/"
} else if (dir.exists("Y:/working/boeings/")){
    hpc.mount <- "Y:/working/boeings/"
} else if (dir.exists("/camp/stp/babs/working/boeings/")){
    hpc.mount <- "/camp/stp/babs/working/boeings/"
} else {
    hpc.mount <- ""
}

#Create the environment and load a suitable version of R, e.g. so:
FN <- paste0(hpc.mount, "Projects/reference_data/documentation/BC.parameters.txt")
dbTable <- read.delim(
    FN, 
    sep = "\t",
    stringsAsFactors = F
)

db.pwd <- as.vector(dbTable[1,1])






# source(
#     paste0(
#         hpc.mount,
#         "Stefan/protocol_files/github/boeings/packages/packageSourceCode/SBwebtools.pckg.r"
#     )
# )

# source(
#     paste0(
#         hpc.mount,
#         "Stefan/protocol_files/github/boeings/packages/scTools/scTools.r"
#     )
# )

source("assets/R/scTools.r")
source("assets/R/SBwebtools.pckg.r")


if (length(.libPaths()) > 2){
    .libPaths(.libPaths()[2:3])
}

ObioFN <- paste0("../", list.files("..")[grep(".bioLOGIC.Robj", list.files(".."))])

if (file.exists(ObioFN)){
    load(paste0(ObioFN))
    print(paste0("Obio object ", Obio@parameterList$localWorkDir, ObioFN, " exists and is loaded."))
} else {
    exit()
}

## Reset paths to local environment


Obio <- setMountingPoint(Obio)
Obio <- setAnalysisPaths(Obio)
Obio <- setCrickGenomeAndGeneNameTable(Obio)
Obio <- createAnalysisFolders(
    Obio
)
Obio <- setDataBaseParameters(Obio)

## Load Seurat object
## Goal: create a table, that can be added via the 'gene' column to the main 
## database table

ObioFN <- paste0("../", list.files("..")[grep(".Seurat.Robj", list.files(".."))])

load(ObioFN)

```



```{r populate_expr_database, eval=TRUE, echo=F, results=F}
###############################################################################
## Otional add extra data set                                                ##

#Create transfer list
transfer.list <- SplitObject(
    OsC, 
    split.by = "meta_DataSource"
)

# for (i in 1:length(transfer.list)) {
#     transfer.list[[i]] <- NormalizeData(transfer.list[[i]], verbose = FALSE)
#     transfer.list[[i]] <- FindVariableFeatures(transfer.list[[i]], selection.method = "vst", 
#         nfeatures = 2000, verbose = FALSE)
# }

# Query = destination
transfer.query <- transfer.list[["Tepe_et_al"]]



    # pcaproject: Project the PCA from the reference onto the query. We recommend using PCA when reference and query datasets are from scRNA-seq
    # 
    # lsiproject: Project the LSI from the reference onto the query. We recommend using LSI when reference and query datasets are from scATAC-seq. This requires that LSI has been computed for the reference dataset, and the same features (eg, peaks or genome bins) are present in both the reference and query. See RunTFIDF and RunSVD
    # 
    # rpca: Project the PCA from the reference onto the query, and the PCA from the query onto the reference (reciprocal PCA projection).
    # 
    # cca: Run a CCA on the reference and query



transfer.anchors <- Seurat::FindTransferAnchors(
    reference = transfer.list[["Zeppilli_et_al"]], 
    query = transfer.query, 
    reduction = "cca",
    dims = 1:Obio@parameterList$singleCellSeuratNpcs4PCA
)

#transfer.anchors <- Obio@dataTableList$referenceList[["sampleAnchors"]]

# Oref <- transfer.list[["Zeppelli"]]
predictions <- Seurat::TransferData(
    anchorset = transfer.anchors, 
    refdata = transfer.list[["Zeppilli_et_al"]]$meta_Zeppilli_et_al_subcluster, 
    weight.reduction = "cca",
    dims = 1:Obio@parameterList$singleCellSeuratNpcs4PCA
)
transfer.query <- AddMetaData(transfer.query, metadata = predictions)

dfAdd <- transfer.query@meta.data[,c("predicted.id", "cellID")]
names(dfAdd) <- gsub("predicted.id", "meta_Zeppilli_et_al_subcluster", names(dfAdd))

## Get other half ##
dfAdd2 <- transfer.list[["Zeppilli_et_al"]]@meta.data[,c("meta_Zeppilli_et_al_subcluster", "cellID")]

dfAddFinal <- rbind(dfAdd, dfAdd2)
names(dfAddFinal) <- gsub("meta_Zeppilli_et_al_subcluster","meta_LT_Zeppilli_et_al_Sublusters", names(dfAddFinal))
row.names(dfAddFinal) <- dfAddFinal$cellID
dfAddFinal$cellID <- NULL



OsC <- addDf2seuratMetaData(
    OsC,
    dfAdd = dfAddFinal
) 
   
save(OsC, 
     file = paste0(
         Obio@parameterList$localWorkDir,
         Obio@parameterList$project_id,
         ".Seurat.Robj"
     )
)


## Upload new metadata table ##
#```{r child = 'src/modules/db_tools/upload.meta.data.table.to.DB.Rmd', eval=TRUE}
#
#```




#database.table[is.na(database.table)] <- 0
## Done adding extra dataset                                                 ##
###############################################################################

###############################################################################
## Otional add extra data set                                                ##

#Create transfer list
transfer.list <- SplitObject(
    OsC, 
    split.by = "meta_DataSource"
)

# for (i in 1:length(transfer.list)) {
#     transfer.list[[i]] <- NormalizeData(transfer.list[[i]], verbose = FALSE)
#     transfer.list[[i]] <- FindVariableFeatures(transfer.list[[i]], selection.method = "vst", 
#         nfeatures = 2000, verbose = FALSE)
# }

# Query = destination
transfer.query <- transfer.list[["Zeppilli_et_al"]]



    # pcaproject: Project the PCA from the reference onto the query. We recommend using PCA when reference and query datasets are from scRNA-seq
    # 
    # lsiproject: Project the LSI from the reference onto the query. We recommend using LSI when reference and query datasets are from scATAC-seq. This requires that LSI has been computed for the reference dataset, and the same features (eg, peaks or genome bins) are present in both the reference and query. See RunTFIDF and RunSVD
    # 
    # rpca: Project the PCA from the reference onto the query, and the PCA from the query onto the reference (reciprocal PCA projection).
    # 
    # cca: Run a CCA on the reference and query



transfer.anchors <- Seurat::FindTransferAnchors(
    reference = transfer.list[["Tepe_et_al"]], 
    query = transfer.query, 
    reduction = "cca",
    dims = 1:Obio@parameterList$singleCellSeuratNpcs4PCA
)

#transfer.anchors <- Obio@dataTableList$referenceList[["sampleAnchors"]]

# Oref <- transfer.list[["Zeppelli"]]
predictions <- Seurat::TransferData(
    anchorset = transfer.anchors, 
    refdata = transfer.list[["Tepe_et_al"]]$meta_Tepe_et_al_Cluster, 
    weight.reduction = "cca",
    dims = 1:Obio@parameterList$singleCellSeuratNpcs4PCA
)
transfer.query <- AddMetaData(transfer.query, metadata = predictions)

dfAdd <- transfer.query@meta.data[,c("predicted.id", "cellID")]
names(dfAdd) <- gsub("predicted.id", "meta_Tepe_et_al_Cluster", names(dfAdd))

## Get other half ##
dfAdd2 <- transfer.list[["Tepe_et_al"]]@meta.data[,c("meta_Tepe_et_al_Cluster", "cellID")]

dfAddFinal <- rbind(dfAdd, dfAdd2)
names(dfAddFinal) <- gsub("meta_Tepe_et_al_Cluster","meta_LT_Tepe_et_al_Clusters", names(dfAddFinal))
row.names(dfAddFinal) <- dfAddFinal$cellID
dfAddFinal$cellID <- NULL



OsC <- addDf2seuratMetaData(
    OsC,
    dfAdd = dfAddFinal
) 
   
save(OsC, 
     file = paste0(
         Obio@parameterList$localWorkDir,
         Obio@parameterList$project_id,
         ".Seurat.Robj"
     )
)


## Upload new metadata table ##
#```{r child = 'src/modules/db_tools/upload.meta.data.table.to.DB.Rmd', eval=TRUE}
#
#```




#database.table[is.na(database.table)] <- 0
## Done adding extra dataset                                                 ##
###############################################################################
```


<!-- Add barchart -->
<!-- Set the chnkPrefix to make all chunks unique in the overall folder -->
```{r partB_N_cell_barchart, echo=TRUE, eval=TRUE, warning=FALSE}
chnkPrefix <- "partB.N.cell.barchart."
VersionPdfExt <- VersionPdfExt <- paste0(".",chnkPrefix,"V", gsub("-", "", Sys.Date()), ".pdf")
```



```{r make_percent_N_cells_barchart, echo=TRUE, eval=TRUE, warning=FALSE, results="asis"}
###############################################################################
## Create datatable for plotting                                             ##
## This plotting procedure requires three sets: the sets cellTypeIDs, clusterIDs, cellTypeIDs
## level1ID, level2ID, level3ID

#dfSample <- unique(OsC@meta.data[,c("meta_DataSource","meta_DataSource")])

dfSample <- data.frame(
    sampleName = unique(OsC@meta.data$meta_DataSource),
    sampleColor = c("red", "black"),
    sampleID = unique(OsC@meta.data$meta_DataSource),
    stringsAsFactors= F
)

#dfSample <- unique(OsC@meta.data[,c("sampleName", "sampleColor", "sampleID")])
row.names(dfSample) <- dfSample$sampleID
#dfSample <- dfSample[names(Obio@sampleDetailList),]
sampleIDs <- dfSample$sampleName
colVec <- dfSample$sampleColor
clusterIDs <- unique(dfSample[,"sampleName"])
if (length(grep("cellIdent", names(OsC@meta.data))) == 0){
  OsC@meta.data[["cellIdent"]] <- "All"
}
cellTypeIDs <- unique(OsC@meta.data[,"cellIdent"])
dfTemp <- OsC@meta.data
if (length(grep("^cellIdent$", names(dfTemp))) == 0){
  dfTemp[["cellIdent"]] <- "All"
}
#dfTemp <- dfTemp[dfTemp$percent.mt <= max(Obio@parameterList$singleCellSeuratMtCutoff), ]
dfTemp[["cellID"]] <- row.names(dfTemp)
#dfTemp <- unique(dfTemp[,c("cellID", "sampleName", "clusterName", "cellIdent")])
dfTemp <- unique(dfTemp[,c("cellID", "meta_DataSource", "meta_LT_Zeppilli_et_al_Sublusters", "cellIdent")])
names(dfTemp) <- c("cellID", "sampleName", "clusterName", "cellIdent")


names(dfTemp) <- gsub("clusterName", "Cluster", names(dfTemp) )
 dfTemp <- unique(dfTemp[,c("cellID", "sampleName", "Cluster","cellIdent")])
 
dfRes <- dfTemp
dfRes$cellID <- NULL
row.names(dfRes) <- NULL
dfRes <- unique(dfRes)
dfRes[["N_cells"]] <- 0
for (i in 1:nrow(dfRes)){
  dfRes[i, "N_cells"] <- nrow(dfTemp[dfTemp$sampleName == dfRes[i,"sampleName"] & dfTemp$Cluster == dfRes[i,"Cluster"] & dfTemp$cellIdent == dfRes[i,"cellIdent"], ])
}
## Calculate cluster percentages per celltypeID ##
dfRes[["Perc_cells"]] <- 0
for (i in 1:length(cellTypeIDs)){
  dfResTemp2 <- dfRes[dfRes$cellIdent == cellTypeIDs[i], ]
  tempCluster <- as.vector(unique(dfResTemp2$Cluster))
  
  for (j in 1:length(tempCluster)){
    dfResTemp3 <- dfResTemp2[dfResTemp2$Cluster == tempCluster[j],]
    NclusterTotal <- sum(dfResTemp3[, "N_cells"])
    dfResTemp3[,"Perc_cells"] <- round(dfResTemp3[,"N_cells"]/NclusterTotal, 4)*100
    
    
    if (j ==1){
      dfRes3 <- dfResTemp3
    } else {
      dfRes3 <- rbind(dfResTemp3, dfRes3)
    }
  }
  
  if (i ==1){
    dfRes4 <- dfRes3
  } else {
    dfRes4 <- rbind(dfRes3, dfRes4)
  }
  
}
 
dfRes <- dfRes4
plotList <- list()
chnkVec <- as.vector(NULL, mode = "character")
for (i in 1:length(cellTypeIDs)){
  #############################################################################
  ## Create cell number plot                                                 ##
  tag <- paste0(cellTypeIDs[i], "_Number")
  dfResTemp <- dfRes[dfRes$cellIdent == cellTypeIDs[i], ]
  
  ## Set cluster order large to small ##
  library(tidyverse)
  df <- dfResTemp[,c("Cluster", "N_cells")]
  
  df <- df %>% 
    group_by(Cluster) %>% 
    summarise(N_cells = sum(N_cells)) %>% arrange(desc(N_cells))
  
  levels <- sort(df$Cluster)
  #levels <- c("T1", "ET1", "ET2", "ET3", "ET4", "M1","M2","M3","PG" , "Rest"  )
  dfResTemp$Cluster <- factor(dfResTemp$Cluster, levels = levels)
  
  ## Order ##
   
   plotList[[tag]] <- ggplot(
    ) + geom_bar(aes(y = N_cells, x = Cluster, fill = sampleName), data = dfResTemp, stat="identity"
    ) + labs(title="Cell Numbers Per Cluster", x="", y = "Cell Count"
    ) + theme_bw(
    ) +  theme(
      panel.border = element_rect(colour = "black", fill=NA, size=1),
      plot.title = element_text(hjust = 0.5, size = 12)
    ) + coord_flip() + guides(fill=guide_legend(title="Samples"))
  
  #h <- sum(c("sampleName", "sampleColor") %in% names(OsC@meta.data))
  #if (h ==2){
      #dfCol <- unique(OsC@meta.data[,c("sampleName", "sampleColor")])
      #dfCol <- dfCol[dfCol$sampleName %in% unique(dfResTemp$sampleName), ]
      colVec <- as.vector(dfSample$sampleColor)
      names(colVec) <- as.vector(dfSample$sampleName)
      plotList[[tag]] <- plotList[[tag]] + scale_fill_manual("Samples" ,values = colVec
      ) 
  #}
  
  ## Calculate percentages for this subset ##
  
 
  
  ###########################################################################
  ## Save plot to file                                                     ##
  FNbase <- paste0(tag,".Ncells", VersionPdfExt)
  FN <- paste0(Obio@parameterList$reportFigDir, FNbase)
  FNrel <- paste0("report_figures/", FNbase)
    
  pdf(FN)
      print(plotList[[tag]])
  dev.off()
  ##                                                                       ##
  ###########################################################################
    
  ###########################################################################
  ## Add to chunk                                                          ##
  figCap <- paste0(
      '**Figure ',
      figureCount,
      'A:** Cell Count in each cluster for ', 
      tag,
      'Download a pdf of this figure <a href="',FNrel,'" target="_blank">here</a>. '
  )
  
  NewChnk <- paste0(
    paste0("#### Barchart_ ", tag),
        "\n```{r Barchart-",tag,", results='asis', echo=F, eval=TRUE, warning=FALSE, fig.cap='",figCap,"'}\n",
        "\n",
        "\n print(plotList[['",tag,"']])",
        "\n cat(  '\n')",
        "\n\n\n```\n"   
  )
    
  chnkVec <- c(
      chnkVec,
      NewChnk
  )
  ## Done adding                                                             ##
  #############################################################################
  
  #############################################################################
  ## Add percentage plot                                                     ##
  tag <- paste0(cellTypeIDs[i], "_Percent")
  plotList[[tag]] <- ggplot(
    ) + geom_bar(aes(x = Cluster, y = Perc_cells, fill = sampleName), data = dfResTemp, stat="identity"
    ) + labs(title="Percent Cells Per Cluster", x="", y = "Percent Cells"
    ) + theme_bw(
    ) +  theme(
      panel.border = element_rect(colour = "black", fill=NA, size=1),
      plot.title = element_text(hjust = 0.5, size = 12)
    ) +  coord_flip() 
  
  # h <- sum(c("sampleName", "sampleColor") %in% names(OsC@meta.data))
  #if (h ==2){
      # dfCol <- unique(OsC@meta.data[,c("sampleName", "sampleColor")])
      # dfCol <- dfCol[dfCol$sampleName %in% unique(dfResTemp$sampleName), ]
      # colVec <- as.vector(dfCol$sampleColor)
      # names(colVec) <- as.vector(dfCol$sampleName)
      
      colVec <- as.vector(dfSample$sampleColor)
      names(colVec) <- as.vector(dfSample$sampleName)
      plotList[[tag]] <- plotList[[tag]] + scale_fill_manual("Samples" ,values = colVec
      ) 
  #}
  
  ###########################################################################
  ## Save plot to file                                                     ##
  FNbase <- paste0(tag, ".percent.cells",VersionPdfExt)
  FN <- paste0(Obio@parameterList$reportFigDir, FNbase)
  FNrel <- paste0("report_figures/", FNbase)
    
  pdf(FN)
      print(plotList[[tag]])
  dev.off()
  ##                                                                       ##
  ###########################################################################
    
  ###########################################################################
  ## Add to chunk                                                          ##
  figCap <- paste0(
      '**Figure ',
      figureCount,
      'B:** Cell percentages in each cluster for ', 
      tag,
      'Download a pdf of this figure <a href="',FNrel,'" target="_blank">here</a>. '
  )
  
  NewChnk <- paste0(
    paste0("#### Barchart_ ", tag),
        "\n```{r Barchart-percent_",tag,", results='asis', echo=F, eval=TRUE, warning=FALSE, fig.cap='",figCap,"'}\n",
        "\n",
        "\n print(plotList[['",tag,"']])",
        "\n cat(  '\n')",
        "\n\n\n```\n"   
  )
    
  chnkVec <- c(
      chnkVec,
      NewChnk
  )
  ## Done adding percentage plot                                             ##
  #############################################################################
  
  
  figureCount <- figureCount + 1
  
  #############################################################################
  ## Order Percent Cells by Similarity
  if (!is.null(Obio@parameterList$clusterNameOrder)){
        #############################################################################
        ## Add percentage plot                                                     ##
        if (sum(unique(dfResTemp$Cluster) %in% Obio@parameterList$clusterNameOrder) == length(Obio@parameterList$clusterNameOrder)){
            dfResTemp$Cluster <- factor(dfResTemp$Cluster, levels = Obio@parameterList$clusterNameOrder)
        }
        
        
        
        tag <- paste0(cellTypeIDs[i], "_Percent_clustered")
        plotList[[tag]] <- ggplot(
          ) + geom_bar(aes(x = Cluster, y = Perc_cells, fill = sampleName), data = dfResTemp, stat="identity"
          ) + labs(title="Percent Cells Per Cluster Clustered", x="", y = "Percent Cells"
          ) + theme_bw(
          ) +  theme(
            panel.border = element_rect(colour = "black", fill=NA, size=1),
            plot.title = element_text(hjust = 0.5, size = 12)
          ) +  coord_flip() 
        
         #h <- sum(c("sampleName", "sampleColor") %in% names(OsC@meta.data))
        #if (h ==2){
        #    dfCol <- unique(OsC@meta.data[,c("sampleName", "sampleColor")])
        #    dfCol <- dfCol[dfCol$sampleName %in% unique(dfResTemp$sampleName), ]
        #    colVec <- as.vector(dfCol$sampleColor)
           # names(colVec) <- as.vector(dfCol$sampleName)
            colVec <- as.vector(dfSample$sampleColor)
      names(colVec) <- as.vector(dfSample$sampleName)
            
            plotList[[tag]] <- plotList[[tag]] + scale_fill_manual("Samples" ,values = colVec
            ) 
        }
        
        ###########################################################################
        ## Save plot to file                                                     ##
        FNbase <- paste0(tag, ".percent.cells.clustered",VersionPdfExt)
        FN <- paste0(Obio@parameterList$reportFigDir, FNbase)
        FNrel <- paste0("report_figures/", FNbase)
          
        pdf(FN)
            print(plotList[[tag]])
        dev.off()
        ##                                                                       ##
        ###########################################################################
          
        ###########################################################################
        ## Add to chunk                                                          ##
        figCap <- paste0(
            '**Figure ',
            figureCount,
            'C:** Cell percentages in each cluster for ', 
            tag,'. Clustered by cluster similarity.',
            'Download a pdf of this figure <a href="',FNrel,'" target="_blank">here</a>. '
        )
        
        NewChnk <- paste0(
          paste0("#### Barchart_ ", tag),
              "\n```{r Barchart-percent_",tag,", results='asis', echo=F, eval=TRUE, warning=FALSE, fig.cap='",figCap,"'}\n",
              "\n",
              "\n print(plotList[['",tag,"']])",
              "\n cat(  '\n')",
              "\n\n\n```\n"   
        )
          
        chnkVec <- c(
            chnkVec,
            NewChnk
        )
        ## Done adding percentage plot                                             ##
        #############################################################################
        
        
        figureCount <- figureCount + 1
      
  }
  
  
  ##
  #############################################################################
  

## Done creating data table                                                  ##
###############################################################################
if (length(plotList) > 3){
    tabVar <- ".tabset .tabset-fade .tabset-dropdown"
} else {
    tabVar <- ".tabset .tabset-fade .tabset-pills"
}
```

### Barchart N cells and Percent in Clusters {`r tabVar`}
if you could prepare a bar-shape graph with the %of cells clusters representing our populations (like in the Nat Med)

```{r plot_barchart, echo=TRUE, eval=TRUE, warning=FALSE, results="asis"}
cat(paste(knit(text = chnkVec, quiet = T), collapse = '\n'))
```

```{r saveobject, eval=TRUE, echo=T, results=F}
### Will save Obio object here, so it can be re-used with different parameters
save(Obio, 
     file = paste0(
         Obio@parameterList$localWorkDir,
         Obio@parameterList$project_id,
         ".bioLOGIC.Robj"
     )
)

print("Obio Object saved.")

# save(OsC,
#     file = paste0(
#          Obio@parameterList$localWorkDir,
#          Obio@parameterList$project_id,
#         ".Seurat.Robj"
#      )
# )

```

## Documentation
```{r documentation, eval=TRUE, echo=T, results=T}
sessionInfo()
```