<!-- Set PArameters Module -->
<!-- Set the chnkPrefix to make all chunks unique in the overall folder -->
```{r partB_pcaB6_plots, echo=TRUE, eval=TRUE, warning=FALSE}
chnkPrefix <- "B6.pca.plots."
VersionPdfExt <- VersionPdfExt <- paste0(".",chnkPrefix,"V", gsub("-", "", Sys.Date()), ".pdf")

```



```{r partB_upload_markers, echo=TRUE, eval=TRUE, warning=FALSE, results=F}

###############################################################################
## Upload general markers                                                    ##

dfGeneralMarkers <- Obio@dataTableList[["dfGeneralMarkers"]] 
dfDat <- dfGeneralMarkers
dfDat <- unique(dfDat[,c("gene", "cluster")])


if (Obio@parameterList$geneIDcolumn != "hgnc_symbol" & Obio@parameterList$geneIDcolumn != "mgi_symbol"){
    refGeneIDcolumn <- "hgnc_symbol"
    dfAnno <- Obio@dfGeneAnnotation
    dfAnno <- unique(dfAnno[,c("hgnc_symbol",Obio@parameterList$geneIDcolumn )])
    dfAnno <- dfAnno[dfAnno[,Obio@parameterList$geneIDcolumn] %in% dfDat[,"gene"],]
    
    dfDat <- merge(
        dfDat,
        dfAnno,
        by.x = "gene",
        by.y = Obio@parameterList$geneIDcolumn
    )
    dfDat$gene <- NULL
    names(dfDat) <- gsub("hgnc_symbol", "gene",names(dfDat))
    
} else {
    refGeneIDcolumn <- Obio@parameterList$geneIDcolumn
}

library(tidyverse)
#library(dplyr)

if (ncol(dfDat) > 1){
  
  dfDat <- dfDat %>%
         dplyr::group_by(cluster) %>% 
         dplyr::mutate(rn = row_number()) %>%
         ungroup %>%
         tidyr::pivot_wider(names_from = cluster, values_from = gene, values_fill = "") %>% dplyr::select(-rn)
  
  orderVec <- sort(names(dfDat))
  dfDat <- data.frame(dfDat[,orderVec])
  
  names(dfDat) <- paste0(
      names(dfDat)
      #"_Marker_Genes_Cluster_",
      #Obio@parameterList$project_id
  )
  
  dfDat <- data.frame(dfDat)
  
  ## Insert description row ##
  descriptionRow <- data.frame(dfDat[1,])
  descriptionRow[1,] <- t(names(dfDat))
  descriptionRow[1,] <- paste0(descriptionRow[1,], " from Seurat FindAllMarkers.")
  
  dfDat <- rbind(
    descriptionRow, 
    dfDat
  )
  # dfCatRef <- names(dfCatRef)
  # names(dfCatRef) <- names(dfDat)
  # 
  # dfDat <- rbind(
  #   dfCatRef, 
  #   dfDat
  # )
  
  #######################################################################
  ## Upload/update category by category                                ##
  updatedCatIDs <- as.vector(NULL, mode = "character")
  updatedCatNames <- as.vector(NULL, mode = "character")
  DGEmarkerGeneList <- list()
          
  for (i in 1:ncol(dfDat)){
      cat.name <- names(dfDat)[i]
      #cat_type <- paste0("temp_cluster_marker_", Obio@parameterList$project_id)
              
      #cat.description.text <- as.vector(dfDat[1,i])
              
      gene.vec <- as.vector(
          dfDat[,i]
      )[2:nrow(dfDat)]
              
      gene.vec <- gene.vec[gene.vec != ""]
      gene.vec <- sort(na.omit(gene.vec))
              
      ## Determine if cat exists ##
      if (length(gene.vec) > 0){
          DGEmarkerGeneList[[cat.name]] <- gene.vec
      }
              
      # if (upload.results.to.database){        
      #     catID <- add.category.to.lab.reference.table.hs(
      #         host = Obio@dbDetailList$host,
      #         pwd = db.pwd,
      #         user = Obio@dbDetailList$db.user,
      #         cat.ref.db = Obio@dbDetailList$ref.cat.db,
      #         cat.ref.db.table = Obio@parameterList$lab.categories.table,
      #         gene.vector = gene.vec,
      #         gene.id = refGeneIDcolumn, #options hgnc_symbol, mgi_symbol
      #         mm.hs.conversion.file =  paste0(cwd, "/assets/annotation/homologene.data.txt"),
      #         cat_name = cat.name,
      #         cat_type = cat_type,
      #         data_source = paste0(Obio@parameterList$labname, " Lab"),
      #         comments_1 = "",
      #         comments_2 = "",
      #         new.lab.category.table = F,
      #         cat.description.db  = "internal_categories",
      #         cat.description.db.table = "category_description",
      #         cat.description.text = cat.description.text,
      #         lab.name = Obio@parameterList$labname,
      #         replaceExistingCatName = T
      #     ) 
      # } else {
      #   catID <- paste0("B5_", i)
      # }
          
              
  #     updatedCatIDs <- c(
  #         updatedCatIDs, 
  #         catID
  #     )    
  #     
  #     updatedCatNames <- c(
  #       updatedCatNames, 
  #       cat.name
  #     )
   } ## End dfDat loop
          
  # dfFAMplotIDs <- data.frame(
  #   cat_id = updatedCatIDs, 
  #   cat_name = updatedCatNames,
  #   stringsAsFactors = F
  # )    
  
  Obio@dataTableList[["DGEmarkerGeneList"]] <- DGEmarkerGeneList

        
## Done uploading general markers                                            ##
###############################################################################

} else {
     #Obio@dataTableList[["dfGeneralMarkers"]] <- NULL
     Obio@dataTableList[["DGEmarkerGeneList"]] <- NULL
}

#############################################################

```


If you wish to get a bit of background on tSNE dimensionality reduction, take a look at 
<a href="https://www.youtube.com/watch?v=NEaUSP4YerM" target="_blank"> this youtube video</a> by Josh Starmer from the University of North Carolina.

If you wish to get a bit of background on UMAP (and other) dimensionality reduction algorithms, take a look at 
<a href="https://www.youtube.com/watch?v=9iol3Lk6kyU" target="_blank"> this youtube video</a> by
recaping a lecture at the PyData 2018 conference.   
```{r data_prep_sample_UMAP_rendering, echo=TRUE, eval=TRUE, warning=FALSE, results=FALSE} 

reductionVec <- c("umap", "tsne")

plotList <- list()
chnkVec <- as.vector(NULL, mode = "character")


###############################################################################
## First UMAP all samples together                                           ##
tag <- paste0("UMAP_sample_level")

dfPlot <- OsC@meta.data
pos <- grep("included", names(dfPlot))
if (length(pos) == 0){
  dfPlot[["included"]] <- "+"
}

pos <- grep("cellID", names(dfPlot))
if (length(pos) == 0){
  dfPlot[["cellID"]] <- row.names(dfPlot)
}

dfPlot$UMAP_1 <- NULL
dfPlot$UMAP_2 <- NULL
            
## Get UMAP coordinates ##
coord <- data.frame(OsC@reductions$umap@cell.embeddings)
coord[["cellID"]] <- row.names(coord)
coord <-coord[coord$cellID %in% dfPlot$cellID, ]
            
dfPlot <- merge(dfPlot, coord, by.x = "cellID", by.y="cellID", all=T)
dfPlot[is.na(dfPlot)] <- 0
dfPlot <- dfPlot[dfPlot$UMAP_1 != 0 & dfPlot$UMAP_2 != 0,]
            
            
## Add cluster colors ##
dfPlot[["Cluster"]] <- dfPlot$sampleName
clusterVec <- as.vector(sort(unique(dfPlot$sampleName)))

maxX <- 1.1*max(dfPlot$UMAP_1, na.rm = T)
minX <- 1.1*min(dfPlot$UMAP_1, na.rm = T)
maxY <- 1.1*max(dfPlot$UMAP_2, na.rm = T)
minY <- 1.1*min(dfPlot$UMAP_2, na.rm = T)            

dfPair <- unique(OsC@meta.data[,c("sampleName","sampleID", "sampleColor")])
row.names(dfPair) <- dfPair$sampleID

#colVec <- dfPair$sampleColor
#names(colVec) <- dfPair$sampleName

#dfPlot$Cluster <- factor(dfPlot$Cluster, levels = dfPair$sampleName)

dfPlot$sampleName <- factor(
    dfPlot$sampleName, 
    levels = Obio@parameterList$sampleNameOrder
)

dfPlot <- dfPlot[order(dfPlot$sampleName),]

# dotsize  = 1
# if (nrow(dfPlot) > 10000){
#   dotsize  = 0.75
# } else if (nrow(dfPlot) > 20000){
#   dotsize = 0.5
# } else if (nrow(dfPlot) > 50000){
#   dotsize = 0.25
# }

plotList[[tag]] <- ggplot2::ggplot(
    data=dfPlot[dfPlot$included == "+",], 
    ggplot2::aes(UMAP_1, UMAP_2, color=sampleName)
  ) + ggplot2::geom_point( shape=16, size = as.numeric(dotsize)
  ) + ggplot2::xlab("UMAP1") + ggplot2::ylab("UMAP2"
  ) + ggplot2::theme_bw(
  )  +  ggplot2::theme(
      axis.text.y   = ggplot2::element_text(size=8),
      axis.text.x   = ggplot2::element_text(size=8),
      axis.title.y  = ggplot2::element_text(size=8),
      axis.title.x  = ggplot2::element_text(size=8),
      axis.line = ggplot2::element_line(colour = "black"),
      panel.border = ggplot2::element_rect(colour = "black", fill=NA, size=1),
      plot.title = ggplot2::element_text(hjust = 0.5, size = 12),
      legend.title = ggplot2::element_blank()
  ) + ggplot2::guides(col = ggplot2::guide_legend(override.aes = list(shape = 16, size = legendDotSize))
  ) + ggplot2::ggtitle(paste0("Sample: ", gsub("_", " ", tag))
  ) + ggplot2::xlim(minX, maxX) + ggplot2::ylim(minY, maxY
  ) + ggplot2::coord_fixed(ratio=1
  )  


h <- sum(c("sampleName", "sampleColor") %in% names(dfPlot))
if (h ==2){
  dfCol <- unique(dfPlot[,c("sampleName", "sampleColor")])
  colVec <- as.vector(dfCol$sampleColor)
  names(colVec) <- as.vector(dfCol$sampleName)
  plotList[[tag]] <- plotList[[tag]] + ggplot2::scale_colour_manual("Samples" ,values = colVec
      ) + ggplot2::guides(col = ggplot2::guide_legend(override.aes = list(shape = 16, size = legendDotSize))
  )
}
## Add colors if specified ##

            
if (length(unique(dfPlot$Cluster)) > 15){
   plotList[[tag]] <- plotList[[tag]] + ggplot2::theme(legend.position = "none")
}
            FNbase <- paste0(tag, VersionPdfExt)
            FN <- paste0(Obio@parameterList$reportFigDir, FNbase)
            FNrel <- paste0("report_figures/", FNbase)
            
            pdf(FN)
                print(plotList[[tag]])
            dev.off()
            
            
            if (exists("shinyURL") & !is.null(shinyURL)){
            link <- paste0(
              'An interactive version of this figure with additional viewing options can be found <a href="',shinyURL,'?_inputs_&y_axis=%22UMAP_2%22&x_axis=%22UMAP_1%22&colorBy=%22sampleName%22&splitByColumn=%22all%22" target="_blank">here</a>. '
            )
            
            } else {
              link <- ""
            }
            
            figLegend <- paste0(
                '**Figure ', 
                figureCount, 
                ':** ',
                ' UMAP showing all cells from all samples together. Download a pdf of this figure <a href="',FNrel,'" target="_blank">here</a>. ',
                 link
            )
            
            figureCount <- figureCount + 1
            
            NewChnk <- paste0(
                "#### ", tag,
                "\n```{r Sample_UMAP_",
                tag,", results='asis', echo=F, eval=TRUE, warning=FALSE, fig.cap='",
                figLegend,"'}\n",
                "\n",
                "\n print(plotList[['",tag,"']])",
                "\n cat(  '\n')",
                "\n\n\n```\n"   
            )
            
            chnkVec <- c(
                chnkVec,
                NewChnk
            )


## Done first umap all samples                                               ##
###############################################################################
            
###############################################################################
## First tsne all samples together                                           ##
tag <- paste0("tSNE_All_Samples")
dfPlot <- OsC@meta.data
pos <- grep("included", names(dfPlot))
if (length(pos) == 0){
  dfPlot[["included"]] <- "+"
}

pos <- grep("cellID", names(dfPlot))
if (length(pos) == 0){
  dfPlot[["cellID"]] <- row.names(dfPlot)
}



dfPlot$tSNE_1 <- NULL
dfPlot$tSNE_2 <- NULL
            
## Get tsNE coordinates ##
coord <- data.frame(OsC@reductions$tsne@cell.embeddings)
coord[["cellID"]] <- row.names(coord)
coord <-coord[coord$cellID %in% dfPlot$cellID, ]
            
dfPlot <- merge(dfPlot, coord, by.x = "cellID", by.y="cellID", all=T)
dfPlot[is.na(dfPlot)] <- 0
dfPlot <- dfPlot[dfPlot$tSNE_1 != 0 & dfPlot$tSNE_2 != 0,]
            
            
## Add cluster colors ##
dfPlot[["Cluster"]] <- dfPlot$sampleName
# clusterVec <- as.vector(unique(sort(dfPlot$sampleName)))
clusterVec <- Obio@parameterList$sampleNameOrder 

maxX <- 1.1*max(dfPlot$tSNE_1, na.rm = T)
minX <- 1.1*min(dfPlot$tSNE_1, na.rm = T)
maxY <- 1.1*max(dfPlot$tSNE_2, na.rm = T)
minY <- 1.1*min(dfPlot$tSNE_2, na.rm = T)            

# library(scales)
# clusterCols = hue_pal()(length(clusterVec))
# dfPlot$Cluster <- factor(dfPlot$Cluster, levels = clusterVec)

# dotsize  = 1.5
# if (nrow(dfPlot) > 10000){
#   dotsize  = 0.75
# } else if (nrow(dfPlot) > 50000){
#   dotsize = 0.5
# } else {
#   dotsize = 0.25
# }

dfPlot$sampleName <- factor(
    dfPlot$sampleName, 
    levels = Obio@parameterList$sampleNameOrder
)

dfPlot <- dfPlot[order(dfPlot$sampleName),]

plotList[[tag]] <- ggplot2::ggplot(data=dfPlot[dfPlot$included == "+",], ggplot2::aes(tSNE_1, tSNE_2, color=sampleName)
            ) + ggplot2::geom_point( shape=16, size = as.numeric(dotsize)
            ) + ggplot2::xlab("tSNE1") + ylab("tSNE2"
            ) + ggplot2::theme_bw(
            )  +  ggplot2::theme(
                axis.text.y   = ggplot2::element_text(size=8),
                axis.text.x   = ggplot2::element_text(size=8),
                axis.title.y  = ggplot2::element_text(size=8),
                axis.title.x  = ggplot2::element_text(size=8),
                axis.line = ggplot2::element_line(colour = "black"),
                panel.border = ggplot2::element_rect(colour = "black", fill=NA, size=1),
                plot.title = ggplot2::element_text(hjust = 0.5, size = 12),
                legend.title = ggplot2::element_blank()
            ) + ggplot2::ggtitle(paste0("Sample: ", tag)
            ) + ggplot2::guides(col = guide_legend(override.aes = list(shape = 16, size = legendDotSize))
            ) + ggplot2::xlim(minX, maxX) + ggplot2::ylim(minY, maxY
            ) + ggplot2::coord_fixed(ratio=1
            ) 

h <- sum(c("sampleName", "sampleColor") %in% names(dfPlot))
if (h ==2){
  dfCol <- unique(dfPlot[,c("sampleName", "sampleColor")])
  colVec <- as.vector(dfCol$sampleColor)
  names(colVec) <- as.vector(dfCol$sampleName)
  plotList[[tag]] <- plotList[[tag]] + ggplot2::scale_colour_manual("Samples" ,values = colVec
      ) + ggplot2::guides(col = ggplot2::guide_legend(override.aes = list(shape = 16, size = legendDotSize))
  )
}
            
if (length(unique(dfPlot$Cluster)) > 15){
   plotList[[tag]] <- plotList[[tag]] + ggplot2::theme(legend.position = "none")
}
            FNbase <- paste0(tag, VersionPdfExt)
            FN <- paste0(Obio@parameterList$reportFigDir, FNbase)
            FNrel <- paste0("report_figures/", FNbase)
            
            pdf(FN)
                print(plotList[[tag]])
            dev.off()
            
            if (exists("shinyURL") & !is.null(shinyURL)){
                link <- paste0(
                  'An interactive version of this figure with additional viewing options can be found <a href="',shinyURL,'?_inputs_&y_axis=%22tSNE_2%22&x_axis=%22tSNE_1%22&colorBy=%22sampleName%22&splitByColumn=%22all%22" target="_blank">here</a>. '
                )
            } else {
              link <- ""
            }
            
          
            
            figLegend <- paste0(
                '**Figure ', 
                figureCount, 
                ':** ',
                ' tSNE showing all cells from all samples together. Download a pdf of this figure <a href="',FNrel,'" target="_blank">here</a>.',
                link
            )
            
            figureCount <- figureCount + 1
            
            NewChnk <- paste0(
                "#### ", tag,
                "\n```{r Sample_tSNE_",
                tag,", results='asis', echo=F, eval=TRUE, warning=FALSE, fig.cap='",
                figLegend,"'}\n",
                "\n",
                "\n print(plotList[['",tag,"']])",
                "\n cat(  '\n')",
                "\n\n\n```\n"   
            )
            
            chnkVec <- c(
                chnkVec,
                NewChnk
            )


## Done first tsne all samples                                               ##
###############################################################################            
###############################################################################
## Make one UMAP plot per sample                                             ##

sampleVec <- Obio@parameterList$sampleNameOrder            
            

dfPlot <- OsC@meta.data
pos <- grep("included", names(dfPlot))
if (length(pos) == 0){
  dfPlot[["included"]] <- "+"
}

pos <- grep("cellID", names(dfPlot))
if (length(pos) == 0){
  dfPlot[["cellID"]] <- row.names(dfPlot)
}

## Get UMAP coordinates ##
coord <- data.frame(OsC@reductions$umap@cell.embeddings)
coord[["cellID"]] <- row.names(coord)
coord <-coord[coord$cellID %in% dfPlot$cellID, ]
dfPlot$UMAP_1 <- NULL
dfPlot$UMAP_2 <- NULL
            
dfPlot <- merge(dfPlot, coord, by.x = "cellID", by.y="cellID", all=T)
dfPlot[is.na(dfPlot)] <- 0
dfPlot <- dfPlot[dfPlot$UMAP_1 != 0 & dfPlot$UMAP_2 != 0,]
            
            
## Add cluster colors ##
dfPlot[["Cluster"]] <- dfPlot$sampleID
clusterVec <- as.vector(unique(sort(dfPlot$sampleName)))
            
# library(scales)
# clusterCols = hue_pal()(length(clusterVec))
# 
# dfPlot$Cluster <- factor(dfPlot$Cluster, levels = clusterVec)            
            
maxX <- 1.1*max(dfPlot$UMAP_1, na.rm = T)
minX <- 1.1*min(dfPlot$UMAP_1, na.rm = T)
maxY <- 1.1*max(dfPlot$UMAP_2, na.rm = T)
minY <- 1.1*min(dfPlot$UMAP_2, na.rm = T)               
                                   
for (i in 1:length(sampleVec)){
    tag <- paste0("UMAP_plot_by_", sampleVec[i])
    
    dfPlotSel <- dfPlot[dfPlot$sampleName == sampleVec[i], ]
    dfPlotSel$sampleName       
            
            
    plotList[[tag]] <- ggplot2::ggplot(data=dfPlotSel[dfPlotSel$included == "+",], ggplot2::aes(UMAP_1, UMAP_2, color=sampleName)
            ) + ggplot2::geom_point( shape=16, size = as.numeric(dotsize)
            ) + ggplot2::xlab("UMAP1") + ggplot2::ylab("UMAP2"
            ) + ggplot2::theme_bw(
            )  +  ggplot2::theme(
                axis.text.y   = ggplot2::element_text(size=8),
                axis.text.x   = ggplot2::element_text(size=8),
                axis.title.y  = ggplot2::element_text(size=8),
                axis.title.x  = ggplot2::element_text(size=8),
                axis.line = ggplot2::element_line(colour = "black"),
                panel.border = ggplot2::element_rect(colour = "black", fill=NA, size=1),
                plot.title = ggplot2::element_text(hjust = 0.5, size = 12),
                legend.title = ggplot2::element_blank()
            ) + ggplot2::guides(col = ggplot2::guide_legend(override.aes = list(shape = 16, size = legendDotSize))    
            ) + ggplot2::ggtitle(paste0("Sample: ", gsub("_", " ", tag))
            ) + ggplot2::xlim(minX, maxX) + ggplot2::ylim(minY, maxY
            ) + ggplot2::coord_fixed(ratio=1)
            #) + scale_color_manual(values = clusterCols[i]
             
    
            h <- sum(c("sampleName", "sampleColor") %in% names(dfPlotSel))
            if (h ==2){
              dfCol <- unique(dfPlotSel[,c("sampleName", "sampleColor")])
              colVec <- as.vector(dfCol$sampleColor)
              names(colVec) <- as.vector(dfCol$sampleName)
              plotList[[tag]] <- plotList[[tag]] + ggplot2::scale_colour_manual("Samples" ,values = colVec
                  ) + ggplot2::guides(col = ggplot2::guide_legend(override.aes = list(shape = 16, size = legendDotSize))
              )
            }    
    
    if (length(unique(dfPlot$Cluster)) > 15){
   plotList[[tag]] <- plotList[[tag]] + ggplot2::theme(legend.position = "none")
}
            
            FNbase <- paste0(tag, VersionPdfExt)
            FN <- paste0(Obio@parameterList$reportFigDir, FNbase)
            FNrel <- paste0("report_figures/", FNbase)
            
            pdf(FN)
                print(plotList[[tag]])
            dev.off()
            
            
            if (exists("shinyURL") & !is.null(shinyURL)){
            link <- paste0(
              'An interactive version of this figure with additional viewing options can be found <a href="',shinyURL,'?_inputs_&y_axis=%22UMAP_2%22&x_axis=%22UMAP_1%22&colorBy=%22sampleName%22&splitByColumn=%22sampleName%22" target="_blank">here</a>. '
            )
            
            } else {
              link <- ""
            }
            
            figLegend <- paste0(
                '**Figure ', 
                figureCount, 
                ':** ',
                ' Sample-level UMAPs. Download a pdf of this figure <a href="',FNrel,'" target="_blank">here</a>. ',
                link
            )
            
            figureCount <- figureCount + 1
            
            NewChnk <- paste0(
                paste("#### ", tag),
                "\n```{r Sample_UMAP_",
                tag,", results='asis', echo=F, eval=TRUE, warning=FALSE, fig.cap='",
                figLegend,"'}\n",
                "\n",
                "\n print(plotList[['",tag,"']])",
                "\n cat(  '\n')",
                "\n\n\n```\n"   
            )
            
            chnkVec <- c(
                chnkVec,
                NewChnk
            )
            
            
    
    
    
    
}

## Done making one umap plot per sample                                      ##
###############################################################################


###############################################################################
## Add cluster dendrogram by sample                                          ##

# if (length(unique(OsC@meta.data$sampleID)) > 2){
#   
#   library(ggtree)
#   library(Seurat)
#   # Buildclustertree only works like this
#   Seurat::Idents(OsC) <- "sampleName"
#   OsC <- Seurat::BuildClusterTree(OsC)
#       
#   tag <- paste0("Sample_Dendrogram")
#       
#   OsC@tools$BuildClusterTree$tip.label <- paste0( OsC@tools$BuildClusterTree$tip.label)
#       
#   plotList[[tag]]  <- ggplot2::ggplot(OsC@tools$BuildClusterTree
#       ) + ggtree::geom_tree(
#       ) + ggtree::theme_tree(
#       ) 
#   
#   h <- sum(c("sampleName", "sampleColor") %in% names(OsC@meta.data))
#   if (h ==2){
#     dfCol <- unique(OsC@meta.data[,c("sampleName", "sampleColor")])
#     colVec <- as.vector(dfCol$sampleColor)
#     names(colVec) <- as.vector(dfCol$sampleName)
#     plotList[[tag]] <- plotList[[tag]] + ggtree::geom_tiplab(color=colVec
#       ) 
#   } else {
#     plotList[[tag]] <- plotList[[tag]] + ggtree::geom_tiplab(
#       )   
#   }
#   
#   #plotList[[tag]] <- plotList[[tag]] + geom_tippoint(aes(color=sampleName), size=1.5)
#   
#   plotList[[tag]] <- plotList[[tag]] + ggplot2::labs(title=tag
#       ) + ggplot2::theme(
#         panel.border = ggplot2::element_rect(colour = "black", fill=NA, size=1),
#         axis.title.x=ggplot2::element_blank(),
#         plot.title = ggplot2::element_text(hjust = 0.5, size = 12)
#       )  + ggplot2::xlim(0,dendrofactor*max(OsC@tools$BuildClusterTree[[2]]))
#  
#       
#   ## Save to file ##
#   FNbase <- paste0(tag,".", VersionPdfExt)
#   FN <- paste0(Obio@parameterList$reportFigDir, FNbase)
#   FNrel <- paste0("report_figures/", FNbase)
#       
#   pdf(FN)
#       print(plotList[[tag]])
#   dev.off()
#       
#   
#   
#   figLegend <- paste0(
#       '**Figure ', 
#           figureCount, 
#           ':** ',
#           ' Clusterplot dendrogram by sample ID. ','A pdf of this figure can be downloaded <a href="',FNrel,'" target="_blank">here</a>. '
#       )
#       
#       
#       NewChnk <- paste0(
#           "#### SampleID Dendrogram",
#           "\n```{r ", tag, "results='asis', echo=F, eval=TRUE, warning=FALSE, fig.cap='",
#           figLegend,"'}\n",
#           "\n",
#           "\n print(plotList[['",tag,"']])",
#           "\n cat(  '\n')",
#           "\n\n\n```\n"   
#       )
#       
#       chnkVec <- c(
#           chnkVec,
#           NewChnk
#       )
#       
#       
#       figureCount <- figureCount + 1
# }

## Done by sample                                                            ##
###############################################################################

###############################################################################
## Save intermediate objects                                                 ##
save(OsC,
    file = paste0(
         Obio@parameterList$localWorkDir,
         Obio@parameterList$project_id,
        ".Seurat.Robj"
     )
)

save(Obio, 
     file = paste0(
         Obio@parameterList$localWorkDir,
         Obio@parameterList$project_id,
         ".bioLOGIC.Robj"
     )
)

## Done                                                                      ##
###############################################################################

if (length(plotList) > 2){
    tabVar <- ".tabset .tabset-fade .tabset-dropdown"
} else {
    tabVar <- ".tabset .tabset-fade .tabset-pills"
}

```

### Dimensionality Reduction Plots by Sample {`r tabVar`}

```{r Plot_tsne_data_plotting, echo=TRUE, eval=TRUE, warning=FALSE, results="asis"} 

cat(paste(knitr::knit(text = chnkVec, quiet = T), collapse = '\n'))

```
