<!-- Set PArameters Module -->
<!-- Set the chnkPrefix to make all chunks unique in the overall folder -->
```{r partB_cell_cycle_phase, echo=TRUE, eval=TRUE, warning=FALSE}
chnkPrefix <- "partB.doublet."
VersionPdfExt <- VersionPdfExt <- paste0(".",chnkPrefix,"V", gsub("-", "", Sys.Date()), ".pdf")

```



```{r Plot_dimred_by_cell_cycle_phase_data_prep, echo=TRUE, eval=TRUE, warning=FALSE, results=FALSE} 

###############################################################################
## Estimate cell cycle genes                                                 ##
exprFN <- paste0(hpc.mount, "Projects/reference_data/cell_cycle_vignette_files/nestorawa_forcellcycle_expressionMatrix.txt")

exp.mat <- read.table(file = exprFN, header = TRUE, 
                      as.is = TRUE, row.names = 1)


# A list of cell cycle markers, from Tirosh et al, 2015, is loaded with Seurat.  We can
# segregate this list into markers of G2/M phase and markers of S phase
s.genes <- cc.genes$s.genes
g2m.genes <- cc.genes$g2m.genes

print(paste0("Used as S-phase marker genes: ", sort(unique(paste(s.genes, collapse = ", ")))))
print(paste0("Used as G2M-phase marker genes: ", sort(unique(paste(g2m.genes, collapse = ", ")))))

# Create our Seurat object and complete the initalization steps
OsC <- CellCycleScoring(OsC, s.features = s.genes, g2m.features = g2m.genes, set.ident = TRUE)

reductionVec <- c("umap", "tsne")
plotList <- list()
chnkVec <- as.vector(NULL, mode = "character")

###############################################################################
## First UMAP all samples together                                           ##
tag <- paste0("CellCyclePhase_All_Samples")
dfPlot <- OsC@meta.data
pos <- grep("included", names(dfPlot))
if (length(pos) == 0){
  dfPlot[["included"]] <- "+"
}
dfPlot[["cellID"]] <- row.names(dfPlot)
dfPlot$UMAP_1 <- NULL
dfPlot$UMAP_2 <- NULL
            
## Get UMAP coordinates ##
coord <- data.frame(OsC@reductions$umap@cell.embeddings)
coord[["cellID"]] <- row.names(coord)
coord <-coord[coord$cellID %in% dfPlot$cellID, ]
            
dfPlot <- merge(dfPlot, coord, by.x = "cellID", by.y="cellID", all=T)
dfPlot[is.na(dfPlot)] <- 0
dfPlot <- dfPlot[dfPlot$UMAP_1 != 0 & dfPlot$UMAP_2 != 0,]
            
            
## Add cluster colors ##
#dfPlot[["Cluster"]] <- paste0("C", dfPlot$seurat_clusters)
#clusterVec <- as.vector(paste0("C", unique(sort(dfPlot$seurat_clusters))))

maxX <- 1.1*max(dfPlot$UMAP_1, na.rm = T)
minX <- 1.1*min(dfPlot$UMAP_1, na.rm = T)
maxY <- 1.1*max(dfPlot$UMAP_2, na.rm = T)
minY <- 1.1*min(dfPlot$UMAP_2, na.rm = T)            

# library(scales)
# clusterCols = hue_pal()(length(clusterVec))
# dfPlot$Cluster <- factor(dfPlot$Cluster, levels = clusterVec)

# dotsize  = 1
# if (nrow(dfPlot) > 10000){
#   dotsize  = 0.75
# } else if (nrow(dfPlot) > 20000){
#   dotsize = 0.5
# } else if (nrow(dfPlot) > 50000){
#   dotsize = 0.25
# }

plotList[[tag]] <- ggplot(data=dfPlot[dfPlot$included == "+",], aes(UMAP_1, UMAP_2, color=Phase)
            ) + ggrastr::rasterize(ggplot2::geom_point( shape=16, size = as.numeric(dotsize), dpi = rasterDpi)
            ) + xlab("UMAP1") + ylab("UMAP2"
            ) + theme_bw(
            )  +  theme(
                axis.text.y   = element_text(size=8),
                axis.text.x   = element_text(size=8),
                axis.title.y  = element_text(size=8),
                axis.title.x  = element_text(size=8),
                axis.line = element_line(colour = "black"),
                panel.border = element_rect(colour = "black", fill=NA, size=1),
                plot.title = element_text(hjust = 0.5, size = 12),
                legend.title = element_blank()
            ) + guides(col = guide_legend(override.aes = list(shape = 16, size = legendDotSize))
            ) + ggtitle(paste0("Sample: ", tag)
            ) + xlim(minX, maxX) + ylim(minY, maxY
            ) + coord_fixed(ratio=1
            ) 
            
if (length(unique(dfPlot$Cluster)) > 15){
   plotList[[tag]] <- plotList[[tag]] + theme(legend.position = "none")
}
            FNbase <- paste0(tag, VersionPdfExt)
            FN <- paste0(Obio@parameterList$reportFigDir, FNbase)
            FNrel <- paste0("report_figures/", FNbase)
            
            pdf(FN)
                print(plotList[[tag]])
            dev.off()
            
            if (exists("shinyURL") & !is.null(shinyURL)){
            link <- paste0(
              'An interactive version of this figure with additional viewing options can be found <a href="',shinyURL,'?_inputs_&y_axis=%22UMAP_2%22&x_axis=%22UMAP_1%22&colorBy=%22Phase%22&splitByColumn=%22all%22" target="_blank">here</a>. '
            )
            
            } else {
              link <- ""
            }
            
            figLegend <- paste0(
                '**Figure ', 
                figureCount, 
                ':** ',
                ' UMAP showing all cells from all samples together with the estimated cell-cycle phase color-coded. Download a pdf of this figure <a href="',FNrel,'" target="_blank">here</a>. ',
                link
            )
            
            figureCount <- figureCount + 1
            
            NewChnk <- paste0(
                "#### ", tag,
                "\n```{r CC_UMAP_",
                tag,", results='asis', echo=F, eval=TRUE, warning=FALSE, fig.cap='",
                figLegend,"'}\n",
                "\n",
                "\n print(plotList[['",tag,"']])",
                "\n cat(  '\n')",
                "\n\n\n```\n"   
            )
            
            chnkVec <- c(
                chnkVec,
                NewChnk
            )


## Done first umap all samples                                               ##
###############################################################################
            
###############################################################################
## First tsne all samples together                                           ##
tag <- paste0("tSNE_All_Samples")
dfPlot <- OsC@meta.data
pos <- grep("included", names(dfPlot))
if (length(pos) == 0){
  dfPlot[["included"]] <- "+"
}
dfPlot[["cellID"]] <- row.names(dfPlot)
dfPlot$tSNE_1 <- NULL
dfPlot$tSNE_2 <- NULL
            
## Get tsNE coordinates ##
coord <- data.frame(OsC@reductions$tsne@cell.embeddings)
coord[["cellID"]] <- row.names(coord)
coord <-coord[coord$cellID %in% dfPlot$cellID, ]
            
dfPlot <- merge(dfPlot, coord, by.x = "cellID", by.y="cellID", all=T)
dfPlot[is.na(dfPlot)] <- 0
dfPlot <- dfPlot[dfPlot$tSNE_1 != 0 & dfPlot$tSNE_2 != 0,]
            
            
## Add cluster colors ##
#dfPlot[["Cluster"]] <- paste0("C", dfPlot$seurat_clusters)
#clusterVec <- as.vector(paste0("C", unique(sort(dfPlot$seurat_clusters))))

maxX <- 1.1*max(dfPlot$tSNE_1, na.rm = T)
minX <- 1.1*min(dfPlot$tSNE_1, na.rm = T)
maxY <- 1.1*max(dfPlot$tSNE_2, na.rm = T)
minY <- 1.1*min(dfPlot$tSNE_2, na.rm = T)            

#library(scales)
#clusterCols = hue_pal()(length(clusterVec))
#dfPlot$Cluster <- factor(dfPlot$Cluster, levels = clusterVec)

# dotsize  = 1.5
# if (nrow(dfPlot) > 10000){
#   dotsize  = 0.75
# } else if (nrow(dfPlot) > 50000){
#   dotsize = 0.5
# } else {
#   dotsize = 0.25
# }

plotList[[tag]] <- ggplot(data=dfPlot[dfPlot$included == "+",], aes(tSNE_1, tSNE_2, color=Phase)
            ) + ggrastr::rasterize(ggplot2::geom_point( shape=16, size = as.numeric(dotsize), dpi = rasterDpi)
            ) + xlab("tSNE1") + ylab("tSNE2"
            ) + theme_bw(
            )  +  theme(
                axis.text.y   = element_text(size=8),
                axis.text.x   = element_text(size=8),
                axis.title.y  = element_text(size=8),
                axis.title.x  = element_text(size=8),
                axis.line = element_line(colour = "black"),
                panel.border = element_rect(colour = "black", fill=NA, size=1),
                plot.title = element_text(hjust = 0.5, size = 12),
                legend.title = element_blank()
            ) + guides(col = guide_legend(override.aes = list(shape = 16, size = legendDotSize))
            ) + ggtitle(paste0("Sample: ", tag)
            ) + xlim(minX, maxX) + ylim(minY, maxY
            ) + coord_fixed(ratio=1
            ) 
            
if (length(unique(dfPlot$Cluster)) > 15){
   plotList[[tag]] <- plotList[[tag]] + theme(legend.position = "none")
}
            FNbase <- paste0(tag, VersionPdfExt)
            FN <- paste0(Obio@parameterList$reportFigDir, FNbase)
            FNrel <- paste0("report_figures/", FNbase)
            
            pdf(FN)
                print(plotList[[tag]])
            dev.off()
            
            if (exists("shinyURL") & !is.null(shinyURL)){
            link <- paste0(
              'An interactive version of this figure with additional viewing options can be found <a href="',shinyURL,'?_inputs_&y_axis=%22tSNE_2%22&x_axis=%22tSNE_1%22&colorBy=%22Phase%22&splitByColumn=%22all%22" target="_blank">here</a>. '
            )
            
            } else {
              link <- ""
            }
            
            figLegend <- paste0(
                '**Figure ', 
                figureCount, 
                ':** ',
                ' tSNE showing all cells from all samples together. The esimated cell-cycle phase is color coded. Download a pdf of this figure <a href="',FNrel,'" target="_blank">here</a>. ',
                link
            )
            
            figureCount <- figureCount + 1
            
            NewChnk <- paste0(
                "#### ", tag,
                "\n```{r CC_tSNE_",
                tag,", results='asis', echo=F, eval=TRUE, warning=FALSE, fig.cap='",
                figLegend,"'}\n",
                "\n",
                "\n print(plotList[['",tag,"']])",
                "\n cat(  '\n')",
                "\n\n\n```\n"   
            )
            
            chnkVec <- c(
                chnkVec,
                NewChnk
            )


## Done first tsne all samples                                               ##
###############################################################################            
###############################################################################
## Make one UMAP plot per sample                                             ##

sampleVec <- sort(unique(OsC@meta.data$sampleID))

dfPlot <- OsC@meta.data
pos <- grep("included", names(dfPlot))
if (length(pos) == 0){
  dfPlot[["included"]] <- "+"
}
dfPlot[["cellID"]] <- row.names(dfPlot)
            
## Get UMAP coordinates ##
coord <- data.frame(OsC@reductions$umap@cell.embeddings)
coord[["cellID"]] <- row.names(coord)
coord <-coord[coord$cellID %in% dfPlot$cellID, ]
dfPlot$UMAP_1 <- NULL
dfPlot$UMAP_2 <- NULL
            
dfPlot <- merge(dfPlot, coord, by.x = "cellID", by.y="cellID", all=T)
dfPlot[is.na(dfPlot)] <- 0
dfPlot <- dfPlot[dfPlot$UMAP_1 != 0 & dfPlot$UMAP_2 != 0,]
            
            
## Add cluster colors ##
#dfPlot[["Cluster"]] <- paste0("C", dfPlot$seurat_clusters)
#clusterVec <- as.vector(paste0("C", unique(sort(dfPlot$seurat_clusters))))
            
#library(scales)
#clusterCols = hue_pal()(length(clusterVec))
            
#dfPlot$Cluster <- factor(dfPlot$Cluster, levels = clusterVec)            
            
maxX <- 1.1*max(dfPlot$UMAP_1, na.rm = T)
minX <- 1.1*min(dfPlot$UMAP_1, na.rm = T)
maxY <- 1.1*max(dfPlot$UMAP_2, na.rm = T)
minY <- 1.1*min(dfPlot$UMAP_2, na.rm = T)               
                                   
for (i in 1:length(sampleVec)){
    tag <- paste0("UMAP_CC_plot_by_", sampleVec[i])
    
    dfPlotSel <- dfPlot[dfPlot$sampleID == sampleVec[i], ]
            
            
            
    plotList[[tag]] <- ggplot(data=dfPlotSel[dfPlot$included == "+",], aes(UMAP_1, UMAP_2, color=Phase)
            ) + ggrastr::rasterize(ggplot2::geom_point( shape=16, size = as.numeric(dotsize), dpi=rasterDpi)
            ) + xlab("UMAP1") + ylab("UMAP2"
            ) + theme_bw(
            )  +  theme(
                axis.text.y   = element_text(size=8),
                axis.text.x   = element_text(size=8),
                axis.title.y  = element_text(size=8),
                axis.title.x  = element_text(size=8),
                axis.line = element_line(colour = "black"),
                panel.border = element_rect(colour = "black", fill=NA, size=1),
                plot.title = element_text(hjust = 0.5, size = 12),
                legend.title = element_blank()
            ) + guides(col = guide_legend(override.aes = list(shape = 16, size = legendDotSize))
            ) + ggtitle(paste0("Sample: ", tag)
            ) + xlim(minX, maxX) + ylim(minY, maxY
            ) + coord_fixed(ratio=1
            ) 
    
    if (length(unique(dfPlot$Cluster)) > 15){
   plotList[[tag]] <- plotList[[tag]] + theme(legend.position = "none")
}
            
            FNbase <- paste0(tag, VersionPdfExt)
            FN <- paste0(Obio@parameterList$reportFigDir, FNbase)
            FNrel <- paste0("report_figures/", FNbase)
            
            pdf(FN)
                print(plotList[[tag]])
            dev.off()
            
            if (exists("shinyURL") & !is.null(shinyURL)){
            link <- paste0(
              'An interactive version of this figure with additional viewing options can be found <a href="',shinyURL,'?_inputs_&y_axis=%22UMAP_2%22&x_axis=%22UMAP_1%22&colorBy=%22Phase%22&splitByColumn=%22sampleName%22" target="_blank">here</a>. '
            )
            
            } else {
              link <- ""
            }
            
            figLegend <- paste0(
                '**Figure ', 
                figureCount, 
                ':** ',
                ' Sample-level UMAPs. Estimated cell-cylce phase color-coded. Download a pdf of this figure <a href="',FNrel,'" target="_blank">here</a>. ',
                link
            )
            
            figureCount <- figureCount + 1
            
            NewChnk <- paste0(
                paste("#### ", tag),
                "\n```{r CC_UMAP_",
                tag,", results='asis', echo=F, eval=TRUE, warning=FALSE, fig.cap='",
                figLegend,"'}\n",
                "\n",
                "\n print(plotList[['",tag,"']])",
                "\n cat(  '\n')",
                "\n\n\n```\n"   
            )
            
            chnkVec <- c(
                chnkVec,
                NewChnk
            )
            
            
    
    
    
    
}

## Done making one umap plot per sample                                      ##
###############################################################################


###############################################################################
## Add cluster dendrogram by sample                                          ##

if (length(unique(OsC@meta.data$sampleID)) > 3){
  library(ggtree)
  Idents(OsC) <- "sampleName"
  OsC <- BuildClusterTree(OsC)
      
  tag <- paste0("Sample_Dendrogram")
      
  OsC@tools$BuildClusterTree$tip.label <- paste0( OsC@tools$BuildClusterTree$tip.label)
      
  plotList[[tag]]  <- ggplot(OsC@tools$BuildClusterTree
      ) + geom_tree(
      ) + theme_tree(
      ) 
  h <- sum(c("sampleName", "sampleColor") %in% OsC@meta.data)
  if (h ==2){
    dfCol <- unique(OsC@meta.data[,c("sampleName", "sampleColor")])
    colVec <- as.vector(dfCol$sampleColor)
    names(colVec) <- as.vector(dfCol$sampleName)
    plotList[[tag]] <- plotList[[tag]] + geom_tiplab(color=colVec
      ) 
  } else {
    plotList[[tag]] <- plotList[[tag]] + geom_tiplab(
      )   
  }
  
  
  plotList[[tag]] <- plotList[[tag]] + labs(title=tag
      ) + theme(
        panel.border = element_rect(colour = "black", fill=NA, size=1),
        axis.title.x=element_blank(),
        plot.title = element_text(hjust = 0.5, size = 12)
      )  + xlim(0,dendrofactor*max(OsC@tools$BuildClusterTree[[2]]))
 
      
  ## Save to file ##
  FNbase <- paste0(tag,".", VersionPdfExt)
  FN <- paste0(Obio@parameterList$reportFigDir, FNbase)
  FNrel <- paste0("report_figures/", FNbase)
      
  pdf(FN)
      print(plotList[[tag]])
  dev.off()
      
  figLegend <- paste0(
      '**Figure ', 
          figureCount, 
          ':** ',
          ' Clusterplot dendrogram by sample ID. ','A pdf of this figure can be downloaded <a href="',FNrel,'", target="_blank>here</a>.'
      )
      
      
      NewChnk <- paste0(
          "#### SampleID Dendrogram",
          "\n```{r ", tag, "results='asis', echo=F, eval=TRUE, warning=FALSE, fig.cap='",
          figLegend,"'}\n",
          "\n",
          "\n print(plotList[['",tag,"']])",
          "\n cat(  '\n')",
          "\n\n\n```\n"   
      )
      
      chnkVec <- c(
          chnkVec,
          NewChnk
      )
      
      
      figureCount <- figureCount + 1
}

## Done by sample                                                            ##
###############################################################################
            
###############################################################################
## Add cluster dendrogram by cluster                                         ##
library(ggtree)
Idents(OsC) <- "clusterName"
OsC <- BuildClusterTree(OsC)
    
tag <- paste0("Cluster_Dendrogram")
    
OsC@tools$BuildClusterTree$tip.label <- paste0("C", OsC@tools$BuildClusterTree$tip.label)
    
plotList[[tag]]  <- ggplot(OsC@tools$BuildClusterTree
    ) + geom_tree(
    ) + theme_tree(
    ) 

h <- sum(c("clusterName", "clusterColor") %in% names(OsC@meta.data))
if (h ==2){
    dfCol <- unique(OsC@meta.data[,c("clusterName", "clusterColor")])
    colVec <- as.vector(dfCol$clusterColor)
    names(colVec) <- as.vector(dfCol$clusterName)
    plotList[[tag]] <- plotList[[tag]] + geom_tiplab(color=colVec
    ) 
} else {
    plotList[[tag]] <- plotList[[tag]] + geom_tiplab(
    )   
}



plotList[[tag]] <- plotList[[tag]] + labs(title=tag
    ) + theme(
      panel.border = element_rect(colour = "black", fill=NA, size=1),
      axis.title.x=element_blank(),
      plot.title = element_text(hjust = 0.5, size = 12)
    )  + xlim(0,dendrofactor*max(OsC@tools$BuildClusterTree[[2]]))
    
    #+ xlim(-1,1.2*max(OsC@tools$BuildClusterTree$edge)) 
    
    
## Save to file ##
FNbase <- paste0(tag,".", VersionPdfExt)
FN <- paste0(Obio@parameterList$reportFigDir, FNbase)
FNrel <- paste0("report_figures/", FNbase)
    
pdf(FN)
    print(plotList[[tag]])
dev.off()
    
figLegend <- paste0(
    '**Figure ', 
        figureCount, 
        ':** ',
        ' Clusterplot dendrogram. ','A pdf of this figure can be downloaded <a href="',FNrel,'" target="_blank">here</a>.'
    )
    
    
    NewChnk <- paste0(
        "#### Cluster Dendrogram",
        "\n```{r ", tag, "results='asis', echo=F, eval=TRUE, warning=FALSE, fig.cap='",
        figLegend,"'}\n",
        "\n",
        "\n print(plotList[['",tag,"']])",
        "\n cat(  '\n')",
        "\n\n\n```\n"   
    )
    
    chnkVec <- c(
        chnkVec,
        NewChnk
    )
    
    
    figureCount <- figureCount + 1

## Done integraed analysis                                                   ##
###############################################################################

if (length(plotList) > 3){
    tabVar <- ".tabset .tabset-fade .tabset-dropdown"
} else {
    tabVar <- ".tabset .tabset-fade .tabset-pills"
}


```

### Cell Cycle Markers {`r tabVar`}

```{r Plot_dim_red_by_cell_cycle_phase, echo=TRUE, eval=TRUE, warning=FALSE, results="asis"} 

cat(paste(knit(text = chnkVec, quiet = T), collapse = '\n'))

```