<!-- Set PArameters Module -->
<!-- Set the chnkPrefix to make all chunks unique in the overall folder -->
```{r create_sankey_init, echo=TRUE, eval=TRUE, warning=FALSE}
chnkPrefix <- "B134.Barchart."
VersionPdfExt <- VersionPdfExt <- paste0(".",chnkPrefix,"V", gsub("-", "", Sys.Date()), ".pdf")

```



```{r, echo=TRUE, eval=TRUE, warning=FALSE, results=F}


###############################################################################
## This part will allow to just render this chapter                          ##

## Set renderChapter = TRUE if you want individual chapters to be processed
if (!exists("renderChapter")){
    renderChapter <- FALSE
}

# renderChapter <- TRUE

## Load Obio biologic object and OsC single-cell object for renderByChapter mode
if (renderChapter){
      
      ## Load biologic object
      source("load.biologic.robj.R")
  
      ## Load Seurat object
      SeuratFN <- paste0(Obio@parameterList$localWorkDir,list.files(Obio@parameterList$localWorkDir)[grep(".Seurat.Robj", list.files(Obio@parameterList$localWorkDir))])
      
      load(SeuratFN)
}

## All data for this chapter loaded                                          ##
###############################################################################

## Set sampleIDorder
## Give the order in which sampleIDs should be displayed
sampleIDorder <- Obio@parameterList$sampleNameOrder
sampleNameOrder <- rev(Obio@parameterList$sampleNameOrder)

dfOrder <- OsC@meta.data %>% 
  dplyr::distinct(sampleName, sampleID)  %>% 
  magrittr::set_rownames(.$sampleID)

dfOrder <- dfOrder[sampleIDorder,]



## Define cluster order
## Can be set manually. Make sure all clusters are present
clusterOrder <- rev(Obio@parameterList$clusterNameOrder)

project_id <- Obio@parameterList$project_id
## If you work outside of the biologic framework, set the projectID maually. 
## It can be any string

## Set table output directory
reportTableDir <- Obio@parameterList$reportTableDir
## set the directory manually if you're working outside the biologic framework. 
## Make sure that the last character is a "/"

## Set table output directory
reportFigDir <- Obio@parameterList$reportFigDir
## set the directory manually if you're working outside the biologic framework. 
## Make sure that the last character is a "/"

## Make sure the directory exists
if (!dir.exists(reportTableDir)){
    dir.create(reportTableDir, recursive = T)
}

## set figure count variable, if it doesent exists already
if (!exists("figureCount")){
    figureCount <- 1
}

```


```{r, echo=TRUE, eval=TRUE, warning=FALSE, results="asis"}
###############################################################################
## Create datatable for plotting                                             ##
library(dplyr)


## This plotting procedure requires three sets: the sets cellTypeIDs, clusterIDs, cellTypeIDs
## level1ID, level2ID, level3ID
selCol <- "meta_Treatment"

pos <- grep(selCol, names(OsC@meta.data))

if (length(pos) != 1){
  selCol <- "sampleName"
}

dfCluster <- OsC@meta.data %>% 
    dplyr::distinct(clusterName, clusterColor) %>% 
    magrittr::set_rownames(.$clusterName)

dfCluster <- dfCluster[Obio@parameterList$clusterNameOrder,]


colVec <- dfCluster$clusterColor

clusterIDs <- unique(OsC@meta.data[,"clusterName"])

if (length(grep("cellIdent", names(OsC@meta.data))) == 0){
    OsC@meta.data[["cellIdent"]] <- "All"
}

cellTypeIDs <- unique(OsC@meta.data[,"cellIdent"])

dfTemp <- OsC@meta.data

if (length(grep("^cellIdent$", names(dfTemp))) == 0){
    dfTemp[["cellIdent"]] <- "All"
}

dfTemp$cellIdent <- dfTemp$meta_Treatment


## Make Ncell barchart
plotList <- list()
chnkVec <- as.vector(NULL, mode="character")
clusterNameOrder <- Obio@parameterList$clusterNameOrder

clusterNameOrder <- clusterNameOrder[clusterNameOrder %in% unique(dfTemp$clusterName)]
dfTemp$clusterName <- factor(dfTemp$clusterName, levels = clusterNameOrder)

tag <- "Cluster_Barchart_Ncells"
plotList[[tag]] <- ggplot2::ggplot(data=dfTemp, ggplot2::aes(x=meta_Treatment, fill=clusterName)) + ggplot2::geom_bar() + 
ggplot2::labs(title=paste0("Cells per Treatment"), x="", y = "Counts") + 
ggplot2::theme_bw() +  
ggplot2::theme(
  panel.border = ggplot2::element_rect(colour = "black", fill=NA, size=1),
  plot.title = ggplot2::element_text(hjust = 0.5, size = 12)
) 
plotList[[tag]] <- plotList[[tag]] + 
      ggplot2::guides(fill= ggplot2::guide_legend(title="Clusters"))
  
    h <- sum(c("clusterName", "clusterColor") %in% names(OsC@meta.data))
    if (h ==2){
        dfCol <- unique(OsC@meta.data[,c("clusterName", "clusterColor")])
        row.names(dfCol) <- dfCol$clusterName
        dfCol <- dfCol[clusterNameOrder, ]
        
        dfCol <- dfCol[dfCol$clusterName %in% unique(dfTemp$clusterName), ]
        colVec <- as.vector(dfCol$clusterColor)
        names(colVec) <- as.vector(dfCol$clusterName)
        colVec <- rev(colVec)
        
        plotList[[tag]] <- plotList[[tag]] + ggplot2::scale_fill_manual("Clusters" ,values = colVec
        ) 
    }

###########################################################################
## Save plot to file                                                     ##
FNbase <- paste0(tag,".Ncells", VersionPdfExt)
FN <- paste0(reportFigDir, FNbase)
FNrel <- paste0("report_figures/", FNbase)

pdf(FN)
  print(plotList[[tag]])
dev.off()
##                                                                       ##
###########################################################################
figCap <- paste0(
    '**Figure ',
    figureCount,
    ':** Percentages of cells in each treatment group by cluster.',
    'Download a pdf of this figure <a href="',FNrel,'" target="_blank">here</a>. '
)

NewChnk <- paste0(
paste0("#### ", tag),
    "\n```{r Barchart-",tag,", results='asis', echo=F, eval=TRUE, warning=FALSE, fig.cap='",figCap,"'}\n",
    "\n",
    "\n print(plotList[['",tag,"']])",
    "\n cat(  '\n')",
    "\n\n\n```\n"   
)

chnkVec <- c(
    chnkVec,
    NewChnk
)
    
## Percentage
    

tag <- "Cluster_Barchart_Percent"
plotList[[tag]] <- ggplot2::ggplot(data=dfTemp, ggplot2::aes(x=meta_Treatment, fill=clusterName)) + ggplot2::geom_bar(position = "fill") + 
ggplot2::labs(title=paste0("Percent Cells per Treatment"), x="", y = "Percent") + 
ggplot2::theme_bw() +  
ggplot2::theme(
  panel.border = ggplot2::element_rect(colour = "black", fill=NA, size=1),
  plot.title = ggplot2::element_text(hjust = 0.5, size = 12)
) 
plotList[[tag]] <- plotList[[tag]] + 
      ggplot2::guides(fill= ggplot2::guide_legend(title="Clusters"))
  
    h <- sum(c("clusterName", "clusterColor") %in% names(OsC@meta.data))
    if (h ==2){
        dfCol <- unique(OsC@meta.data[,c("clusterName", "clusterColor")])
        row.names(dfCol) <- dfCol$clusterName
        dfCol <- dfCol[clusterNameOrder, ]
        
        dfCol <- dfCol[dfCol$clusterName %in% unique(dfTemp$clusterName), ]
        colVec <- as.vector(dfCol$clusterColor)
        names(colVec) <- as.vector(dfCol$clusterName)
        colVec <- rev(colVec)
        
        plotList[[tag]] <- plotList[[tag]] + ggplot2::scale_fill_manual("Clusters" ,values = colVec
        ) 
    }
    

###########################################################################
## Save plot to file                                                     ##
    FNbase <- paste0(tag,".Ncells", VersionPdfExt)
    FN <- paste0(reportFigDir, FNbase)
    FNrel <- paste0("report_figures/", FNbase)
    
    pdf(FN)
      print(plotList[[tag]])
    dev.off()
##                                                                       ##
###########################################################################

figCap <- paste0(
    '**Figure ',
    figureCount,
    ':** Percentages of cells in each treatment group by cluster.',
    'Download a pdf of this figure <a href="',FNrel,'" target="_blank">here</a>. '
)

NewChnk <- paste0(
paste0("#### ", tag),
    "\n```{r Barchart-",tag,", results='asis', echo=F, eval=TRUE, warning=FALSE, fig.cap='",figCap,"'}\n",
    "\n",
    "\n print(plotList[['",tag,"']])",
    "\n cat(  '\n')",
    "\n\n\n```\n"   
)

chnkVec <- c(
    chnkVec,
    NewChnk
)
## Done adding                                                             ##
#############################################################################
            
    
## Done barchart                                                             ##
###############################################################################


if (length(plotList) > 3){
    tabVar <- ".tabset .tabset-fade .tabset-dropdown"
} else {
    tabVar <- ".tabset .tabset-fade .tabset-pills"
}

```

### Barchart N cells and Percent in Clusters {`r tabVar`}
if you could prepare a bar-shape graph with the %of cells clusters representing our populations (like in the Nat Med)

```{r plot_barchart, echo=TRUE, eval=TRUE, warning=FALSE, results="asis"}
cat(paste(knitr::knit(text = chnkVec, quiet = T), collapse = '\n'))
```
