<!-- Set Parameters Module -->
<!-- Set the chnkPrefix to make all chunks unique in the overall folder -->
```{r partT_ouija_init, echo=TRUE, eval=TRUE, warning=FALSE}
chnkPrefix <- "T4.ouija."
VersionPdfExt <- VersionPdfExt <- paste0(".",chnkPrefix,"V", gsub("-", "", Sys.Date()), ".pdf")

Sys.setenv(DOWNLOAD_STATIC_LIBV8 = 1)
#renv::install("V8")
renv::install("kieranrcampbell/ouija")

invertOuijaPseudotime <- TRUE
useCachedOuijaObject <- TRUE

```



```{r ouija_genes, eval=TRUE, echo=F, results=F}

earlySwitch <- c("VCAM1", "CTGF", "THY1", "IGFBP4")
earlySwitch <- earlySwitch[earlySwitch %in% row.names(OsC)]

lateSwitch <- c("HOPX", "IVL", "FLG", "SPINK5")
lateSwitch <- lateSwitch[lateSwitch %in% row.names(OsC)]

transient <- c("CDH1", "EPCAM", "CLDN7")
transient <- transient[transient %in% row.names(OsC)]


response_type <- c(
    rep("switch", length(earlySwitch) + length(lateSwitch)), 
    rep("transient", length(transient))
)

allMarkers <- unique(
    c(
        earlySwitch,
        lateSwitch,
        transient
    )
)

## prepare matrix ##
OsC_subL1 <- OsC
OsC_subL1 <- subset(OsC_subL1, features = allMarkers)
dfMat <- data.matrix(OsC_subL1@assays[["RNA"]]@data)
dfTmat <- data.matrix(t(dfMat))
#dfTmat <- dfTmat[sample(row.names(dfTmat), 5000),]

## Make sure no row has zero counts ##
selVec  <- (colSums(dfTmat) > 0)
dfTmat <- dfTmat[,selVec]
response_type <- response_type[selVec]



# library(rslurm)
# sjob <- slurm_apply(test_func, pars, jobname = 'test_apply',
#                     nodes = 2, cpus_per_node = 2, submit = FALSE)

pos <- grep(".Ouija.Robj", list.files(tempWorkDir))
objectLoaded <- FALSE

options(mc.cores = parallel::detectCores())


if (length(pos) == 1 && useCachedOuijaObject){
    OuijaFN <- paste0(
        tempWorkDir, "/", 
        list.files(tempWorkDir)[grep(".Ouija.Robj", list.files(tempWorkDir))]
    )
    load(OuijaFN)
    objectLoaded <- TRUE
}

if (!objectLoaded) {
    nIter = 500
    ouija.mode <- "vb"
    oui <- ouija::ouija(
        dfTmat, 
        response_type, 
        inference_type = ouija.mode,  # is orders of magnitude faster than hmc
        iter = nIter # ideal 4000
    )
    
    OuijaFN <- paste0(Obio@parameterList$project_id, "_nIter", nIter, "_mode_", ouija.mode, "Ouija.Robj")
    save(oui, 
        file = paste0(
            Obio@parameterList$localWorkDir,
            Obio@parameterList$project_id,
            "_nIter", nIter, "_mode_", ouija.mode, "Ouija.Robj"
        )
    )
}




Ouija_Pseudotime <- ouija::map_pseudotime(oui)

if (invertOuijaPseudotime){
    Ouija_Pseudotime <- (1 - Ouija_Pseudotime)
}

Ouija_Switchtime <- ouija::switch_times(oui) # MAP switch times
Ouija_Peaktime <- ouija::peak_times(oui) # MAP peak times
Ouija_SwitchStrength <-  ouija::switch_strengths(oui) # MAP switch strengths

dfRes <- data.frame(
    cellID = row.names(dfTmat),
    Ouija_Pseudotime
)

row.names(dfRes) <- dfRes$cellID
dfRes$cellID <- NULL

OsC <- biologicToolsSC::addDf2seuratMetaData(
    OsC, 
    dfRes
)

save(OsC,
    file = paste0(
         Obio@parameterList$localWorkDir,
         Obio@parameterList$project_id,
        ".Seurat.Robj"
     )
)


###############################################################################
## Gene Regs Table                                                           ##

gene_regs <- ouija::gene_regulation(oui)
#head(gene_regs)

##                                                                           ##
###############################################################################

###############################################################################
## Init Plot Collection                                                      ##

plotList <- list()
chnkVec <- as.vector(NULL, mode = "character")

## Done                                                                      ##
###############################################################################


###############################################################################
## Diagnostic plot 1                                                         ##
# We can plot the gene expression over pseudotime along with the maximum a posteriori (MAP) estimates of the mean function (the sigmoid or Gaussian transient function) using the plot_expression function:

tag <- "Ouija_Expression"

plotList[[tag]] <- ouija::plot_expression(oui) + ggplot2::theme_bw(
    ) +  ggplot2::theme(
         axis.text.y   = ggplot2::element_text(size=8),
         axis.text.x   = ggplot2::element_text(size=8),
         axis.title.y  = ggplot2::element_text(size=8),
         axis.title.x  = ggplot2::element_text(size=8),
         axis.line = ggplot2::element_line(colour = "black"),
         panel.border = ggplot2::element_rect(colour = "black", fill=NA, size=1),
         plot.title = ggplot2::element_text(hjust = 0.5, size = 12)
    )


## Save to file ##
FNbase <- paste0(tag, VersionPdfExt)
FN <- paste0(Obio@parameterList$reportFigDir, FNbase)
FNrel <- paste0("report_figures/", FNbase)


pdf(FN)
    print(plotList[[tag]])
dev.off()



## Create R markdown chunk ##
figLegend <- paste0(
    '**Figure ', 
    figureCount, 
    '**: We can plot the gene expression over pseudotime along with the maximum a posteriori (MAP) estimates of the mean function (the sigmoid or Gaussian transient function)',
    '. Download a pdf of this figure <a href="',FNrel,'" target="_blank">here</a>. '
)
figureCount <- figureCount + 1 

NewChnk <- paste0(
    "\n#### ", tag, 
    "\n```{r ", tag, ", results='asis', echo=F, eval=TRUE, warning=FALSE, fig.cap='",
    figLegend,"'}\n",
    "\n",
    "\n print(plotList[['",tag,"']])",
    "\n cat(  '\n')",
    "\n\n\n```\n"   
)

chnkVec <- c(
    chnkVec,
    NewChnk
)



##                                                                           ##
###############################################################################

###############################################################################
## Diagnostic plot 2                                                         ##
# We can plot the gene expression over pseudotime along with the maximum a posteriori (MAP) estimates of the mean function (the sigmoid or Gaussian transient function) using the plot_expression function:

# tag <- "Ouija_Diagnostic"
# 
# plotList[[tag]] <- ouija::plot_diagnostics(oui) + ggplot2::theme_bw(
#     ) +  ggplot2::theme(
#          axis.text.y   = ggplot2::element_text(size=8),
#          axis.text.x   = ggplot2::element_text(size=8),
#          axis.title.y  = ggplot2::element_text(size=8),
#          axis.title.x  = ggplot2::element_text(size=8),
#          axis.line = ggplot2::element_line(colour = "black"),
#          panel.border = ggplot2::element_rect(colour = "black", fill=NA, size=1),
#          plot.title = ggplot2::element_text(hjust = 0.5, size = 12)
#     )
# 
# 
# ## Save to file ##
# FNbase <- paste0(tag, VersionPdfExt)
# FN <- paste0(Obio@parameterList$reportFigDir, FNbase)
# FNrel <- paste0("report_figures/", FNbase)
# 
# 
# pdf(FN)
#     print(plotList[[tag]])
# dev.off()
# 
# 
# 
# ## Create R markdown chunk ##
# figLegend <- paste0(
#     '**Figure ', 
#     figureCount, 
#     '**: It’s good practice to look at the trace and aurocorrelation of the (log)-likelihood to make sure the distribution has (roughly) converged.'
# )
# figureCount <- figureCount + 1 
# 
# NewChnk <- paste0(
#     "\n#### ", tag, 
#     "\n```{r ", tag, ", results='asis', echo=F, eval=TRUE, warning=FALSE, fig.cap='",
#     figLegend,"'}\n",
#     "\n",
#     "\n print(plotList[['",tag,"']])",
#     "\n cat(  '\n')",
#     "\n\n\n```\n"   
# )
# 
# chnkVec <- c(
#     chnkVec,
#     NewChnk
# )



##                                                                           ##
###############################################################################

###############################################################################
## Diagnostic plot 3                                                         ##
# We can also visualise when in the trajectory gene regulation behaviour occurs, either in the form of the switch time or the peak time (for switch-like or transient genes) using the plot_switch_times and plot_transient_times functions:

tag <- "Ouija_Switch_Times"

plotList[[tag]] <- ouija::plot_switch_times(oui) + ggplot2::theme_bw(
    ) +  ggplot2::theme(
         axis.text.y   = ggplot2::element_text(size=8),
         axis.text.x   = ggplot2::element_text(size=8),
         axis.title.y  = ggplot2::element_text(size=8),
         axis.title.x  = ggplot2::element_text(size=8),
         axis.line = ggplot2::element_line(colour = "black"),
         panel.border = ggplot2::element_rect(colour = "black", fill=NA, size=1),
         plot.title = ggplot2::element_text(hjust = 0.5, size = 12)
    )


## Save to file ##
FNbase <- paste0(tag, VersionPdfExt)
FN <- paste0(Obio@parameterList$reportFigDir, FNbase)
FNrel <- paste0("report_figures/", FNbase)


pdf(FN)
    print(plotList[[tag]])
dev.off()



## Create R markdown chunk ##
figLegend <- paste0(
    '**Figure ', 
    figureCount, 
    '**: We can also visualise when in the trajectory gene regulation behaviour occurs, either in the form of the switch time or the peak time (for switch-like or transient genes).',
    '. Download a pdf of this figure <a href="',FNrel,'" target="_blank">here</a>. '
)
figureCount <- figureCount + 1 

NewChnk <- paste0(
    "\n#### ", tag, 
    "\n```{r ", tag, ", results='asis', echo=F, eval=TRUE, warning=FALSE, fig.cap='",
    figLegend,"'}\n",
    "\n",
    "\n print(plotList[['",tag,"']])",
    "\n cat(  '\n')",
    "\n\n\n```\n"   
)

chnkVec <- c(
    chnkVec,
    NewChnk
)



##                                                                           ##
###############################################################################


###############################################################################
## Diagnostic plot 4                                                         ##
# We can also visualise when in the trajectory gene regulation behaviour occurs, either in the form of the switch time or the peak time (for switch-like or transient genes) using the plot_switch_times and plot_transient_times functions:

tag <- "Ouija_Peak_Times"

plotList[[tag]] <- ouija::plot_peak_times(oui) + ggplot2::theme_bw(
    ) +  ggplot2::theme(
         axis.text.y   = ggplot2::element_text(size=8),
         axis.text.x   = ggplot2::element_text(size=8),
         axis.title.y  = ggplot2::element_text(size=8),
         axis.title.x  = ggplot2::element_text(size=8),
         axis.line = ggplot2::element_line(colour = "black"),
         panel.border = ggplot2::element_rect(colour = "black", fill=NA, size=1),
         plot.title = ggplot2::element_text(hjust = 0.5, size = 12)
    )


## Save to file ##
FNbase <- paste0(tag, VersionPdfExt)
FN <- paste0(Obio@parameterList$reportFigDir, FNbase)
FNrel <- paste0("report_figures/", FNbase)


pdf(FN)
    print(plotList[[tag]])
dev.off()



## Create R markdown chunk ##
figLegend <- paste0(
    '**Figure ', 
    figureCount, 
    '**: We can also visualise when in the trajectory gene regulation behaviour occurs, either in the form of the switch time or the peak time (for switch-like or transient genes).',
    '. Download a pdf of this figure <a href="',FNrel,'" target="_blank">here</a>. '
)
figureCount <- figureCount + 1 

NewChnk <- paste0(
    "\n#### ", tag, 
    "\n```{r ", tag, ", results='asis', echo=F, eval=TRUE, warning=FALSE, fig.cap='",
    figLegend,"'}\n",
    "\n",
    "\n print(plotList[['",tag,"']])",
    "\n cat(  '\n')",
    "\n\n\n```\n"   
)

chnkVec <- c(
    chnkVec,
    NewChnk
)



##                                                                           ##
###############################################################################


###############################################################################
##                                                                           ##
# This step consumes a lot of time
# cmo <- consistency_matrix(oui)

# pdf("../temp4.consistency.matrix.pdf")
# plot_consistency(oui)
# dev.off()
##                                                                           ##
## cell_classifications <- cluster_consistency(cmo)
# map_pst <- map_pseudotime(oui)
# df_class <- data.frame(map_pst, cell_classifications)
# 
# pdf("../temp5.cell.classifications.pdf")
# ggplot(df_class, aes(x = map_pst, y = cell_classifications)) +
#   geom_point() +
#   xlab("MAP pseudotime") +
#   ylab("Cell classification")
# dev.off()
###############################################################################
if (length(plotList) > 3){
    tabVar <- ".tabset .tabset-fade .tabset-dropdown"
} else {
    tabVar <- ".tabset .tabset-fade .tabset-pills"
}

```


### Ouija Trajectory Inference {`r tabVar`}
In this section trajectory analysis using the Ouija method are presented.  

```{r Ouija_main, echo=TRUE, eval=TRUE, warning=FALSE, results="asis"} 

cat(paste(knitr::knit(text = chnkVec, quiet = T), collapse = '\n'))

``` 


```{r ouija_heatmaps_part1, eval=TRUE, echo=F, results=F}
if (length(plotList) > 3){
    tabVar <- ".tabset .tabset-fade .tabset-dropdown"
} else {
    tabVar <- ".tabset .tabset-fade .tabset-pills"
}

###############################################################################
## Find most variable genes in trajectory                                    ##

pseudotimeLineageName <- "Ouija_Pseudotime"
plotTopNgenes <- 100

Y <- data.matrix( OsC@assays[["RNA"]]@data)
        
Y <-  Y[OsC@assays$integrated@var.features,]
        
t <- OsC@meta.data[,pseudotimeLineageName]
        
# Fit GAM for each gene using pseudotime as independent variable.
        
gam.pval <- apply(Y, 1, function(z){
    d <- data.frame(z=z, t=t)
    tmp <- gam::gam(z ~ gam::lo(t), data=d)
    p <- summary(tmp)[4][[1]][1,5]
    p
})


gam.pval <- sort(gam.pval, decreasing = FALSE)
gam.pval <- gam.pval[gam.pval < 0.01]
gam.pval <- sort(gam.pval, decreasing=FALSE)


display.gam.pval <- log10(gam.pval)
maxVal <- max(display.gam.pval[display.gam.pval < Inf])
display.gam.pval[display.gam.pval == Inf] <- maxVal

topgenes <- names(gam.pval)[1:plotTopNgenes]

heatmapGeneList <- list(
    "Top_Pseudotime_Variable_Genes" = topgenes
)


###################
## Make Table

dfOut <- data.frame(gene=names(gam.pval), time_variability_gam_lg10_p_value=display.gam.pval)
dfOut[["Most_time_variable_genes"]] <- ""
dfOut[dfOut$gene %in% topgenes, "Most_time_variable_genes"] <- "+"

## Done
####################

pos <- grep("TFs", names(Obio@dataTableList$referenceList))

if (length(pos > 0)){
    topgenes.TF <- names(sort(gam.pval, decreasing = FALSE))[names(sort(gam.pval, decreasing = FALSE)) %in% Obio@dataTableList[["referenceList"]]$TFs]
    topgenes.TF <- topgenes.TF[1:plotTopNgenes]
    heatmapGeneList[["Top_Pseudotime_Variable_Transcription_Factors"]] <- topgenes.TF
    dfOut[["Most_time_variable_TFs"]] <- ""
    dfOut[dfOut$gene %in% topgenes.TF, "Most_time_variable_TFs"] <- "+"

} else {
    topgenes.TF <- 0
}

#########################################
## Add average expression column

###############################################################################
## Add percentage expressed genes                                            ##
DefaultAssay(OsC) <- "RNA"
my_genes <- rownames(x = OsC@assays$RNA)

exp <- FetchData(OsC, my_genes)

ExprMatrix <- round(as.matrix(colMeans(exp  > 0)) *100,1)
colnames(ExprMatrix)[1] <- "Percent_cells_expressing"
dfExprMatrix <- data.frame(ExprMatrix)
dfExprMatrix[["gene"]] <- row.names(dfExprMatrix)

dfExprMatrix <- dfExprMatrix[dfExprMatrix$gene %in% dfOut$gene, ]

dfOut <- dplyr::full_join(
    dfOut,
    dfExprMatrix,
    by="gene"
)

dfOutDisplay <- dfOut[dfOut$Percent_cells_expressing >= 10, ]

##
#########################################

#########################################
## Write to Excel 
if (!dir.exists(Obio@parameterList[["reportTableDir"]])){
  dir.create(Obio@parameterList[["reportTableDir"]])
}

baseFN <- paste0(
   Obio@parameterList$project_id, 
   ".Lineage1.variability.table.xlsx"
)


outPutFN <- paste0(
     Obio@parameterList$reportTableDir,
     baseFN
)
  
 
FNrel <- paste0("report_table/", baseFN)

wb <- openxlsx::createWorkbook()

hs1 <- openxlsx::createStyle(
    fontColour = "#ffffff",
    fgFill = "#000000",
    halign = "CENTER",
    textDecoration = "Bold"
)
sheetName <- substr("Lineage_1",1,30)
  
openxlsx::addWorksheet(
    wb, 
    sheetName = sheetName
)
  
openxlsx::freezePane(wb, sheetName ,  firstActiveRow = 2)
sheetN=1
openxlsx::writeData(wb, sheetN, dfOut, startRow = 1, startCol = 1, headerStyle = hs1)
openxlsx::saveWorkbook(
  wb, 
  outPutFN , 
  overwrite = TRUE
)

## Create table download option ##
#FNbase <- paste0(Obio@parameterList$project_id, "_Pseudotime_Variable_Genes.xlsx")
#FN <- paste0(Obio@parameterList$reportTableDir, FNbase)
#FNrel <- paste0("report_tables/", FNbase)
tabDownloadLink <- paste0("This table list all potentially time-variable genes in this trajectory [here](",FNrel,")")
tabLegend = paste0(
    "**Table: ** Time-variable genes in this trajectory. ",
    tabDownloadLink
)
chnkVec <- paste0(
        #"#### ", names(dtList),
        "\n```{r PT_var_datatable, results='asis', echo=F, eval=TRUE, warning=FALSE, fig.cap='",
        tabLegend,"'}\n",
        "\n",
        "\n DT::datatable(dfOutDisplay,rownames = FALSE,  escape = FALSE)",
        "\n cat(  '\n')",
        "\n\n\n```\n"   
    )
tabVar <- "### Table Time-variable Genes"



##
###############################################################################
```

`r tabVar`
```{r render_QCTable, echo=TRUE, eval=TRUE, warning=FALSE, results="asis"}
    cat(paste(knitr::knit(text = chnkVec, quiet = T), collapse = '\n'))
```


```{r ouija_heatmaps_part2, eval=TRUE, echo=F, results=F}


###############################################################################
## Init Plot Collection                                                      ##

plotList <- list()
chnkVec <- as.vector(NULL, mode = "character")

## Done                                                                      ##
###############################################################################

for (i in 1:length(heatmapGeneList)){
    ## Relative Heatmap
    tag <- paste0(names(heatmapGeneList)[i], "_relative")
    plotList[[tag]] <- createLineageHeatmap(
    OsC,  
    lineageSelection = NULL,
    pseudotimeLineageName = "Ouija_Pseudotime",
    heatmapGeneVec = heatmapGeneList[[i]],
    clusterRows = TRUE
    )
 
    ## Save to file ##
    FNbase <- paste0(tag, VersionPdfExt)
    FN <- paste0(Obio@parameterList$reportFigDir, FNbase)
    FNrel <- paste0("report_figures/", FNbase)
    
    
    pdf(FN)
        print(plotList[[tag]])
    dev.off()
    
    
    
    ## Create R markdown chunk ##
    figLegend <- paste0(
        '**Figure ', 
        figureCount, 
        '**: Heatmap (relative values) ',tag,
        '. Download a pdf of this figure <a href="',FNrel,'" target="_blank">here</a>. '
    )
    figureCount <- figureCount + 1 
    
    NewChnk <- paste0(
        "\n#### ", tag, 
        "\n```{r ", tag, ", results='asis', echo=F, eval=TRUE, warning=FALSE, fig.cap='",
        figLegend,"'}\n",
        "\n",
        "\n print(plotList[['",tag,"']])",
        "\n cat(  '\n')",
        "\n\n\n```\n"   
    )
    
    chnkVec <- c(
        chnkVec,
        NewChnk
    )
    
    ## Absolute Heatmap
    tag <- paste0(names(heatmapGeneList)[i], "_absolute")
    plotList[[tag]] <- createLineageHeatmap(
        OsC,  
        lineageSelection = NULL,
        pseudotimeLineageName = "Ouija_Pseudotime",
        heatmapGeneVec = heatmapGeneList[[i]],
        clusterRows = TRUE,
        #plotTopNgenes = 100,
        plotAbsoluteValues = TRUE,  # otherwise: relative
        highColor = "#00008B",
        #midColor = "#fffbbc",
        lowColor = "#d3d3d3"
    )
 
    ## Save to file ##
    FNbase <- paste0(tag, VersionPdfExt)
    FN <- paste0(Obio@parameterList$reportFigDir, FNbase)
    FNrel <- paste0("report_figures/", FNbase)
    
    
    pdf(FN)
        print(plotList[[tag]])
    dev.off()
    
    
    
    ## Create R markdown chunk ##
    figLegend <- paste0(
        '**Figure ', 
        figureCount, 
        '**: Heatmap ',tag,
        '. Download a pdf of this figure <a href="',FNrel,'" target="_blank">here</a>. '
    )
    figureCount <- figureCount + 1 
    
    NewChnk <- paste0(
        "\n#### ", tag, 
        "\n```{r ", tag, ", results='asis', echo=F, eval=TRUE, warning=FALSE, fig.cap='",
        figLegend,"'}\n",
        "\n",
        "\n print(plotList[['",tag,"']])",
        "\n cat(  '\n')",
        "\n\n\n```\n"   
    )
    
    chnkVec <- c(
        chnkVec,
        NewChnk
    )
    
    
    ## Done                                                                      ##
    ###############################################################################
}

if (length(plotList) > 3){
    tabVar <- ".tabset .tabset-fade .tabset-dropdown"
} else {
    tabVar <- ".tabset .tabset-fade .tabset-pills"
}

```

### Ouija Heatmaps {`r tabVar`}
```{r Ouija_hm_main, echo=TRUE, eval=TRUE, warning=FALSE, results="asis"} 

cat(paste(knitr::knit(text = chnkVec, quiet = T), collapse = '\n'))

``` 
