<!-- Set Parameters Module -->
<!-- Set the chnkPrefix to make all chunks unique in the overall folder -->
## Branch 2 - Ouija 
```{r, echo=TRUE, eval=TRUE, warning=FALSE}

## Export Pseudotime to Seurat object ##
# Branch 1
# Clusters Polykeratins (5) > mTecDiff (12) > NEDC_I_NEUROD1 (1) > NEDC_II_NEUROD1 (4) > NEDC_III_SOX2 (2) > NEDC_IV_SOX2 (11)

# Clusters Polykeratins (5) > cTecDiff (9) > cTECI (0) > cTECIII (6) > cTECII (3)
branch1 <- c(5, 9, 0, 6,3)
#branch1 <- c(5, 12, 1, 4, 2, 11)

branchName <- "branch2"

chnkPrefix <- paste0("T4.oui.", branchName, ".")
VersionPdfExt <- VersionPdfExt <- paste0(".",chnkPrefix,"V", gsub("-", "", Sys.Date()), ".pdf")

#install.packages("V8")
#renv::install("cole-trapnell-lab/leidenbase")
#renv::install("cole-trapnell-lab/monocle3")

## Requires conda environment as gdal can't be installed. ##
## remember module purge to flush old R versions
# list all conda environments
# conda env list

# conda activate R-monocle3
# R-version of the above: R 4.0.2


invertPseudotime <- FALSE
useCachedObject <- TRUE
startClusterID <- 5
startClusterColName <- "seurat_clusters"
plotTopNgenes <- 100
nTimeBins <- 100
mainPTcol <- "Pseudotime_Ouija"

###############################################################################
## Ouija genes                                                               ##

earlySwitch <- c(
    "HMGB1",	
    "FOS",
    "FOXC1",
    "HES1",
    "JUN",
    "JUNB"
)

earlySwitch <- earlySwitch[earlySwitch %in% row.names(OsC)]

lateSwitch <- c(
    "CEBPD",
    "NFIA"
)
lateSwitch <- lateSwitch[lateSwitch %in% row.names(OsC)]

transient <- c("SCX", "BTG2")
transient <- transient[transient %in% row.names(OsC)]


response_type <- c(
    rep("switch", length(earlySwitch) + length(lateSwitch)), 
    rep("transient", length(transient))
)

allMarkers <- unique(
    c(
        earlySwitch,
        lateSwitch,
        transient
    )
)

## Done
###############################################################################

###############################################################################
## Gene list to plot                                                         ##
heatmapGeneListAdditions <- list(
    "Custom_GeneSet_Branch_2" = c(
    "KRT15",
    "KRT19",
    "PRRX1",
    "ARID5B",
    "FN1",
    "IFITM3",
    "HES1",
    "CEBPD",
    "ZFP36L2",
    "CLU",
    "S100A14",
    "CSTB",
    "PLTP",
    "CTSV",
    "SCX",
    "LY75",
    "PRSS16",
    "TBATA",
    "CCL25",
    "GNG11",
    "PSMB11"
), 
"Custom_GeneSet_2_Branch_2" = c(
    "HES1",
    "CEBPD",
    "ZFP36L2",
    "MYC",
    "CLU",
    "KRT14",
    "KRT15",
    "KRT19",
    "KRT17",
    "IFITM3",
    "PRRX1",
    "ARID5B",
    "FN1",
    "TIMP1",
    "SOX4",
    "CLDN3",
    "CLDN4",
    "ASCL1",
    "LY75", 
    "KNCIP3",
    "TBATA",
    "PRSS16",
    "TSC22D1",
    "PTTG1",
    "CTSV",
    "GNG11",
    "COX7A1",
    "PSMB11",
    "SCX",
    "CD74",
    "CCL25",
    "CFC1",
    "PEMT",
    "TP53AIP1",
    "PLTP",
    "PITHD1"
)
)

##                                                                           ##
###############################################################################


```
  
  
  
```{r, include=FALSE}
knitr::opts_chunk$set(
  tidy = TRUE,
  tidy.opts = list(width.cutoff = 120),
  message = FALSE,
  warning = FALSE
)
```

```{r, eval=F, echo=T, results=F}
## prepare matrix ##

###############################################################################
## Subset main seurat object
seurat <- OsC

## subset dataset ##
seurat@meta.data[["Branch"]] <- "Rest"
seurat@meta.data[seurat@meta.data[["seurat_clusters"]] %in% branch1, "Branch"] <- "Branch"

seurat <- subset(x = seurat, subset = Branch == "Branch")


##
###############################################################################

###############################################################################
## Add percentage expressed genes                                            ##
DefaultAssay(seurat) <- "RNA"
my_genes <- rownames(x = seurat@assays$RNA)

exp <- FetchData(seurat, allMarkers)

ExprMatrix <- round(as.matrix(colMeans(exp  > 0)) *100,1)
colnames(ExprMatrix)[1] <- "Percent_cells_expressing"
dfExprMatrix <- data.frame(ExprMatrix)
dfExprMatrix[["gene"]] <- row.names(dfExprMatrix)


##
#########################################

OsC_subL1 <- seurat
OsC_subL1 <- subset(OsC_subL1, features = allMarkers)
dfMat <- OsC_subL1@assays[["RNA"]]@data
dfTmat <- data.matrix(t(dfMat))
dfTmat <- dfTmat[rowSums(dfTmat) != 0, ]
#dfTmat <- dfTmat[sample(row.names(dfTmat), 5000),]

## Make sure no row has zero counts ##
selVec  <- (colSums(dfTmat) > 0)
dfTmat <- dfTmat[,selVec]
response_type <- response_type[selVec]



# library(rslurm)
# sjob <- slurm_apply(test_func, pars, jobname = 'test_apply',
#                     nodes = 2, cpus_per_node = 2, submit = FALSE)

options(mc.cores = parallel::detectCores())
oui <- ouija::ouija(
    dfTmat, 
    response_type, 
    inference_type = "vb",  # is orders of magnitude faster than hmc
    iter = 500 # ideal 4000
)

FN <- paste0(
    Obio@parameterList$localWorkDir,
    Obio@parameterList$project_id,
    ".", branchName,
    ".ouija.SCE.rds"
)

saveRDS(oui, FN)
```

```{r , echo=TRUE, eval=TRUE, warning=FALSE, results=F}
###############################################################################
## Visualization                                                             ##
## Load Rds
FN <- paste0(
    Obio@parameterList$localWorkDir,
    Obio@parameterList$project_id,
    ".", branchName,
    ".ouija.SCE.rds"
)

oui <-readRDS(FN)

plotList <- list()
chnkVec <- as.vector(NULL, mode = "character")

Ouija_Pseudotime <- map_pseudotime(oui)
Ouija_Switchtime <- switch_times(oui) # MAP switch times
Ouija_Peaktime <- peak_times(oui) # MAP peak times
Ouija_SwitchStrength <-  switch_strengths(oui) # MAP switch strengths

dfRes <- data.frame(
    cellID = row.names(dfTmat),
    Ouija_Pseudotime
)

row.names(dfRes) <- dfRes$cellID
dfRes$cellID <- NULL

names(dfRes) <- gsub("Ouija_Pseudotime", paste0("Pseudotime_Ouija_", branchName), names(dfRes) )


OsC <- biologicToolsSC::addDf2seuratMetaData(
    OsC, 
    dfRes
)

OsC@meta.data[is.na(OsC@meta.data)] <- 0


gene_regs <- gene_regulation(oui)
#head(gene_regs)

###############################################################################
## Diagnostic plot 1                                                         ##
# We can plot the gene expression over pseudotime along with the maximum a posteriori (MAP) estimates of the mean function (the sigmoid or Gaussian transient function) using the plot_expression function:
tag <- "Expression"

plotList[[tag]] <- plot_expression(oui) + ggplot2::theme_bw(
) +  ggplot2::theme(
      axis.text.y   = ggplot2::element_text(size=8),
      axis.text.x   = ggplot2::element_text(size=8),
      axis.title.y  = ggplot2::element_text(size=8),
      axis.title.x  = ggplot2::element_text(size=8),
      axis.line = ggplot2::element_line(colour = "black"),
      panel.border = ggplot2::element_rect(colour = "black", fill=NA, size=1),
      plot.title = ggplot2::element_text(hjust = 0.5, size = 12),
      legend.title = ggplot2::element_blank()
) + ggplot2::guides(col = ggplot2::guide_legend(override.aes = list(shape = 16, size = legendDotSize))
) + ggplot2::ggtitle(paste0(lineageTag, ": ", gsub("_", " ", tag))
)

FNbase <- paste0(tag, VersionPdfExt)
FN <- paste0(Obio@parameterList$reportFigDir, FNbase)
FNrel <- paste0("report_figures/", FNbase)

pdf(FN)
  plotList[[tag]]
dev.off()
            
# if (exists("shinyURL") & !is.null(shinyURL)){
#     link <- paste0(
#       'An interactive version of this figure with additional viewing options can be found <a href="',shinyURL,'?_inputs_&y_axis=%22UMAP_2%22&x_axis=%22UMAP_1%22&colorBy=%22Pseudotime_MC%22&splitByColumn=%22all%22" target="_blank">here</a>. '
#     )
# } else {
#     link <- ""
# }

link <- ""
    
figLegend <- paste0(
    '**Figure ', 
    figureCount, 
    ':** ',
    ' We can plot the gene expression over pseudotime along with the maximum a posteriori (MAP) estimates of the mean function (the sigmoid or Gaussian transient function). Download a pdf of this figure <a href="',FNrel,'" target="_blank">here</a>. ',
     link
)

figureCount <- figureCount + 1

NewChnk <- paste0(
    "#### ", tag,
    "\n```{r, results='asis', echo=F, eval=TRUE, warning=FALSE, fig.cap='",
    figLegend,"'}\n",
    "\n",
    "\n print(plotList[['",tag,"']])",
    "\n cat(  '\n')",
    "\n\n\n```\n"   
)

chnkVec <- c(
    chnkVec,
    NewChnk
)


##                                                                           ##
###############################################################################

###############################################################################
##                                                                           ##
# We can also visualise when in the trajectory gene regulation behaviour occurs, either in the form of the switch time or the peak time (for switch-like or transient genes) using the plot_switch_times and plot_transient_times functions:

tag <- "Peak_Times"

plotList[[tag]] <- ouija::peak_times(oui
#) + ggplot2::theme_bw(
#) +  ggplot2::theme(
#      axis.text.y   = ggplot2::element_text(size=8),
#      axis.text.x   = ggplot2::element_text(size=8),
#      axis.title.y  = ggplot2::element_text(size=8),
#      axis.title.x  = ggplot2::element_text(size=8),
#      axis.line = ggplot2::element_line(colour = "black"),
#      panel.border = ggplot2::element_rect(colour = "black", fill=NA, size=1),
#      plot.title = ggplot2::element_text(hjust = 0.5, size = 12),
#      legend.title = ggplot2::element_blank()
#) + ggplot2::guides(col = ggplot2::guide_legend(override.aes = list(shape = 16, size = legendDotSize))
#) + ggplot2::ggtitle(paste0(lineageTag, ": ", gsub("_", " ", tag))
)

FNbase <- paste0(tag, VersionPdfExt)
FN <- paste0(Obio@parameterList$reportFigDir, FNbase)
FNrel <- paste0("report_figures/", FNbase)

pdf(FN)
  plotList[[tag]]
dev.off()
            
# if (exists("shinyURL") & !is.null(shinyURL)){
#     link <- paste0(
#       'An interactive version of this figure with additional viewing options can be found <a href="',shinyURL,'?_inputs_&y_axis=%22UMAP_2%22&x_axis=%22UMAP_1%22&colorBy=%22Pseudotime_MC%22&splitByColumn=%22all%22" target="_blank">here</a>. '
#     )
# } else {
#     link <- ""
# }

link <- ""
    
figLegend <- paste0(
    '**Figure ', 
    figureCount, 
    ':** ',
    ' We can also visualise when in the trajectory gene regulation behaviour occurs, either in the form of the switch time or the peak time (for switch-like or transient genes). Download a pdf of this figure <a href="',FNrel,'" target="_blank">here</a>. ',
     link
)

figureCount <- figureCount + 1

NewChnk <- paste0(
    "#### ", tag,
    "\n```{r, results='asis', echo=F, eval=TRUE, warning=FALSE, fig.cap='",
    figLegend,"'}\n",
    "\n",
    "\n print(plotList[['",tag,"']])",
    "\n cat(  '\n')",
    "\n\n\n```\n"   
)

chnkVec <- c(
    chnkVec,
    NewChnk
)


##                                                                           ##
###############################################################################

###############################################################################
##                                                                           ##
tag <- "Switch_Times"

plotList[[tag]] <- ouija::plot_switch_times(oui) + ggplot2::theme_bw(
) +  ggplot2::theme(
      axis.text.y   = ggplot2::element_text(size=8),
      axis.text.x   = ggplot2::element_text(size=8),
      axis.title.y  = ggplot2::element_text(size=8),
      axis.title.x  = ggplot2::element_text(size=8),
      axis.line = ggplot2::element_line(colour = "black"),
      panel.border = ggplot2::element_rect(colour = "black", fill=NA, size=1),
      plot.title = ggplot2::element_text(hjust = 0.5, size = 12),
      legend.title = ggplot2::element_blank()
) + ggplot2::guides(col = ggplot2::guide_legend(override.aes = list(shape = 16, size = legendDotSize))
) + ggplot2::ggtitle(paste0(lineageTag, ": ", gsub("_", " ", tag))
)

FNbase <- paste0(tag, VersionPdfExt)
FN <- paste0(Obio@parameterList$reportFigDir, FNbase)
FNrel <- paste0("report_figures/", FNbase)

pdf(FN)
  plotList[[tag]]
dev.off()
            
# if (exists("shinyURL") & !is.null(shinyURL)){
#     link <- paste0(
#       'An interactive version of this figure with additional viewing options can be found <a href="',shinyURL,'?_inputs_&y_axis=%22UMAP_2%22&x_axis=%22UMAP_1%22&colorBy=%22Pseudotime_MC%22&splitByColumn=%22all%22" target="_blank">here</a>. '
#     )
# } else {
#     link <- ""
# }

link <- ""
    
figLegend <- paste0(
    '**Figure ', 
    figureCount, 
    ':** ',
    ' We can also visualise when in the trajectory gene regulation behaviour occurs, either in the form of the switch time or the peak time (for switch-like or transient genes). Download a pdf of this figure <a href="',FNrel,'" target="_blank">here</a>. ',
     link
)

figureCount <- figureCount + 1

NewChnk <- paste0(
    "#### ", tag,
    "\n```{r, results='asis', echo=F, eval=TRUE, warning=FALSE, fig.cap='",
    figLegend,"'}\n",
    "\n",
    "\n print(plotList[['",tag,"']])",
    "\n cat(  '\n')",
    "\n\n\n```\n"   
)

chnkVec <- c(
    chnkVec,
    NewChnk
)

##                                                                           ##
###############################################################################

###############################################################################
##                                                                           ##
# This step consumes a lot of time
# cmo <- consistency_matrix(oui)

# pdf("../temp4.consistency.matrix.pdf")
# plot_consistency(oui)
# dev.off()
##                                                                           ##
###############################################################################

###############################################################################
##                                                                           ##
# cell_classifications <- cluster_consistency(cmo)
# 
# map_pst <- map_pseudotime(oui)
# df_class <- data.frame(map_pst, cell_classifications)
# 
# pdf("../temp5.cell.classifications.pdf")
# ggplot(df_class, aes(x = map_pst, y = cell_classifications)) +
#   geom_point() +
#   xlab("MAP pseudotime") +
#   ylab("Cell classification")
# dev.off()
##                                                                           ##
###############################################################################

if (length(plotList) > 2){
    tabVar <- ".tabset .tabset-fade .tabset-dropdown"
} else {
    tabVar <- ".tabset .tabset-fade .tabset-pills"
}

```



```{r, echo=TRUE, eval=TRUE, warning=FALSE, results="asis"} 
tag <- paste0("Pseudotime_Ouija_",  branchName)
lineageTag <- paste0("Pseudotime_Ouija_",  branchName)

plotList[[tag]] <- ggplot2::ggplot(
    data = OsC@meta.data, aes_string(x="UMAP_1", y="UMAP_2", color=tag)
) + geom_point() + ggplot2::theme_bw(
) +  ggplot2::theme(
      axis.text.y   = ggplot2::element_text(size=8),
      axis.text.x   = ggplot2::element_text(size=8),
      axis.title.y  = ggplot2::element_text(size=8),
      axis.title.x  = ggplot2::element_text(size=8),
      axis.line = ggplot2::element_line(colour = "black"),
      panel.border = ggplot2::element_rect(colour = "black", fill=NA, size=1),
      plot.title = ggplot2::element_text(hjust = 0.5, size = 12),
      legend.title = ggplot2::element_blank()
) + ggplot2::guides(col = ggplot2::guide_legend(override.aes = list(shape = 16, size = legendDotSize))
) + ggplot2::ggtitle(paste0("Sample: ", gsub("_", " ", tag))
)

FNbase <- paste0(tag, VersionPdfExt)
FN <- paste0(Obio@parameterList$reportFigDir, FNbase)
FNrel <- paste0("report_figures/", FNbase)

pdf(FN)
    print(plotList[[tag]])
dev.off()
            
if (exists("shinyURL") & !is.null(shinyURL)){
    link <- paste0(
      'An interactive version of this figure with additional viewing options can be found <a href="',shinyURL,'?_inputs_&y_axis=%22UMAP_2%22&x_axis=%22UMAP_1%22&colorBy=%22',tag,'%22&splitByColumn=%22all%22" target="_blank">here</a>. '
    )
} else {
    link <- ""
}
    
figLegend <- paste0(
    '**Figure ', 
    figureCount, 
    ':** ',
    ' Ouija pseudotime projection on UMAP. Download a pdf of this figure <a href="',FNrel,'" target="_blank">here</a>. ',
     link
)

figureCount <- figureCount + 1

NewChnk <- paste0(
    "#### ", tag,
    "\n```{r, results='asis', echo=F, eval=TRUE, warning=FALSE, fig.cap='",
    figLegend,"'}\n",
    "\n",
    "\n print(plotList[['",tag,"']])",
    "\n cat(  '\n')",
    "\n\n\n```\n"   
)

chnkVec <- c(
    chnkVec,
    NewChnk
)


## Done overview plot                                                        ##
###############################################################################

if (length(plotList) > 2){
    tabVar <- paste0("### Ouija Pseudotime Subtrajectory ",branchName," {.tabset .tabset-fade .tabset-dropdown}")
} else {
    tabVar <- paste0("### Ouija Pseudotime Subtrajectory ",branchName," {.tabset .tabset-fade .tabset-pills}")
}



```

`r tabVar`

```{r , echo=TRUE, eval=TRUE, warning=FALSE, results="asis"} 

cat(paste(knitr::knit(text = chnkVec, quiet = T), collapse = '\n'))

```


```{r, echo=TRUE, eval=TRUE, warning=FALSE, results=F}
plotList <- list()
chnkVec <- as.vector(NULL, mode = "character")

###############################################################################
## Find most variable genes in trajectory                                    ##

pseudotimeLineageName <-  tag
# plotTopNgenes <- 100

###############################################################################
## Subset main seurat object
## subset dataset ##
seurat <- OsC
seurat@meta.data[["Branch"]] <- "Rest"
seurat@meta.data[seurat@meta.data[["seurat_clusters"]] %in% branch1, "Branch"] <- "Branch"

seurat <- subset(x = seurat, subset = Branch == "Branch")

##
###############################################################################

Y <- data.matrix( seurat@assays[["RNA"]]@data)

## Focus on most variable genes in the study        
Y <-  Y[seurat@assays$integrated@var.features,]
Y <- Y[rowSums(Y) > 0,]
        
t <- seurat@meta.data[,tag]
        
# Fit GAM for each gene using pseudotime as independent variable.
        
gam.pval <- apply(Y, 1, function(z){
    d <- data.frame(z=z, t=t)
    tmp <- gam::gam(z ~ gam::lo(t), data=d)
    p <- summary(tmp)[4][[1]][1,5]
    p
})


gam.pval <- sort(gam.pval, decreasing = FALSE)
gam.pval <- gam.pval[gam.pval < 0.01]
gam.pval <- sort(gam.pval, decreasing=FALSE)


display.gam.pval <- -1*log10(gam.pval)
maxVal <- max(display.gam.pval[display.gam.pval < Inf])
display.gam.pval[display.gam.pval == Inf] <- maxVal

topgenes <- names(gam.pval)[1:plotTopNgenes]

heatmapGeneList <- list(
    "Top_Pseudotime_Variable_Genes" = topgenes
)


###################
## Make Table

dfOut <- data.frame(gene=names(gam.pval), time_variability_gam_lg10_p_value=round(display.gam.pval,3))
dfOut[["Most_time_variable_genes"]] <- ""
dfOut[dfOut$gene %in% topgenes, "Most_time_variable_genes"] <- "+"

## Done
####################

pos <- grep("TFs", names(Obio@dataTableList$referenceList))

if (length(pos > 0)){
    topgenes.TF <- names(sort(gam.pval, decreasing = FALSE))[names(sort(gam.pval, decreasing = FALSE)) %in% Obio@dataTableList[["referenceList"]]$TFs]
    topgenes.TF <- topgenes.TF[1:plotTopNgenes]
    heatmapGeneList[["Top_Pseudotime_Variable_Transcription_Factors"]] <- topgenes.TF
    dfOut[["Most_time_variable_TFs"]] <- ""
    dfOut[dfOut$gene %in% topgenes.TF, "Most_time_variable_TFs"] <- "+"

} else {
    topgenes.TF <- 0
}

###############################################################################
## Add additional gene sets to heatmapset                                    ##

if (exists("heatmapGeneListAdditions") & (length(heatmapGeneListAdditions) > 0)){
    heatmapGeneList <- do.call(c, list(heatmapGeneList, heatmapGeneListAdditions))
}

##                                                                           ##
###############################################################################


#########################################
## Add average expression column

###############################################################################
## Add percentage expressed genes                                            ##
DefaultAssay(OsC) <- "RNA"
my_genes <- rownames(x = seurat@assays$RNA)

exp <- FetchData(seurat, my_genes)

ExprMatrix <- round(as.matrix(colMeans(exp  > 0)) *100,1)
colnames(ExprMatrix)[1] <- "Percent_cells_expressing"
dfExprMatrix <- data.frame(ExprMatrix)
dfExprMatrix[["gene"]] <- row.names(dfExprMatrix)

dfExprMatrix <- dfExprMatrix[dfExprMatrix$gene %in% dfOut$gene, ]

dfOut <- dplyr::full_join(
    dfOut,
    dfExprMatrix,
    by="gene"
)


##
#########################################

###############################################################################
## Detect peak genes among most variable genes                               ##

## Get data
dfData <- seurat@assays[["RNA"]]@data[names(gam.pval),]

dfData <- dfData[unique(na.omit(c(topgenes, topgenes.TF))), ]

dfPT <- seurat@meta.data[,c("cellID", tag)]

first <- TRUE
maxPeakPosition <- as.vector(NULL, mode="numeric")
peakType <- as.vector(NULL, mode="character")
gene <- as.vector(NULL, mode="character")
peakMax <- as.vector(NULL, mode="numeric")

for (i in 1:nrow(dfData)){
    dfTempData <- data.frame(cellID=colnames(dfData), assign(row.names(dfData)[i], as.vector(dfData[i,])))
    names(dfTempData)[2] <- "gene"
    
    dfTempData <- merge(
        dfPT, 
        dfTempData, 
        by.x = "cellID",
        by.y = "cellID"
    )
    smoothing <- 0.1
    loessMod <- loess(formula(paste0("gene ~", tag)), data=dfTempData, span=smoothing)
    
    xl <- seq(min(dfTempData[,tag]),max(dfTempData[,tag]), (max(dfTempData[,tag]) - min(dfTempData[,tag]))/99)
    yl <- predict(loessMod,xl)
        
    yl[is.na(yl)] <- 0
      
    ## Annotate peak position ##
    if (sum(yl) > 0){
        peakPos <- find_peaks(yl, m=length(yl)/2)  
        
        if (length(peakPos) > 0){
            pos <- grep( max(yl[peakPos]), yl[peakPos])
            peakPos <- peakPos[pos]   
        }
        
        peakMax[i] <- max(yl)
        
        gene[i] <- row.names(dfData)[i]
        
        if (length(peakPos) > 0){
            maxPeakPosition[i] <- peakPos  
            
            if (peakPos <= 15){
            peakType[i] <- "proximal"
        } else if (peakPos >15 & peakPos < 85) {
            peakType[i] <- "middle"
        } else if (peakPos >= 85){
            peakType[i] <- "distal"
        } else {
            "none"
        }
            
        } else {
            maxPeakPosition[i] <- NA
            peakType[i] <- ""
            peakMax[i] <- 0
        }
        
        
        
    }
    
    
        #row_mean <- mean(yl)
        #row_hm <- log2(yl/row_mean)
        #row_hm[row_hm > setMax] = setMax
        #row_hm[row_hm < setMin] = setMin
        
    new.row <- data.frame(t(yl))
    row.names(new.row) <- row.names(dfData)[i]
        
        
    if (first){
        dfRes <- new.row
        first <- FALSE
    } else {
        dfRes <- rbind(
            dfRes, 
            new.row
        )
    }
    
    if (i%%20 == 0){
      print(i)
    }
}

# bs = cr, denoting cubic regression splines
###############################################################################
## Classify peaks                                                            ##

## Classify as peak everything peaking between bin 15 and 85
dfPeak <- data.frame(
    gene, 
    peakType,
    maxPeakPosition,
    peakMax
)

dfPeak <- dfPeak[order(dfPeak$maxPeakPosition, decreasing = F),]

dfOut <- merge(
    dfOut, 
    dfPeak, 
    by.x = "gene",
    by.y = "gene",
    all=TRUE
)

dfOutDisplay <- dfOut[dfOut$Percent_cells_expressing >= 10, ]
## Done                                                                      ##
###############################################################################

##                                                                           ##
###############################################################################

#########################################
## Write to Excel 
if (!dir.exists(Obio@parameterList[["reportTableDir"]])){
  dir.create(Obio@parameterList[["reportTableDir"]])
}

baseFN <- paste0(
   Obio@parameterList$project_id, 
   ".ouija.variability.table.xlsx"
)


outPutFN <- paste0(
     Obio@parameterList$reportTableDir,
     baseFN
)
  
 
FNrel <- paste0("report_tables/", baseFN)

wb <- openxlsx::createWorkbook()

hs1 <- openxlsx::createStyle(
    fontColour = "#ffffff",
    fgFill = "#000000",
    halign = "CENTER",
    textDecoration = "Bold"
)
sheetName <- substr("Lineage_1",1,30)
  
openxlsx::addWorksheet(
    wb, 
    sheetName = sheetName
)
  
openxlsx::freezePane(wb, sheetName ,  firstActiveRow = 2)
sheetN=1
openxlsx::writeData(wb, sheetN, dfOut, startRow = 1, startCol = 1, headerStyle = hs1)
openxlsx::saveWorkbook(
  wb, 
  outPutFN , 
  overwrite = TRUE
)

## Create table download option ##
#FNbase <- paste0(Obio@parameterList$project_id, "_Pseudotime_Variable_Genes.xlsx")
#FN <- paste0(Obio@parameterList$reportTableDir, FNbase)
#FNrel <- paste0("report_tables/", FNbase)
tabDownloadLink <- paste0("This table list all potentially time-variable genes in this trajectory [here](",FNrel,")")
tabLegend = paste0(
    "**Table: ** Time-variable genes in this trajectory. ",
    tabDownloadLink
)
chnkVec <- paste0(
        #"#### ", names(dtList),
        "\n```{r, results='asis', echo=F, eval=TRUE, warning=FALSE, fig.cap='",
        tabLegend,"'}\n",
        "\n",
        "\n DT::datatable(dfOutDisplay,rownames = FALSE,  escape = FALSE)",
        "\n cat(  '\n')",
        "\n\n\n```\n"   
    )
tabVar <- "### Table Time-variable Genes"



##
###############################################################################
```

`r tabVar`
```{r, echo=TRUE, eval=TRUE, warning=FALSE, results="asis"}
    cat(paste(knitr::knit(text = chnkVec, quiet = T), collapse = '\n'))
```

```{r, echo=TRUE, eval=TRUE, warning=FALSE, results=F}
###############################################################################
## Create Heatmap N most variable genes                                      ##

plotList <- list()
chnkVec <- as.vector(NULL, mode = "character")

for (i in 1:length(heatmapGeneList)){
    ## Relative Heatmap
    tag <- paste0(names(heatmapGeneList)[i], "_relative")
    plotList[[tag]] <- createLineageHeatmap(
    seurat,  
    lineageSelection = NULL,
    pseudotimeLineageName = lineageTag,
    heatmapGeneVec = heatmapGeneList[[i]],
    clusterRows = TRUE
    )
 
    ## Save to file ##
    FNbase <- paste0(tag, VersionPdfExt)
    FN <- paste0(Obio@parameterList$reportFigDir, FNbase)
    FNrel <- paste0("report_figures/", FNbase)
    
    
    pdf(FN)
        print(plotList[[tag]])
    dev.off()
    
    
    
    ## Create R markdown chunk ##
    figLegend <- paste0(
        '**Figure ', 
        figureCount, 
        '**: Heatmap (relative values) ',tag,
        '. Download a pdf of this figure <a href="',FNrel,'" target="_blank">here</a>. '
    )
    figureCount <- figureCount + 1 
    
    NewChnk <- paste0(
        "\n#### ", tag, 
        "\n```{r, results='asis', echo=F, eval=TRUE, warning=FALSE, fig.cap='",
        figLegend,"'}\n",
        "\n",
        "\n print(plotList[['",tag,"']])",
        "\n cat(  '\n')",
        "\n\n\n```\n"   
    )
    
    chnkVec <- c(
        chnkVec,
        NewChnk
    )
    
    ## Absolute Heatmap
    tag <- paste0(names(heatmapGeneList)[i], "_absolute")
    plotList[[tag]] <- createLineageHeatmap(
        seurat,  
        lineageSelection = NULL,
        pseudotimeLineageName = lineageTag,
        heatmapGeneVec = heatmapGeneList[[i]],
        clusterRows = TRUE,
        #plotTopNgenes = 100,
        plotAbsoluteValues = TRUE,  # otherwise: relative
        highColor = "#00008B",
        #midColor = "#fffbbc",
        lowColor = "#d3d3d3"
    )
 
    ## Save to file ##
    FNbase <- paste0(tag, VersionPdfExt)
    FN <- paste0(Obio@parameterList$reportFigDir, FNbase)
    FNrel <- paste0("report_figures/", FNbase)
    
    
    pdf(FN)
        print(plotList[[tag]])
    dev.off()
    
    
    
    ## Create R markdown chunk ##
    figLegend <- paste0(
        '**Figure ', 
        figureCount, 
        '**: Heatmap ',tag,
        '. Download a pdf of this figure <a href="',FNrel,'" target="_blank">here</a>. '
    )
    figureCount <- figureCount + 1 
    
    NewChnk <- paste0(
        "\n#### ", tag, 
        "\n```{r, results='asis', echo=F, eval=TRUE, warning=FALSE, fig.cap='",
        figLegend,"'}\n",
        "\n",
        "\n print(plotList[['",tag,"']])",
        "\n cat(  '\n')",
        "\n\n\n```\n"   
    )
    
    chnkVec <- c(
        chnkVec,
        NewChnk
    )
    
    
    ## Done                                                                      ##
    ###############################################################################
}


## Done                                                                      ##
###############################################################################
if (length(plotList) > 3){
    tabVar <- ".tabset .tabset-fade .tabset-dropdown"
} else {
    tabVar <- ".tabset .tabset-fade .tabset-pills"
}

```

### Ouija Trajectory Heatmaps {`r tabVar`}
```{r, echo=TRUE, eval=TRUE, warning=FALSE, results="asis"} 

cat(paste(knitr::knit(text = chnkVec, quiet = T), collapse = '\n'))

```

```{r, echo=TRUE, eval=TRUE, warning=FALSE, results=F}



###############################################################################
if (length(plotList) > 3){
    tabVar <- ".tabset .tabset-fade .tabset-dropdown"
} else {
    tabVar <- ".tabset .tabset-fade .tabset-pills"
}

```
