<!-- Set PArameters Module -->
<!-- Set the chnkPrefix to make all chunks unique in the overall folder -->
```{r partB_heatmaps_and_dotplots, echo=TRUE, eval=TRUE, warning=FALSE}
chnkPrefix <- "partB.heatmaps.dotplots."
VersionPdfExt <- VersionPdfExt <- paste0(".",chnkPrefix,"V", gsub("-", "", Sys.Date()), ".pdf")

```



```{r Cluster_overview_data_prep, echo=TRUE, eval=TRUE, warning=FALSE, results=F}

## Need cluster_stage column
selClust <- "cluster_Treatment"
OsC_HM <- OsC
OsC_HM@meta.data[[selClust]] <- paste0(
  OsC_HM@meta.data$clusterName,
  "_",
  OsC_HM@meta.data$meta_Treatment
)



###############################################################################
## Calculataing average expression across all samples                        ##
Seurat::Idents(OsC_HM) <- selClust
OsCsel <- Seurat::AverageExpression(OsC_HM, return.seurat = TRUE)


# 

dfAdd <- unique(OsC_HM@meta.data[,c("clusterName", "clusterColor",  "meta_Treatment", selClust)])

dfAdd[["treatmentGroupColor"]] <- dfAdd$meta_Treatment
dfAdd$treatmentGroupColor <- gsub("Control", "#3B5EF7", dfAdd$treatmentGroupColor)
dfAdd$treatmentGroupColor <- gsub("MatB52", "#4DA868", dfAdd$treatmentGroupColor)
dfAdd$treatmentGroupColor <- gsub("Regeneron", "#EE6C58", dfAdd$treatmentGroupColor)

row.names(dfAdd) <- dfAdd[,selClust]

OsCsel <- biologicToolsSC::addDf2seuratMetaData(
  obj = OsCsel, 
  dfAdd = dfAdd
)

OsCsel@meta.data$meta_Treatment <- factor(
  OsCsel@meta.data$meta_Treatment,
  levels = c( "Control", "MatB52", "Regeneron")
)

OsCsel@meta.data$clusterName <- factor(
  OsCsel@meta.data$clusterName,
  levels=Obio@parameterList$clusterNameOrder
)


OsCsel@meta.data <- OsCsel@meta.data[order(OsCsel@meta.data$clusterName,OsCsel@meta.data$meta_Treatment),]

dfData <- data.frame(OsCsel[["RNA"]]@data)
dataMatrix <- data.matrix(dfData)
dfMeta <- OsCsel@meta.data
 
dataMatrix <- dataMatrix[,dfMeta[,selClust]]


#########################3
# Create heatmap gene list

dfGeneralMarkers <- Obio@dataTableList$dfGeneralMarkers 
dfGeneralMarkersPos <- dfGeneralMarkers[dfGeneralMarkers$avg_diff > 0,]

Nsel <- 1
Ncluster <- length(unique(OsC@meta.data$clusterName))

geneVec <- as.vector(NULL, mode="character")
while(length(geneVec) < 5*Ncluster & Nsel < nrow(dfGeneralMarkersPos)){
    geneVec <-  as.vector(unique(data.frame(dfGeneralMarkersPos %>% group_by(cluster) %>% top_n(Nsel, avg_diff))[,"gene"]))
    Nsel <- Nsel + 1
}



if (length(geneVec) > 2){
    Obio@parameterList[["cat2HMplotList"]][["Top_Cluster_Markers"]] <- geneVec 
}

## Add top transcription factors for each cluster ##
## Get transcription factor genes ##
if (Obio@parameterList$geneIDcolumn != "mgi_symbol" & Obio@parameterList$geneIDcolumn != "hgnc_symbol") {
    queryGS <- "hgnc_symbol" 
} else {
    queryGS <- Obio@parameterList$geneIDcolumn
}


tempVec <- retrieve.gene.category.from.db(
    cat_id = "ag_lab_categories__10",
    password = db.pwd,
    gene.symbol = queryGS,
    user = Obio@parameterList$db.user,
    host = Obio@parameterList$host
)

###############################################################################
## If this is fish, translation is non-human or non-mouse, translation is necessary
if (queryGS != Obio@parameterList$geneIDcolumn){
    dfAnno <- Obio@dfGeneAnnotation
    dfAnno <- unique(dfAnno[,c("hgnc_symbol",Obio@parameterList$geneIDcolumn )])
    dfAnno <- dfAnno[dfAnno$hgnc_symbol != "", ]
    dfAnno <- dfAnno[dfAnno$hgnc_symbol %in% tempVec, ]
    tempVec <- unique(dfAnno[,Obio@parameterList$geneIDcolumn])
    tempVec <- tempVec[tempVec != ""]
}

dfHMG <- dfGeneralMarkersPos[dfGeneralMarkersPos$gene %in% tempVec, ]
dfHMGsel <- data.frame(dfHMG %>% group_by(cluster) %>% top_n(5, avg_diff))

if (length(as.vector(unique(dfHMGsel$gene))) > 2){
    Obio@parameterList[["cat2HMplotList"]][["Top_TF_Cluster_Markers"]] <- as.vector(unique(dfHMGsel$gene))
}
## Done with translation
  

## Add linear regression heatmap for all genes ##

dfClusterResiduals <- Obio@dataTableList[["dfClusterResiduals"]] 

dfLongResiduals <- data.frame(
    dfClusterResiduals %>% pivot_longer(!gene, names_to = "cluster", values_to = "residuals")
)

dfTop5 <- data.frame(dfLongResiduals %>% group_by(cluster) %>%   top_n(5, residuals))
dfTop5 <- dfTop5[order(dfTop5$cluster),]
geneVec <- as.vector(unique(dfTop5$gene))
if (length(geneVec) > 2){
    Obio@parameterList[["cat2HMplotList"]][["Top_LR_Cluster_Markers"]] <- geneVec
}
## Add linear regression heatmap for transcription factors ##
dfLRsel <- dfLongResiduals[dfLongResiduals$gene %in% tempVec, ]
dfTop5 <- data.frame(dfLRsel %>% group_by(cluster) %>%   top_n(5, residuals))
dfTop5 <- dfTop5[order(dfTop5$cluster),]

geneVec <- as.vector(unique(dfTop5$gene))
if (length(geneVec) > 2){
    Obio@parameterList[["cat2HMplotList"]][["Top_LR_TF_Cluster_Markers"]] <- geneVec
}



## Invert listing order##
orderVec <- rev(names(Obio@parameterList$cat2HMplotList))

topVec <- c(
    "Top_Cluster_Markers", 
    "Top_TF_Cluster_Markers", 
    "Top_LR_Cluster_Markers",
    "Top_LR_TF_Cluster_Markers"
)

topVec <- topVec[topVec %in% orderVec]
orderVec <- orderVec[!(orderVec %in% topVec)]

orderVec <- c(
  topVec, 
  orderVec
)

# Obio@parameterList$cat2HMplotList <- Obio@parameterList$cat2HMplotList[orderVec]
# 
# lapply(Obio@parameterList[["cat2HMplotList"]], function(x) x[length(x) > 2])
## Set cluster order ##
Idents(OsC_HM) <- "clusterName"
Idents(OsC_HM) <- factor(Idents(OsC_HM), levels = Obio@parameterList[["clusterNameOrder"]])

l <- unlist(lapply(Obio@parameterList[["cat2HMplotList"]], function(x) length(as.vector(x)) > 2))
selVec <- names(Obio@parameterList[["cat2HMplotList"]] )[l]

Obio@parameterList[["cat2HMplotList"]] <- Obio@parameterList[["cat2HMplotList"]][selVec]


## Done creating heatmapgenelists


# Done
##########################


#library(ComplexHeatmap)
plotList <- list()
chnkVec <- as.vector(NULL, mode="character")


## Make Heatmaps
if (!exists("figureCount")){
  figureCount <- 1  
}

###############################################################################
## Function to create heatmaps                                               ##

addHeatmap2List <- function(
    dataMatrix,
    geneGroupList,
    cluster_column_slices   = FALSE,
    cluster_columns         = TRUE,
    relativeExpression = FALSE,
    cmdVec = NULL,
    tag = NULL,
    showAllLegends = TRUE,
    figureCount = 1,
    chnkVec = NULL, 
    plotList = NULL,
    maxNcharCatName = 10,
    dfMeta,
    group1ColorCol = "clusterColor", 
    group1NameCol = "clusterName",
    group2ColorCol = "sampleColor", 
    group2NameCol = "sampleName",
    columnSplitCol = "clusterName"
    ){
  
  if (is.null(chnkVec)){
    chnkVec <- as.vector(NULL, mode="character")
  }
  
  if (is.null(plotList)){
    plotList <- list()
  }
  
    allGenes <- unique(as.vector(unlist(geneGroupList)))
    
    
    if (is.null(cmdVec)){
      cmdVec <- as.vector(NULL, mode="character")
    }
    
    if (is.null(tag)){
      tag <- paste("Heatmap_", (length(plotList) + 1))
    }
    
    if (relativeExpression){
      legendString <- "log2 row mean"
    } else {
      legendString <- "lg10 Expr"
    }

# library("RColorBrewer")
# library("Seurat")
# library("ggplot2")
# library("viridis")
# #library("scMCA")
# library("circlize")
# library("ComplexHeatmap")



## Complex heatmap of cell/celltype correlations using just the top annotation per cell.  It's split by seurat cluster.
numbers_plot <- 1
# cors       <-  data.frame(OsC[["RNA"]]@data)
#cors_index <- apply(cors, 2, gettissue, numbers_plot)
#cors_index <- sort(unique(as.integer(cors_index)))
allGenes <- allGenes[allGenes %in% row.names(dataMatrix)]

heat.dat   <- dataMatrix[allGenes, ]
#heat.dat <- heat.dat
#heat.dat   <- t(apply(heat.dat,1,function(x){(x-mean(x))/sd(x)}))

# Comment out for absolute expression

heat.dat <- heat.dat[apply(heat.dat, 1, mean) != 0, ]

if (relativeExpression){
  heat.dat   <- t(apply(heat.dat,1,function(x){log2((x/mean(x)))}))  
} 

heat.dat[heat.dat == -Inf] <- 0

## make sure cat names aren't too long
nMax <- max(nchar(names(geneGroupList)))

if (nMax > maxNcharCatName){
  shortNames <- sapply(
    names(geneGroupList),
    function(x){
      substr(x, 1, maxNcharCatName)
    }
  )
  
  if (sum(duplicated(shortNames)) > 0){
    indexVec <- 1:length(shortNames)
    shortNames[duplicated(shortNames)] <- paste0(shortNames[duplicated(shortNames)],"_", indexVec[duplicated(shortNames)])
  }
  
  names(geneGroupList) <- shortNames
  
}



rowSplitVec <- row.names(heat.dat)   
for (i in 1:length(geneGroupList)){
  rowSplitVec[rowSplitVec %in% geneGroupList[[i]]] <- names(geneGroupList)[i]
}



dfCol <- unique(dfMeta[,c(group1ColorCol, group1NameCol)])
colVec <- dfCol[,group1ColorCol]
names(colVec) <- dfCol[,group1NameCol]

dfCol2 <- unique(dfMeta[,c(group2ColorCol, group2NameCol)])
colVec2 <- dfCol2[,group2ColorCol]
names(colVec2) <- dfCol2[,group2NameCol]
# 
# colList <- list(
#   dfCol, 
#   dfCol2
# )


ht.anno <- ComplexHeatmap::HeatmapAnnotation(
    Age =  dfMeta[,group2NameCol],
    Cluster =  dfMeta[,group1NameCol],
    col = list(
        Age = colVec2,
        Cluster = colVec
    ),
    show_legend = showAllLegends
)


#bulkLogFC <- dfSel[allGenes, "contrast_2_logFC_p27NULL_E185OC_vs_WT_E185OC"]
#xcol <- ifelse(bulkLogFC < 0, "blue", "red")



#row_ha = rowAnnotation(Bulk = anno_barplot(bulkLogFC, gp = gpar(fill=xcol)),
#        show_legend = showAllLegends
#)   

#lrow_ha = rowAnnotation(foo = anno_block(gp = gpar(fill = c("blue", "red")),
#        labels = c("Down", "Up"), 
#        labels_gp = gpar(col = "white", fontsize = 10)),
#        show_legend = showAllLegends
#)
#     df = data.frame(
#         cluster = OsC_HM@meta.data$clusterName),
#     # col = list(
#     #     gp = gpar(col = "white")
#     # ),
#     annotation_legend_param = list(direction = "horizontal")
# )

if (relativeExpression){
  colRamp <- circlize::colorRamp2(c(-3, 0, 3),c("#3060cf", "#fffbbc","#c4463a"))
} else {
  colRamp <- circlize::colorRamp2(c(0, 6),c("#d3d3d3","#3060cf"))
}

if (nrow(heat.dat) > 100){
    rowFont <- 1
} else if (nrow(heat.dat) > 50){
    rowFont <- 1
} else if (nrow(heat.dat) > 25){
    rowFont <- 6
} else {
    rowFont <- 8
}

plotList[[tag]] <- ComplexHeatmap::Heatmap(
    heat.dat,
    row_split               = rowSplitVec,
    name                    = legendString,
    column_title_gp         = grid::gpar(fontsize = 6),
    row_title_rot           = 0, # Must be 0 or 90
    column_title_rot        = 90,
    column_split            = dfMeta[,columnSplitCol],
    #column_split            = column_split,
    cluster_column_slices   = cluster_column_slices,
    cluster_columns         = cluster_columns,
    cluster_rows            = TRUE,
    show_row_names          = TRUE,
    show_column_names       = FALSE,
    column_names_side       = "bottom",
    show_column_dend        = TRUE,
    row_dend_width          = grid::unit(20, "mm"),
    show_heatmap_legend     = showAllLegends,
    column_names_max_height = grid::unit(8, "cm"),
    row_names_gp            = grid::gpar(fontsize = 6),
    top_annotation          = ht.anno,
    #right_annotation = row_ha,
    #left_annotation = lrow_ha,
    #col                     = colorRamp2(c(-2, 0, 2),magma(3)),
    col                     = colRamp,
    column_names_rot        = 90,
    border = TRUE
)

  FNbase <- paste0(tag, VersionPdfExt)

  FN <- paste0(Obio@parameterList$reportFigDir, FNbase)
  FNrel <- paste0("report_figures/", FNbase)
            
  pdf(FN)
    print(plotList[[tag]])
  dev.off()

  figLegend <- paste0(
    '**Figure ', 
    figureCount, 
    ':** ',
    'Heatmap split by cluster for gene set ',gsub("_", " ", tag),'. Download a pdf of this figure <a href="',FNrel,'" target="_blank">here</a>.'
  )
            
  figureCount <- figureCount + 1

  NewChnk <- paste0(
    "#### ", tag,
    "\n```{r hm_",
    tag,", results='asis', echo=F, eval=TRUE, warning=FALSE, fig.cap='",
    figLegend,"'}\n",
    "\n",
    "\n print(plotList[['",tag,"']])",
    "\n cat(  '\n')",
    "\n\n\n```\n"   
)

  chnkVec <- c(
    chnkVec,
    NewChnk
  )
  
  returnList <- list(
    "plotList" = plotList,
    "chnkVec"  = chnkVec,
    "figureCount" = figureCount
  )

return(returnList)
}

## Done function to create heatmaps
###############################################################################


HMgeneSelections <- Obio@parameterList[["cat2HMplotList"]]
HMgeneSelections2 <- list()

for (i in 1:length(HMgeneSelections)){
  hl <- list(HMgeneSelections[[i]])
  names(hl)[1] <- names(HMgeneSelections)[i]
  HMgeneSelections2[[names(HMgeneSelections)[i]]]  <- hl
}


for (i in 1:length(HMgeneSelections2)){
  if (length(unlist(HMgeneSelections2[[i]])) > 1){
    returnList <- addHeatmap2List(
        dataMatrix = dataMatrix,
        cluster_column_slices   = FALSE,
        cluster_columns         = FALSE,
        geneGroupList = HMgeneSelections2[[i]],
        relativeExpression = FALSE,
        cmdVec = NULL,
        tag = paste0(names(HMgeneSelections)[i], "_Abs"),
        showAllLegends = TRUE,
        figureCount = figureCount,
        plotList = plotList,
        maxNcharCatName = 10,
        dfMeta = dfMeta,
        group1ColorCol = "clusterColor", 
        group1NameCol = "clusterName",
        group2ColorCol = "treatmentGroupColor", 
        group2NameCol = "meta_Treatment",
        chnkVec = chnkVec,
        columnSplitCol = "clusterName"
        
    )
    
    plotList <- returnList[["plotList"]]
    chnkVec <- returnList[["chnkVec"]]
    figureCount <- returnList[["figureCount"]]
  }
}

## Relative
for (i in 1:length(HMgeneSelections2)){
  if (length(unlist(HMgeneSelections2[[i]])) > 1){
    returnList <- addHeatmap2List(
        dataMatrix = dataMatrix,
        cluster_column_slices   = FALSE,
        cluster_columns         = FALSE,
        geneGroupList = HMgeneSelections2[[i]],
        relativeExpression = TRUE,
        cmdVec = NULL,
        tag = paste0(names(HMgeneSelections)[i], "_Rel"),
        showAllLegends = TRUE,
        figureCount = figureCount,
        plotList = plotList,
        maxNcharCatName = 10,
        dfMeta = dfMeta,
        group1ColorCol = "clusterColor", 
        group1NameCol = "clusterName",
        group2ColorCol = "treatmentGroupColor", 
        group2NameCol = "meta_Treatment",
        chnkVec = chnkVec,
        columnSplitCol = "clusterName"
        
    )
    
    plotList <- returnList[["plotList"]]
    chnkVec <- returnList[["chnkVec"]]
    figureCount <- returnList[["figureCount"]]
  }
}





###############################################################################
## Make Heatmap                                                              ##

#OsC@meta.data[["hmIdent2"]] <- paste0("C", OsC@meta.data[,"seurat_clusters"])

#Idents(OsC) <- "clusterName"

# levels <- Obio@parameterList$clusterNameOrder
# 
# levels(OsC) <- levels

## Deal with more than 5000 cells ##
# if (nrow(OsC@meta.data) > 5000){
#     set.seed(127)
#     n.cells <- 5000
#     OsC_HM <- OsC
#     OsC_HM@meta.data[["HM_sel"]] <- 0
#     selPos <- sample(x = nrow(OsC_HM@meta.data), size = n.cells, replace = FALSE, prob = NULL)
#     OsC_HM@meta.data[selPos, "HM_sel"] <- 1
#     
#     OsC_HM <- subset(x = OsC_HM, subset = HM_sel == 1)
#     
#     subsetString <- paste0("For this heatmap 5000 cells were randomly selected from ", nrow(OsC@meta.data)," cells in the experiment. ")
# } else {
#     OsC_HM <- OsC
#     subsetString <- ""
# }
# 
# ## Scale Data ##
# allGenes <- rownames(x = OsC_HM@assays$RNA)
# OsC_HM <- ScaleData(OsC_HM, verbose = FALSE, features=allGenes)
# 
# ## Set cluster order ##
# Idents(OsC_HM) <- "clusterName"
# Idents(OsC_HM) <- factor(Idents(OsC_HM), levels = Obio@parameterList[["clusterNameOrder"]])

#Idents(OsC_HM) <- "clusterName"

# selVec <- c(
#   grep("cluster_order", gsub("\\.", "_",names(OsC@meta.data))),
#   grep("clusterName", names(OsC@meta.data))
# )
# 
# if (length(selVec) == 2) {
#     dfCO <- unique(OsC@meta.data[,selVec])    
#     
#     names(dfCO) <- gsub("\\.", "_", names(dfCO))
# dfCO <- dfCO[order(dfCO$cluster_order, decreasing=F),]
# 
# Idents(OsC_HM) <- factor(Idents(OsC_HM), levels = as.vector(dfCO$clusterName))
# 
# Obio@parameterList$clusterNameOrder <- as.vector(dfCO$clusterName)
# }

## Order Heatmap Genes by cluster similarity

## For the moment: resetting heatmap list to keep it short ##

## Select heatmap genes ##
 

## Make general markers heatmpa ##


for (i in 1:length(Obio@parameterList[["cat2HMplotList"]])){
    tag <- paste0("HM_", names(Obio@parameterList$cat2HMplotList)[i])
    textSize <- 5
    HMname <- names(Obio@parameterList[["cat2HMplotList"]])[i]
    
    dfCol <- unique(OsC@meta.data[,c("clusterName", "clusterColor")])
    dfCol <- dfCol[dfCol$clusterName %in% Obio@parameterList[["clusterNameOrder"]], ]
    row.names(dfCol) <- dfCol$clusterName
    dfCol <- dfCol[Obio@parameterList[["clusterNameOrder"]], ]
    colors <- dfCol$clusterColor
    
    
    plotList[[tag]] <- DoHeatmap(
                object = OsC_HM,
                features = Obio@parameterList[["cat2HMplotList"]][[i]],
                #group.by = "hmIdent",
                draw.lines =T,
                label = T,
                group.bar = TRUE,
                slot = "scale.data",
                lines.width = 2, #With of separation lines in 'cells',
                size = 2,
                hjust = 0,
                angle = 90,
                group.colors = colors,
                #slim.col.label = TRUE,
                #remove.key = removeKey
            # ) + theme(legend.position = "none"
            ) + theme(
                  text = element_text(size=textSize),
                  legend.position="bottom" #,
                  #axis.text.x = element_text(angle = 90, hjust=1)
                
            ) + scale_fill_gradientn(colors = c("blue", "white", "red")
            ) 
    
    
    
    
    ## Save to file ##
            FNbase <- paste0(tag, VersionPdfExt)
            FN <- paste0(Obio@parameterList$reportFigDir, FNbase)
            FNrel <- paste0("report_figures/", FNbase)

            pdf(FN)
                print(plotList[[tag]])
            dev.off()

            
            
            ###################
            ## Add link to interactive heatmap for this project
                    
            #for (i in 1:length(residualClusterMarkers)){
            
            ## Create default ##
            link <- ""
            if (Obio@projectDetailList$species %in% c("mus_musculus", "homo_sapiens")){
                cat.name <- tag
                cat_type <- paste0("temp_", Obio@parameterList$project_id)
                        
                cat.description.text <- tag 
                        
                gene.vec <- Obio@parameterList[["cat2HMplotList"]][[i]]
                        
                gene.vec <- gene.vec[gene.vec != ""]
                gene.vec <- sort(na.omit(gene.vec))
                        
                ## Determine if cat exists ##
                        
                        
                catID <- add.category.to.lab.reference.table.hs(
                    host = Obio@dbDetailList$host,
                    pwd = db.pwd,
                    user = Obio@dbDetailList$db.user,
                    cat.ref.db = Obio@dbDetailList$ref.cat.db,
                    cat.ref.db.table = Obio@parameterList$lab.categories.table,
                    gene.vector = gene.vec,
                    gene.id = Obio@parameterList$geneIDcolumn, #options hgnc_symbol, mgi_symbol
                    mm.hs.conversion.file =  paste0(cwd, "/assets/annotation/homologene.data.txt"),
                    cat_name = cat.name,
                    cat_type = cat_type,
                    data_source = paste0(Obio@parameterList$labname, " Lab"),
                    comments_1 = "",
                    comments_2 = "",
                    new.lab.category.table = FALSE,
                    cat.description.db  = "internal_categories",
                    cat.description.db.table = "category_description",
                    cat.description.text = cat.description.text,
                    lab.name = Obio@parameterList$labname,
                    replaceExistingCatName = TRUE
                ) 
                    
            link <- paste0('Link to an interactive version of <a href="https://',urlString,'/',Obio@parameterList$project_id,'/category-view/',catID,'" target="_blank">this heatmap</a>. ')            
               
            }    
            #} ## End dfDat loop
            
            
            ## Done adding link
            ##############################
            
            
            
            ## Create R markdown chunk ##
            figLegend <- paste0(
                '**Figure ',
                figureCount,
                ':** ',HMname ,' Heatmap showing the most distinct marker genes in each cluster. ' , subsetString,
                'Download a pdf of this figure <a href="',FNrel,'" target="_blank">here</a>. ',
                link
            )


            



            figureCount <- figureCount + 1

            NewChnk <- paste0(
                "#### Heatmap ", HMname,
                "\n```{r Heatmap_", tag,
                ", results='asis', echo=F, eval=TRUE, warning=FALSE, fig.cap='",
                figLegend,"'}\n",
                "\n",
                "\n print(plotList[['",tag,"']])",
                "\n cat(  '\n')",
                "\n\n\n```\n"
            )

        
    
    chnkVec <- c(
        chnkVec,
        NewChnk
)
    
}



rm(OsC_HM)


## Done making Heatmap                                                       ##
###############################################################################

###############################################################################
## Make dotplot 

Idents(OsC) <- "clusterName"

# levels <- paste0(
#     "C",
#     sort(unique(OsC@meta.data[,"seurat_clusters"]))
#  )
# 
# levels(OsC) <- levels
dfGeneralMarkersFilt <- Obio@dataTableList[["dfGeneralMarkersFilt"]]
    
dfTop1 <- data.frame(dfGeneralMarkers %>% group_by(cluster) %>% top_n(1, avg_diff))
dfTop5 <- data.frame(dfGeneralMarkers %>% group_by(cluster) %>% top_n(5, avg_diff))

dpGenes <- as.vector(unique(dfTop5$gene))


dpGenes <- as.vector(unique(dfTop5$gene))

if (length(dpGenes) >= 50){
  dpGenes <- as.vector(unique(dfTop1$gene))  
}


#dpGenes <- rev(dpGenes[!(duplicated(dpGenes))])

tag <- paste0("Dotplot_", "Var_Genes")
textSize <- 5

dfCol <- unique(OsC@meta.data[,c("clusterName", "clusterColor")])
if(!is.null(Obio@parameterList$clusterNameOrder)){
    row.names(dfCol) <- dfCol$clusterName
    dfCol <- dfCol[Obio@parameterList$clusterNameOrder,]
}

colVec <- as.vector(dfCol$clusterColor)
names(colVec) <- dfCol$clusterName
textSize <- 2
if (length(colVec) > 5){
    textSize <-1
} else if (length(colVec) > 20){
    textSize <- 0.75
} else if (length(colVec) > 40){
    textSize <- 0.5
}


Idents(OsC) <- "clusterName"
Idents(OsC) <- factor(Idents(OsC), levels = Obio@parameterList[["clusterNameOrder"]])

#OsC@meta.data$clusterName <- factor(OsC@meta.data$clusterName, levels = #Obio@parameterList[["clusterNameOrder"]])


plotList[[tag]] <- DotPlotSB(
        object = OsC,
        features = dpGenes,
        assay = "RNA",
        #cols = cols,
        group.by = NULL,
        split.by = NULL,
        dot.scale = 4,
        col.min = 0,
        col.max = 5
    ) + ggtitle(gsub("_", "", tag)
    ) + xlab(""
    ) + coord_fixed(
    # ) + coord_flip(
    ) + theme_bw() +
  theme(axis.text.x = element_text(size=rel(textSize), angle = 45, hjust=1, color = colVec))

# plotList[[tag]] <- DotPlot(
#         object = OsC,
#         features = dpGenes,
#         assay = "RNA",
#         #cols = cols,
#         group.by = NULL,
#         split.by = NULL,
#         dot.scale = 4,
#         col.min = 0,
#         col.max = 5
#     ) + ggtitle(gsub("_", "", tag)
#     ) + xlab(""
#     ) + coord_fixed(
#     #) + coord_flip(
#     ) + theme_bw() +
#   theme(axis.text.x = element_text(size=rel(0.5), angle = 45, hjust=1, color = colVec))
#     
    

## Save to file ##
            FNbase <- paste0(tag, VersionPdfExt)
            FN <- paste0(Obio@parameterList$reportFigDir, FNbase)
            FNrel <- paste0("report_figures/", FNbase)

            pdf(FN)
                print(plotList[[tag]])
            dev.off()


            ## Create R markdown chunk ##
            figLegend <- paste0(
                '**Figure ',
                figureCount,
                ':** Dotplot showing showing selected marker genes. ',
                'Download a pdf of this figure <a href="',FNrel,'" target="_blank">here</a>. '
            )






            figureCount <- figureCount + 1

            NewChnk <- paste0(
                "#### Dotplot Markers",
                "\n```{r Dotplot_var_",
                ", results='asis', echo=F, eval=TRUE, warning=FALSE, fig.cap='",
                figLegend,"'}\n",
                "\n",
                "\n print(plotList[['",tag,"']])",
                "\n cat(  '\n')",
                "\n\n\n```\n"
            )

        
    
    chnkVec <- c(
        chnkVec,
        NewChnk
)    
    
## Done making dotplot                                                       ##
###############################################################################

############################
## Make cat feature plot

## done making cat feature plot
################################

if (length(plotList) > 3){
    tabVar <- ".tabset .tabset-fade .tabset-dropdown"
} else {
    tabVar <- ".tabset .tabset-fade .tabset-pills"
}    
    
```


### Heatmaps and Dotplots {`r tabVar`}

In this section heatmaps and dotplots for various gene categories are provided. 

```{r Cluster_overview, echo=TRUE, eval=TRUE, warning=FALSE, results="asis"}

cat(paste(knit(text = chnkVec, quiet = T), collapse = '\n'))

```