"<!-- Set PArameters Module -->
<!-- Set the chnkPrefix to make all chunks unique in the overall folder -->
```{r partB_pca_loadings, echo=TRUE, eval=TRUE, warning=FALSE}
chnkPrefix <- "partB.pca.loadings."
VersionPdfExt <- VersionPdfExt <- paste0(".",chnkPrefix,"V", gsub("-", "", Sys.Date()), ".pdf")

```



### PCA Gene and Cell Plots {.tabset .tabset-fade .tabset-pills}

```{r elbow_plot, fig.height=6, fig.width=10, fig.cap=paste0("**Figure, ",figureCount,": Elbowplot** Variance explained per PCA dimension")}
figureCount <- figureCount + 1
# An alternative heuristic method generates an 'Elbow plot': a ranking of principle components based on the percentage of variance explained by each one (`ElbowPlot` function). In this example, we can observe an 'elbow' around PC9-10, suggesting that the majority of true signal is captured in the first 10 PCs.

ElbowPlot(object = OsC) +  theme(
    axis.text.y   = element_text(size=8),
    axis.text.x   = element_text(size=8),
    axis.title.y  = element_text(size=8),
    axis.title.x  = element_text(size=8),
    axis.line = element_line(colour = "black"),
    panel.border = element_rect(colour = "black", fill=NA, size=1),
    plot.title = element_text(hjust = 0.5, size = 12)
) + ggtitle(paste0("Variance per PCA Dimension"))

## Plot variance per PCA dimension ##

```


```{r PCA_dataprep, echo=TRUE, eval=TRUE, warning=FALSE,  results=F}


## Add PCA coordinates ##
dfTemp <- data.frame(OsC@reductions$pca@cell.embeddings)[, 1:20]
OsC <- addDf2seuratMetaData(
    obj = OsC, 
    dfAdd = dfTemp
)


## Add UMAP coordinates to Metadata ##
dfAdd <- data.frame(OsC@reductions$umap@cell.embeddings)

OsC <- addDf2seuratMetaData(
    obj = OsC, 
    dfAdd = dfAdd
)

## Add tSNE coordinates to Metadata ##
dfAdd <- data.frame(OsC@reductions$tsne@cell.embeddings)

OsC <- addDf2seuratMetaData(
    obj = OsC, 
    dfAdd = dfAdd
)


Obio@dataTableList[["meta.data"]] <- OsC@meta.data
dfDat <- Obio@dataTableList$meta.data

PCvec <- names(dfDat)[grep("PC_", names(dfDat))] 
oddEven <- gsub("PC_", "", PCvec )
oddEven <- ifelse(as.numeric(oddEven) %% 2 == 0, "even", "odd")

xVec <- PCvec[oddEven == "odd"]
yVec <- PCvec[oddEven == "even"]

minLength <- min(length(xVec), length(yVec))
xVec <- xVec[1:minLength]
yVec <- yVec[1:minLength]



pcVec <- xVec
chnkVec <- as.vector(NULL, mode = "character")
plotListCell <- list()
plotListGene <- list()


xMax <- ceiling(max(dfDat[,"PC_1"]))
xMin <- floor(min(dfDat[,"PC_1"]))
aLimit <- max(abs(c(xMax, xMin)))

###############################################################################
## Collect top-enriched genes                                                ##
EnrichedGenesList <- list()
## Done                                                                      ##
###############################################################################

for (i in 1:length(xVec)){
    ## changed out 202103
    #dfDat <- Obio@dataTableList$meta.data
    dfDat <- OsC@meta.data
  
    dfSel <- dfDat
    selXY <- c(xVec[i], yVec[i])
    colCol <- "clusterName"
    
    tag <- paste0(xVec[i], "and", yVec[i])
    tag <- gsub("_", "", tag)
    
    ## Make Cell level PCA
    plotListCell[[tag]] <- ggplot(data=dfDat, aes_string(selXY[1] , selXY[2], col=colCol, shape="sampleName")
    ) + geom_vline(xintercept = 0, color = "grey", size=0.5
    ) + geom_hline(yintercept = 0, color = "grey", size=0.5
    ) + geom_point()+ ggtitle(paste0("PCA - Cell Level")
    ) + theme_bw(
    ) +  theme(
        axis.text.y   = element_text(size=8),
        axis.text.x   = element_text(size=8),
        axis.title.y  = element_text(size=8),
        axis.title.x  = element_text(size=8),
        axis.line = element_line(colour = "black"),
        panel.border = element_rect(colour = "black", fill=NA, size=1),
        plot.title = element_text(hjust = 0.5, size = 12)
    ) + xlim(-1*aLimit, aLimit)  + ylim(-1*aLimit, aLimit) 
    
    h <- sum(c("clusterName", "sampleColor") %in% names(dfDat))
    if (h ==2){
        dfCol <- unique(dfDat[,c("clusterName", "clusterColor")])
        colVec <- as.vector(dfCol$clusterColor)
        names(colVec) <- as.vector(dfCol$clusterName)
        plotListCell[[tag]] <- plotListCell[[tag]] + scale_colour_manual("clusterName" ,values = colVec
            ) 
    }
    
    plotListCell[[tag]] <- plotListCell[[tag]] + guides(color=guide_legend(title="Clusters"), shape=guide_legend(title="Samples")
    )
    
    ## Save to file ##
    FNbase <- paste0("PCA.cell.level.", xVec[i],".", yVec[i], ".", VersionPdfExt)
        FN <- paste0(Obio@parameterList$reportFigDir, FNbase)
    FNrel <- paste0("report_figures/", FNbase)
    
    pdf(FN)
        print(plotListCell[[tag]])
    dev.off()
    
    # link <- paste0('<a href="https://',urlString,'/',Obio@parameterList$project_id,'/pca?x_axis=',gsub('_', '', xVec[i]),'&y_axis=',gsub('_', '', yVec[i]),'" target = "_blank">here</a>')
    
    if (exists("shinyURL") & !is.null(shinyURL)){
        
            link <- paste0(
              'An interactive version of this figure with additional viewing options can be found <a href="',shinyURL,'?_inputs_&y_axis=%22',yVec[i],'%22&colorBy=%22clusterName%22&splitByColumn=%22all%22&x_axis=%22',xVec[i],'%22" target="_blank">here</a>. '
            )
            
    } else {
        link <- ""
    }
    
    figCap <- paste0(
        '**Figure, ' ,figureCount,'A:** Cell-level PCA plot for dimensions ', xVec[i], ' and ', yVec[i],'. ', 
        'Download a pdf of this figure <a href="',FNrel,'" target="_blank">here</a>. ',
        'An interactive version of this figure can be found ', link, '. '
    )
    
    
    NewChnk <- paste0(
        "#### PCA Cell Level ", xVec[i], " and ",yVec[i],
        "\n```{r PCAcells_", i,
        ", results='asis', echo=F, eval=TRUE, warning=FALSE, fig.cap='",
        figCap,"'}\n",
        "\n",
        "\n print(plotListCell[['",tag,"']])",
        "\n cat(  '\n')",
        "\n\n\n```\n"   
    )
    
    chnkVec <- c(
        chnkVec,
        NewChnk
    )
    
    ## Done with cells                                                       ##
    ###########################################################################
    
    ###########################################################################
    ## Start with genes                                                      ##
    dfPCADat <- data.frame(Loadings(OsC, reduction = "pca"))
        dfPCADat[["gene"]] <- row.names(dfPCADat)
    
    dfPCADat <- gather(
        dfPCADat, 
        condition, 
        measurement, 1:(ncol(dfPCADat)-1), 
        factor_key=TRUE
    )

    Obio@dataTableList[["dfPCAloadings"]] <- dfPCADat

    ## Make Gene Level PCA ##
    dfPCADat <- data.frame(Loadings(OsC, reduction = "pca"))
    dfPCADat[["gene"]] <- row.names(dfPCADat)
    dfPCADat <- gather(
        dfPCADat,
        condition,
        measurement, 1:(ncol(dfPCADat)-1),
        factor_key=TRUE
    )
    
    dfLoad <- dfPCADat
    Obio@dataTableList$dfPCAloadings <- dfLoad
    ## Plot ##
    selXY <- c(xVec[i], yVec[i])
    dfSel <- filter(dfLoad, condition %in% selXY)
    dfSel <- dfSel %>% spread(key=condition, value=measurement)
    row.names(dfSel) <- dfSel$gene
    dfSel[["highlight"]] <- ""
    dfSel[["cat"]] <- ""
    dfSel[["selX"]] <- ""
    dfSel[["selY"]] <- ""
    dfSel <- dfSel[order(dfSel[,selXY[1]], decreasing = FALSE), ]
    dfSel[1:15, "highlight"] <- "+"
    
    ## Use two standard deviations for enrichment ##
    twoSD <- 2*sd(dfSel[,selXY[1]])
    twoSDxLine <- 2*sd(dfSel[,selXY[1]])
    gSvec <- dfSel[dfSel[,selXY[1]] < -1* twoSD, "gene"]
    
    if (length(gSvec) > 3){
      EnrichedGenesList[[paste0(selXY[1], "_neg")]]<- as.vector(gSvec)  
      dfSel[dfSel$gene %in% gSvec, "cat"] <- "Selected"
      dfSel[dfSel$gene %in% gSvec, "selX"] <- "+"
    } else {
      EnrichedGenesList[[paste0(selXY[1], "_neg")]]<- as.vector(dfSel$gene[1:15])
      dfSel[dfSel$gene %in% as.vector(dfSel$gene[1:15]), "cat"] <- "Selected"
      dfSel[dfSel$gene %in% as.vector(dfSel$gene[1:15]), "selX"] <- "+"
    }
    
    
    dfSel <- dfSel[order(dfSel[,selXY[1]], decreasing = TRUE), ]
    dfSel[1:15, "highlight"] <- "+"
    gSvec <- dfSel[dfSel[,selXY[1]] >  twoSD, "gene"]
    
    if (length(gSvec) > 3){
      EnrichedGenesList[[paste0(selXY[1], "_pos")]]<- as.vector(gSvec)  
      dfSel[dfSel$gene %in% gSvec, "cat"] <- "Selected"
      dfSel[dfSel$gene %in% gSvec, "selX"] <- "+"
    } else {
      EnrichedGenesList[[paste0(selXY[1], "_pos")]]<- as.vector(dfSel$gene[1:15])
      dfSel[dfSel$gene %in% as.vector(dfSel$gene[1:15]), "cat"] <- "Selected"
       dfSel[dfSel$gene %in% as.vector(dfSel$gene[1:15]), "selX"] <- "+"
    }
    
    ## Now dim 2
    dfSel <- dfSel[order(dfSel[,selXY[2]], decreasing = FALSE), ]
    dfSel[1:15, "highlight"] <- "+"
    
    twoSD <- 2*sd(dfSel[,selXY[2]])
    twoSDyLine <- 2*sd(dfSel[,selXY[2]])
    gSvec <- dfSel[dfSel[,selXY[2]] < -1* twoSD, "gene"]
    
    if (length(gSvec) > 15){
      EnrichedGenesList[[paste0(selXY[2], "_neg")]]<- as.vector(gSvec)
      dfSel[dfSel$gene %in% gSvec, "cat"] <- "Selected"
      dfSel[dfSel$gene %in% gSvec, "selY"] <- "+"
    } else {
      EnrichedGenesList[[paste0(selXY[2], "_neg")]]<- as.vector(dfSel$gene[1:15])
      dfSel[dfSel$gene %in% as.vector(dfSel$gene[1:15]), "cat"] <- "Selected"
      dfSel[dfSel$gene %in% as.vector(dfSel$gene[1:15]), "selY"] <- "+"
    }
    
    
    dfSel <- dfSel[order(dfSel[,selXY[2]], decreasing = TRUE), ]
    dfSel[1:15, "highlight"] <- "+"
    gSvec <- dfSel[dfSel[,selXY[2]] >  twoSD, "gene"]
    
    if (length(gSvec) > 3){
      EnrichedGenesList[[paste0(selXY[2], "_pos")]]<- as.vector(gSvec)  
      dfSel[dfSel$gene %in% gSvec, "cat"] <- "Selected"
      dfSel[dfSel$gene %in% gSvec, "selY"] <- "+"
    } else {
      EnrichedGenesList[[paste0(selXY[2], "_pos")]]<- as.vector(dfSel$gene[1:15])
      dfSel[dfSel$gene %in% as.vector(dfSel$gene[1:15]), "cat"] <- "Selected"
      dfSel[dfSel$gene %in% as.vector(dfSel$gene[1:15]), "selY"] <- "+"
    }
    
    ## Done
    
    colVec <- c("grey", "black")
    names(colVec) <- c("", "Selected")
    
    plotListGene[[tag]] <- ggplot(data=dfSel, aes_string(x=selXY[1],y=selXY[2], col="cat")
    ) + geom_vline(xintercept = 0, color = "grey", size=0.5
    ) + geom_hline(yintercept = 0, color = "grey", size=0.5
    ) + geom_vline(xintercept = c(twoSDxLine, -1* twoSDxLine), color = "red", lty=2,size=0.5
    ) + geom_hline(yintercept = c(twoSDyLine, -1* twoSDyLine), color = "red", lty=2,size=0.5
    ) + geom_hline(yintercept = 0, color = "grey", size=0.5
    ) + geom_point() + scale_color_manual(values=colVec
    #) + ggtitle(paste0("PCA - Cell Level")
    ) + theme_bw(
    ) +  theme(
        axis.text.y   = element_blank(), # element_text(size=8),
        axis.text.x   = element_blank(), #element_text(size=8),
        axis.title.y  = element_blank(), #element_text(size=8),
        axis.title.x  = element_blank(), #element_text(size=8),
        axis.line = element_line(colour = "black"),
        legend.position = "none",
        panel.border = element_rect(colour = "black", fill=NA, size=1),
        #plot.title = element_text(hjust = 0.5, size = 12)
    )  #+ guides(col = guide_legend(override.aes = list(shape = 16, size = legendDotSize)))
    
    points <-  as.vector(unique(dfSel[dfSel$highlight=="+", "gene"]))
    plotListGene[[tag]] <- LabelPoints(plot = plotListGene[[tag]], points =points, repel = TRUE, xnudge = 0, ynudge = 0)
    
    ## Make historgrams
    library(ggpubr)
    library(gridExtra)
    
    colVec <- c("grey", "black")
    names(colVec) <- c("", "+")
    
    
    hist_top <- ggplot(data=dfSel)+ geom_histogram(aes_string(x= selXY[1],fill="selX", color="selX"), binwidth=0.001) +  theme(
        axis.text.y   = element_blank(),
        axis.text.x   = element_blank(),
        axis.title.y  = element_blank(),
        axis.title.x  = element_blank(),
        legend.position = "none",
        axis.line = element_line(colour = "black"),
        panel.border = element_rect(colour = "black", fill=NA, size=1),
        plot.title = element_text(hjust = 0.5, size = 12)
    ) + geom_vline(xintercept = c(twoSDxLine, -1* twoSDxLine), color = "red", lty=2,size=0.5
    ) + scale_color_manual(values=colVec
    ) + scale_fill_manual(values=colVec
    )
    
    empty <- ggplot()+  geom_blank() + theme(panel.border = element_rect(colour = "white", fill=NA, size=1),)
    
    #scatter <- plotListGene[[tag]] 
    
    hist_right <- ggplot(data=dfSel)+ geom_histogram(aes_string(x= selXY[2],fill="selY", color="selY"), binwidth=0.001) +  theme(
        axis.text.y   = element_blank(),
        axis.text.x   = element_blank(),
        axis.title.y  = element_blank(),
        axis.title.x  = element_blank(),
        legend.position = "none",
        axis.line = element_line(colour = "black"),
        panel.border = element_rect(colour = "black", fill=NA, size=1),
        plot.title = element_text(hjust = 0.5, size = 12)
    ) + geom_vline(xintercept = c(twoSDxLine, -1* twoSDxLine), color = "red", lty=2,size=0.5
    ) + scale_color_manual(values=colVec
    ) + scale_fill_manual(values=colVec
    ) + coord_flip()
    
    ## End histograms
    
    ## Arrange Figure ##
    pdf(pdfTemp)
    plotListGene[[tag]]  <- grid.arrange(hist_top, empty, plotListGene[[tag]] , hist_right, ncol=2, nrow=2, widths=c(4, 1), heights=c(1, 4))
 
    plotListGene[[tag]]  <- annotate_figure(
        plotListGene[[tag]],
        top = text_grob("PCA Loadings Gene Level", face = "bold", size = 12),
        bottom = text_grob(paste0("PCA Dim ",gsub("PC_", "", selXY[1])," Loadings"), size = 12),
        left = text_grob(paste0("PCA Dim ",gsub("PC_", "", selXY[2])," Loadings"), rot = 90, size = 12) #,
                     #right = text_grob(bquote("Superscript: ("*kg~NH[3]~ha^-1~yr^-1*")"), rot = 90),
                     #fig.lab = "Figure 1", fig.lab.face = "bold"
     )
    dev.off()
    unlink(pdfTemp)
    ## Done arranging figure ##
    
    
    ## Save to file ##
    FNbase <- paste0("PCA.cell.level.", xVec[i],".", yVec[i], VersionPdfExt)
    FN <- paste0(Obio@parameterList$reportFigDir, FNbase)
    FNrel <- paste0("report_figures/", FNbase)
    
    pdf(FN)
        plot(plotListGene[[tag]])
    dev.off()
    
    dim1 <- gsub("PC_", "", xVec[i])
    dim2 <- gsub("PC_", "", yVec[i])
    link <- paste0(
        '<a href="https://',urlString,'/',
        Obio@parameterList$project_id, 
        '/scatterplot?x_axis=add_counts_PCA_Dim_',
        dim1, 
        '_Loadings&y_axis=add_counts_PCA_Dim_',
        dim2,
        '_Loadings&highlight_gene=&cat_id=ag_lab_categories__10',
        '" target="_blank">here</a>'
    )
    
    figCap <- paste0(
        "**Figure, " ,figureCount,"B:**Gene-level PCA plot for dimensions ", xVec[i], " and ", yVec[i], ". An interactive version of this figure can be found ", link, ". "
    )
   
    
    NewChnk <- paste0(
        "\n```{r PCA_gene_level_", i,
        ", results='asis', echo=F, eval=TRUE, warning=FALSE, fig.cap='",
        figCap,"'}\n",
        "\n",
        "\n print(plotListGene[['",tag,"']])",
        "\n cat(  '\n')",
        "\n\n\n```\n"   
    )
    
    chnkVec <- c(
        chnkVec,
        NewChnk
    )
    
    ## Done with genes                                                       ##
    ###########################################################################
    figureCount <- figureCount + 1
}


if (length(plotListGene) > 3){
    tabVar <- ".tabset .tabset-fade .tabset-dropdown"
} else {
    tabVar <- ".tabset .tabset-fade .tabset-pills"
}

```

### Characterization of PCA Loadings {`r tabVar`}
```{r plot_PCADimPlots, echo=TRUE, eval=TRUE, warning=FALSE, results="asis"} 
cat(paste(knit(text = chnkVec, quiet = T), collapse = '\n'))
```


```{r pca_boxplot_dataprep, echo=T, eval=TRUE, warning=FALSE, results=F}
selVec <- c("clusterName", names(OsC@meta.data)[grep("^PC", names(OsC@meta.data))])

dfPCdat <- OsC@meta.data[, selVec]

ymin <- 1.1*min(dfPCdat$PC_1)
ymax <- 1.1*max(dfPCdat$PC_1)

h <- sum(c("clusterName", "clusterColor") %in% names(OsC@meta.data))
if (h ==2){
    dfCol <- unique(OsC@meta.data[,c("clusterName", "clusterColor")])
    clusterVec <- dfCol$clusterName
    clusterColVec <- as.vector(dfCol$clusterColor)
    names(clusterColVec) <- as.vector(dfCol$clusterName)
} else{
    clusterVec <- sort(unique(OsC@meta.data[,"clusterName"]))
    colVec <- hue_pal()(length(clusterVec))
    names(colVec) <- clusterVec
}



chnkVec <- as.vector(NULL, mode="character")
plotList <- list()

for (i in 1:length(clusterVec)){
    dfTemp <- dfPCdat[dfPCdat[,"clusterName"] == clusterVec[i],]
    dfTemp[,"clusterName"] <- NULL
  
  
  
    library(tidyr)
    dfTemp <- gather(dfTemp, PC)
  
    orderVec <- sort(as.numeric(gsub("PC_", "",unique(dfTemp$PC))))
    orderVec <- paste0("PC_", orderVec)
  
    dfTemp$PC <- factor(dfTemp$PC, levels = orderVec)
    Ncolumns <- length(unique(dfTemp$PC))
  
    a <- paste0("Cluster_", clusterVec[i])

    tag <- paste0("PCA_Cell_Distributions_", a)

    plotList[[tag]] <-ggplot(
        dfTemp, 
        aes(x=PC, y=value, fill = PC)
        ) + geom_hline(yintercept = 0, color = "black", size=0.5
        )  + geom_jitter(width=0.1,alpha=0.2
        ) + geom_boxplot(
        )  + theme_bw(
        ) +    theme(
            legend.position = "none",
            axis.text.y   = element_text(size=8),
            axis.text.x   = element_text(size=8, angle = 45,vjust = 1, hjust=1),
            axis.title.y  = element_text(size=8),
            axis.title.x  = element_text(size=8),
            axis.line = element_line(colour = "black"),
            panel.border = element_rect(colour = "black", fill=NA, size=1),
            plot.title = element_text(hjust = 0.5, size = 12)
        ) + ggtitle(paste0("PCA Distribution: ", gsub("_", " ", a))
        ) + ylim(ymin, ymax) + scale_fill_manual(values=rep(as.vector(clusterColVec[i]), Ncolumns))  
    
    ## Save to file ##
    FNbase <- paste0(tag, VersionPdfExt)
        FN <- paste0(Obio@parameterList$reportFigDir, FNbase)
    FNrel <- paste0("report_figures/", FNbase)
    
    pdf(FN)
        print(plotList[[tag]])
    dev.off()
    
    
    figCap <- paste0(
        '**Figure, ' ,
        figureCount,
        ':** This plot may help you to identify PCA dimensions, in which marker genes for cluster ',
        clusterVec[i],
        ' become evident. Download a pdf of this figure <a href="',FNrel,'" target="_blank">here</a>. '
    )
    
    figureCount <- figureCount + 1
    
    NewChnk <- paste0(
        "#### ", tag,
        "\n```{r ", tag,
        ", results='asis', echo=F, eval=TRUE, warning=FALSE, fig.cap='",
        figCap,"'}\n",
        "\n",
        "\n print(plotList[['",tag,"']])",
        "\n cat(  '\n')",
        "\n\n\n```\n"   
    )
    
    chnkVec <- c(
        chnkVec,
        NewChnk
    )
}

if (length(plotList) > 3){
    tabVar <- ".tabset .tabset-fade .tabset-dropdown"
} else {
    tabVar <- ".tabset .tabset-fade .tabset-pills"
}
```

### Characterize PCA Dimensions {`r tabVar`}
```{r pca_boxplot, echo=TRUE, eval=TRUE, warning=FALSE, results="asis"} 
cat(paste(knit(text = chnkVec, quiet = T), collapse = '\n'))

```


```{r create-pca-enrichment-data, echo=T, eval=TRUE, warning=FALSE, results=F}
library(knitr)
library(ggplot2)

#save.image("temp.RData")



library(clusterProfiler)
    library(ggplot2)
    
    gmtList <- list()
    pos <- grep("clusterSigEnrichmentList", slotNames(Obio))
    
    if (length(pos) > 0){
    if (is.null(Obio@clusterSigEnrichmentList)){
      dbtableList <- list(
          "Cell Type Signatures" = "mysigdb_sc_sig",
          "Cell Type Signatures" = "cibersort_L22",
          "GO-MF" = "mysigdb_c5_MF",
          "Pathways" = "mysigdb_c2_1329_canonical_pathways",
          "Allen_Brain_Atlas" = "Allen_Brain_Atlas"
      )
    } else {
        dbtableList <- Obio@clusterSigEnrichmentList
    }
    } else {
      dbtableList <- list(
          "Cell Type Signatures" = "mysigdb_sc_sig",
          "Cell Type Signatures" = "cibersort_L22",
          "GO-MF" = "mysigdb_c5_MF",
          "Pathways" = "mysigdb_c2_1329_canonical_pathways",
          "Allen_Brain_Atlas" = "Allen_Brain_Atlas"
      )
    }
    
    for (i in 1:length(dbtableList)){
        
        dfTemp <- unique(import.db.table.from.db(
            host = Obio@dbDetailList$host,
            dbname = Obio@dbDetailList$ref.cat.db,
            dbtable = dbtableList [[i]],
            password = db.pwd,
            user = Obio@dbDetailList$db.user
        ))
        
        rmVec <- grep("temp_", dfTemp$cat_type)
        if (length(rmVec) > 0){
            dfTemp <- dfTemp[-rmVec, ]
        }
        
        dfTemp <- unique(dbcat2gmt(
            dfTemp, # As downloaded from reference_categories_db_new database
            gene.id.column = queryGS
        ))
        
        dfTemp <- dfTemp[!duplicated(dfTemp[,1]), ]
        
        write.table(
            dfTemp,
            "temp.gmt.txt",
            row.names = F, 
            sep = "\t",
            col.names = F,
            quote = F
        )
        
        CPgmt <- read.gmt("temp.gmt.txt")
        unlink("temp.gmt.txt")
        CPgmt <- unique(CPgmt[CPgmt$gene != "", ])
        
        gmtList[[dbtableList[[i]]]] <- CPgmt
    }
    
    ## Edit collection names for plot
    names(gmtList) <- gsub("mysigdb_", "",names(gmtList))
    names(gmtList) <- gsub("c2_1329_canonical_p", "P",names(gmtList))
    names(gmtList) <- gsub("sc_sig", "CellSig",names(gmtList))
    names(gmtList) <- gsub("cibersort_L22", "CellSig",names(gmtList))
    names(gmtList) <- gsub("c5_", "GO_",names(gmtList))
    ## Done creating gmt list
    ###########################
    
    ## Select colors ##
    library(scales)
    enrCols <- hue_pal()(length(gmtList))
    names(enrCols) <- names(gmtList)

PCAdimensions <- paste0("PC_", 1:20)

plotList <- list()
chnkVec <- as.vector(NULL, mode = "character")



for (j in 1:length(PCAdimensions)){
    posTestGeneSet <- as.vector(
        unique(
            EnrichedGenesList[[paste0(PCAdimensions[j], "_pos")]]
        )
    )
    
    
    negTestGeneSet <- as.vector(
        unique(
            EnrichedGenesList[[paste0(PCAdimensions[j], "_neg")]]
        )
    )
   
    
    ###########################################################################
    ## Create GMT file for category enrichment                               ##
    
    ###########################
    ## Create gmt list
    ## Retrieve gmt files from database
    ## Add custom gmt files
    
    
    
    
    ## Done                                                                  ##
    ###########################################################################
     
    library(clusterProfiler)
    library(ggplot2)
    library(tidyr)
        
        if (Obio@parameterList$geneIDcolumn != "mgi_symbol" & Obio@parameterList$geneIDcolumn != "hgnc_symbol") {
            queryGS <- "hgnc_symbol" 
        } else {
            queryGS <- Obio@parameterList$geneIDcolumn
        }
        
        if (Obio@parameterList$host == "10.27.241.234"){
            urlString <- "biologic.thecrick.org"
        } else {
            urlString <- "biologic.crick.ac.uk"
        }
    
    pvalueCutoff <- 0.5
    topMaxCat <- 10
    
    ## Get background gene set ##
    #backgroundGeneVec <- row.names(OsC[["RNA"]]@counts)
    if ((length(posTestGeneSet) >= 3) | (length(negTestGeneSet) >= 3)){
        ## Do enrichment ##
        first <- TRUE
        if (length(posTestGeneSet) >= 3){
            for (k in 1:length(gmtList)){
                    egmt <- data.frame(
                        enricher(
                            negTestGeneSet, 
                            TERM2GENE=gmtList[[k]],
                            pvalueCutoff = pvalueCutoff
                        )
                    )
                    if (!is.null(egmt)){
                        if (nrow(egmt) > 0){
                            egmt[["Collection"]] <- substr(names(gmtList)[k], 1,10)
                        }
                        if (first){
                            dfTempEnriched <- egmt    
                            first <- FALSE
                        } else {
                            dfTempEnriched <- rbind(
                                dfTempEnriched, 
                                egmt
                            )    
                        }
                        
                    }
            }
            if (nrow(dfTempEnriched) > 0){
                dfTempEnriched[["direction"]] <- "positive"
                dfTempEnriched[["log10FDR"]] <- -1*log10(dfTempEnriched$p.adjust)
                dfTempEnriched <- dfTempEnriched[order(dfTempEnriched$log10FDR, decreasing = T),]
                dfTempEnriched <- na.omit(dfTempEnriched)
                
                if (nrow(dfTempEnriched) > topMaxCat){
                    dfTempEnriched <- dfTempEnriched[1:topMaxCat, ]
                }
            }
          
            
        } # end positive
            
            ## Now the negative side ##
            if (length(negTestGeneSet) >= 3){
            first <- TRUE
            for (k in 1:length(gmtList)){
                    egmt <- data.frame(
                        enricher(
                            posTestGeneSet, 
                            TERM2GENE=gmtList[[k]],
                            pvalueCutoff = pvalueCutoff
                        )
                    )
                    if (!is.null(egmt)){
                        if (nrow(egmt) > 0){
                            egmt[["Collection"]] <- substr(names(gmtList)[k], 1,10)
                        }
                        if (first){
                            dfTempEnrichedNeg <- egmt    
                            first <- FALSE
                        } else {
                            dfTempEnrichedNeg <- rbind(
                                dfTempEnrichedNeg, 
                                egmt
                            )    
                        }
                        
                    } 
            }
            if (nrow(dfTempEnrichedNeg) > 0){
                dfTempEnrichedNeg[["direction"]] <- "negative"
                dfTempEnrichedNeg[["log10FDR"]] <- log10(dfTempEnrichedNeg$p.adjust)
                dfTempEnrichedNeg <- dfTempEnrichedNeg[order(dfTempEnrichedNeg$log10FDR, decreasing = F),]
                dfTempEnrichedNeg <- na.omit(dfTempEnrichedNeg)
                
                if (nrow(dfTempEnrichedNeg) > topMaxCat){
                    dfTempEnrichedNeg <- dfTempEnrichedNeg[1:topMaxCat, ]
                }
            }
            } # end negative
        
            
            
            ## Make plot 
            if ((nrow(dfTempEnriched) > 0) | (nrow(dfTempEnrichedNeg) > 0)){
            
            
            
            
            dfSel <- rbind(
                dfTempEnriched,
                dfTempEnrichedNeg
            )
            
            dfSel <- na.omit(dfSel)
            dfSel <- dfSel[order(dfSel$log10FDR),]
            dfSel$log10FDR <- round(dfSel$log10FDR, 2)
            
            dfSel[["Category"]] <- ""
            dfSel[dfSel$log10FDR >= 0, "Category"] <- "Enr."
            dfSel[dfSel$log10FDR < 0, "Category"] <- "Depl."
            
            for (l in 1:nrow(dfSel)){
                if (nchar(dfSel[l, "ID"]) > 30){
                    part1 <- substr(dfSel[l, "ID"], 1, 30)
                    part2 <- substr(dfSel[l, "ID"], 31, 60)
                    dfSel[l, "ID"] <- paste0(part1, " \\n", part2)
                  
                }
            }
            
            
            #dfSel$Term <- gsub("\\(GO", "\\\n\\(GO", dfSel$Term)
            
            dfSel$ID <- factor(dfSel$ID, levels = unique(dfSel$ID))
            
            
            
            plotList[[paste0("PCA_ENR_", j)]] <- ggplot(
                data=dfSel, aes(x= ID, y=log10FDR, fill=Collection, order=log10FDR)
            ) + geom_bar(stat="identity", colour="black"
            ) + coord_flip() +scale_fill_manual(values=enrCols
            ) + theme_bw(
            )  +  theme(
                axis.text.y   = element_text(size=8),
                axis.text.x   = element_text(size=8),
                axis.title.y  = element_text(size=8),
                axis.title.x  = element_text(size=8),
                axis.line = element_line(colour = "black"),
                panel.border = element_rect(colour = "black", fill=NA, size=1),
                plot.title = element_text(hjust = 0.5, size = 12)
            )  + labs(title = paste0("Cluster ", PCAdimensions[j]," enriched genes") ,y = "-log10(FDR)", x = ""
            ) + geom_hline(yintercept = c(-log10(0.05), log10(0.05)), color = "grey", size=0.5, lty=2
            ) + geom_hline(yintercept = 0, color = "black", size=0.5
            ) 
            cat("  \n")
            
            
            
            ## Save to file ##
            FNbase <- paste0("PCA_Cluster_", PCAdimensions[j],".enriched.genes", VersionPdfExt)
            FN <- paste0(Obio@parameterList$reportFigDir, FNbase)
            FNrel <- paste0("report_figures/", FNbase)
            
           
            pdf(FN)
            print(plotList[[paste0("PCA_ENR_", j)]])
            dev.off()
            
            link <- paste0(
                '<a href="https://', urlString, '/',
                Obio@parameterList$project_id,
                '/category-view?category_type=GO-BP" target="_blank">CategoryView</a>'
            )
            
            ## Create R markdown chunk ##
            figLegend <- paste0(
                '**Figure ', 
                figureCount, 
                '**: GO-BP category enrichment analysis for the top genes that have  <font color = "',colVec[2],'"> the most positive </font> and <font color = "',colVec[1],'">the most negative</font> PCA loading values in dimension ', 
               PCAdimensions[j],
                ' associated with them. Download a pdf of this figure <a href="',FNrel,'" target="_blank">here</a>. To view these gene sets in the context of your data, go to ',link,' and find these categories using the search box.'
            )
            figureCount <- figureCount + 1 
            
            NewChnk <- paste0(
                "#### ", PCAdimensions[j],
                "\n```{r enrichr_",
                j,", results='asis', echo=F, eval=TRUE, warning=FALSE, fig.cap='",
                figLegend,"'}\n",
                "\n",
                "\n print(plotList[['",paste0("PCA_ENR_", j),"']])",
                "\n cat(  '\n')",
                "\n\n\n```\n"   
            )
            
            chnkVec <- c(
                chnkVec,
                NewChnk
            )
        }
            
            
            ## done with plot 
            
    } ## Done with per dimension loops
}        
      
 

if (length(plotList) > 3){
    tabVar <- ".tabset .tabset-fade .tabset-dropdown"
} else {
    tabVar <- ".tabset .tabset-fade .tabset-pills"
}
```

### Characterize PCA Dimensions {`r tabVar`} 
```{r create-pca-enrichment-plot, echo=T, eval=TRUE, warning=FALSE, results='asis'}
###############################################################################
## Do category enrichment on clusters                                        ##
cat(paste(knit(text = chnkVec, quiet = T), collapse = '\n'))
## Done doing enrichment on clusters                                         ##
###############################################################################


```
