<!-- Set Parameters Module -->
<!-- Set the chnkPrefix to make all chunks unique in the overall folder -->
# Branch 1
```{r, echo=TRUE, eval=TRUE, warning=FALSE}

## Export Pseudotime to Seurat object ##
# Branch 1

branchSelectionCol <- "seurat_clusters"
branchSelection <- c(2, 0, 1, 3)

#branch1 <- c(5, 9, 0, 6,3)
#branch1 <- c(5, 12, 1, 4, 2, 11)

branchName <- "branch1"

chnkPrefix <- paste0("T3.mc.", branchName, ".")
VersionPdfExt <- VersionPdfExt <- paste0(".",chnkPrefix,"V", gsub("-", "", Sys.Date()), ".pdf")

#install.packages("V8")
#renv::install("cole-trapnell-lab/leidenbase")
#renv::install("cole-trapnell-lab/monocle3")

## Requires conda environment as gdal can't be installed. ##
## remember module purge to flush old R versions
# list all conda environments
# conda env list

# conda activate R-monocle3
# R-version of the above: R 4.0.2


invertMonoclePseudotime <- FALSE
useCachedMonocleObject <- TRUE
startClusterID <- 2
startClusterColName <- "seurat_clusters"
plotTopNgenes <- 100
nMonocleTimeBins <- 100
mainPTcol <- "Pseudotime_MC"

###############################################################################
## Gene list to plot                                                         ##
heatmapGeneListAdditions <- list(
    "Custom_GeneSet_Branch_1" = c(
    "HES1",
    "CEBPD",
    "ZFP36L2",
    "CLU",
    "KRT15",
    "KRT19",
    "FN1",
    "IFITM3",
    "CCL19",
    "PRRX1",
    "ARID5B",
    "HEY1",
    "ASCL1",
    "CLDN3",
    "CLDN4",
    "CLDN9",
    "CD24",
    "HES6",
    "NHLH1",
    "CFAP298",
    "GNG8",
    "STMN1",
    "KIF19",
    "METRN",
    "CIB2",
    "BEX1",
    "NEUROD1",
    "SOX4",
    "SOX2",
    "CHRNA1",
    "LSAMP",
    "SMIM18",
    "MYO6",
    "IRX2",
    "MYO15A",
    "ABCA5",
    "KCNH6",
    "CCER2",
    "POU4F3",
    "PCP4",
    "PKIB",
    "ATOH1",
    "TJAP1",
    "GRXCR1",
    "RBM24",
    "TMPRSS3",
    "USH2A",
    "PAX2",
    "STRC",
    "OTOF",
    "GRXCR2",
    "TRIM36",
    "RSPH1",
    "CD164L2",
    "CRIP3",
    "FAM183A",
    "C1orf194",
    "C1orf232",
    "MINDY4B",
    "CCDC81",
    "C2orf40",
    "SMPX"
  )
)

## Ordered gene list ##

heatmapGeneListAdditionsOrdered <- list(
    "Ordered_GeneSet_Branch_1" = c(
        "CLU",
        "KRT19",
        "KRT15",
        "FN1",
        "IFITM3",
        "PRRX1",
        "CEBPD",
        "ARID5B",
        "ZFP36L2",
        "HES1",
        "HEY1",
        "ASCL1",
        "CLDN3",
        "CLDN4",
        "CLDN9",
        "CD24",
        "SOX4",
        "NEUROD1",
        "HES6",
        "NHLH1",
        "CFAP298",
        "GNG8",
        "STMN1",
        "METRN",
        "BEX1",
        "SOX2",
        "CHRNA1",
        "LSAMP",
        "MYO6",
        "IRX2",
        "MYO15A",
        "CCER2",
        "POU4F3",
        "PCP4",
        "PKIB",
        "ATOH1",
        "TJAP1",
        "GRXCR1",
        "RBM24",
        "TMPRSS3",
        "USH2A",
        "PAX2",
        "STRC",
        "OTOF",
        "GRXCR2",
        "TRIM36",
        "RSPH1",
        "CD164L2",
        "CRIP3",
        "FAM183A",
        "C1orf194",
        "C1orf232",
        "MINDY4B",
        "CCDC81",
        "C2orf40",
        "SMPX"
  )
)

##                                                                           ##
###############################################################################

```
  
  
  
```{r, include=FALSE}
knitr::opts_chunk$set(
  tidy = TRUE,
  tidy.opts = list(width.cutoff = 120),
  message = FALSE,
  warning = FALSE
)
```



```{r, eval=data.analysis.mode, echo=T, results=F}
## This part will only be run for the data analysis mode

## Tutorial from the Trapnell lab
# https://github.com/cole-trapnell-lab/monocle-release/issues/388


library(Seurat)
library(monocle3)
library(htmlwidgets)

## An old version of the matrix package is required
#install.packages("https://cran.r-project.org/src/contrib/Archive/Matrix/Matrix_1.3-3.tar.gz")

###############################################################################
## Subset main seurat object
seurat <- OsC

## subset dataset ##
seurat@meta.data[["Branch"]] <- "Rest"
seurat@meta.data[seurat@meta.data[,branchSelectionCol] %in% branchSelection, "Branch"] <- "Branch"

seurat <- subset(x = seurat, subset = Branch == "Branch")

seurat@meta.data[["Branch"]] <- "Rest"
seurat@meta.data[seurat@meta.data[,mainPTcol] > 0, "Branch"] <- "Branch"

seurat <- subset(x = seurat, subset = Branch == "Branch")
##
###############################################################################


## remove cluster 5 ##
gene_annotation <- as.data.frame(rownames(seurat@reductions[["pca"]]@feature.loadings), row.names = rownames(seurat@reductions[["pca"]]@feature.loadings))
colnames(gene_annotation) <- "gene_short_name"

# part two, cell information

cell_metadata <- as.data.frame(seurat@assays[["RNA"]]@counts@Dimnames[[2]], row.names = seurat@assays[["RNA"]]@counts@Dimnames[[2]])
colnames(cell_metadata) <- "barcode"

# part three, counts sparse matrix

New_matrix <- seurat@assays[["RNA"]]@counts
New_matrix <- New_matrix[rownames(seurat@reductions[["pca"]]@feature.loadings), ]
expression_matrix <- New_matrix


### Construct the basic cds object

cds_from_seurat <- new_cell_data_set(
    expression_matrix,
    cell_metadata = cell_metadata,
    gene_metadata = gene_annotation
)


### Construct and assign the made up partition 
###### I DO NOT ADVISE THIS

recreate.partition <- c(rep(1, length(cds_from_seurat@colData@rownames)))
names(recreate.partition) <- cds_from_seurat@colData@rownames
recreate.partition <- as.factor(recreate.partition)

cds_from_seurat@clusters@listData[["UMAP"]][["partitions"]] <- recreate.partition


### Assign the cluster info

list_cluster <- seurat@meta.data[[sprintf("seurat_clusters")]]
#list_cluster <- seurat@meta.data[[sprintf("ClusterNames_%s_%sPC", 0.5, 20)]]
names(list_cluster) <- seurat@assays[["RNA"]]@data@Dimnames[[2]]

cds_from_seurat@clusters@listData[["UMAP"]][["clusters"]] <- list_cluster


### Could be a space-holder, but essentially fills out louvain parameters

cds_from_seurat@clusters@listData[["UMAP"]][["louvain_res"]] <- "NA"


### Assign UMAP coordinate

## old commented out
# cds_from_seurat@reducedDims@listData[["UMAP"]] <- seurat@reductions[["umap"]]@cell.embeddings

# replaced with from https://github.com/satijalab/seurat/issues/1658
cds_from_seurat@int_colData@listData$reducedDims@listData[["UMAP"]] <- seurat@reductions[["umap"]]@cell.embeddings 

### Assign feature loading for downstream module analysis

cds_from_seurat@preprocess_aux$gene_loadings <- seurat@reductions[["pca"]]@feature.loadings


### Learn graph, this step usually takes a significant period of time for larger samples

print("Learning graph, which can take a while depends on the sample")
# cds_from_seurat <- cluster_cells(cds = cds_from_seurat, reduction_method = "UMAP")
cds_from_seurat <- learn_graph(cds_from_seurat, use_partition = T)

#plot_cells(cds_from_seurat)

####Here I chose to save the gene_metadata, rds, etc.`


###############################################################################
## Calculate pseudotime                                                      ##

# get_earliest_principal_node <- function(cds, time_bin="PF"){
#   cell_ids <- which(colData(cds)[, "time"] == time_bin)
#   cell_ids <- colData(cds)$barcode
#   closest_vertex <-
#   cds@principal_graph_aux[["UMAP"]]$pr_graph_cell_proj_closest_vertex
#   closest_vertex <- as.matrix(closest_vertex[colnames(cds), ])
#   root_pr_nodes <-
#   igraph::V(principal_graph(cds)[["UMAP"]])$name[as.numeric(names
#   (which.max(table(closest_vertex[cell_ids,]))))]
#   root_pr_nodes
# }




## Set root cells - here polykeratin cluster ##
root_cells <- as.vector(
    seurat@meta.data[seurat@meta.data[,startClusterColName] == startClusterID,"cellID"]
)

closest_vertex <- cds_from_seurat@principal_graph_aux[["UMAP"]]$pr_graph_cell_proj_closest_vertex

root_pr_nodes <-
  igraph::V(principal_graph(cds_from_seurat)[["UMAP"]])$name[as.numeric(names
  (which.max(table(closest_vertex[root_cells,]))))]

cds_from_seurat <- order_cells(
    cds_from_seurat,
    root_pr_nodes=root_pr_nodes
)

###############################################################################
## Monocle DGE                                                               ##
## Reference https://cole-trapnell-lab.github.io/monocle3/docs/differential/
# time_models <- monocle3::fit_models(
#     cds_from_seurat,
#     model_formula_str = "~pseudotime",
#     expression_family="negbinomial"
# )
# 
# gene_fits <- monocle3::fit_models(cds_from_seurat, model_formula_str = "~embryo.time + batch")
# fit_coefs <- coefficient_table(gene_fits)
# fit_coefs %>% filter(term != "(Intercept)") %>%
#       select(gene_short_name, term, q_value, estimate)

## Correlation tests ##
# pr_graph_test_res <- monocle3::graph_test(cds_from_seurat, neighbor_graph="knn", cores=8)
# pr_deg_ids <- row.names(subset(pr_graph_test_res, q_value < 0.05))
# 
# ## Find gene modules ##
# gene_module_df <- monocle3::find_gene_modules(cds_from_seurat[pr_deg_ids,], resolution=1e-2)
# 
# cell_group_df <- tibble::tibble(cell=row.names(colData(cds_from_seurat)), 
#                                 cell_group=partitions(cds_from_seurat)[colnames(cds_from_seurat)])
# agg_mat <- aggregate_gene_expression(cds_from_seurat, gene_module_df, cell_group_df)
# row.names(agg_mat) <- stringr::str_c("Module ", row.names(agg_mat))
# colnames(agg_mat) <- stringr::str_c("Partition ", colnames(agg_mat))
# 
# pheatmap::pheatmap(agg_mat, cluster_rows=TRUE, cluster_cols=TRUE,
#                    scale="column", clustering_method="ward.D2",
#                    fontsize=6)
# 
# 
# ## Finding genes that change as a function of pseudotime ##
# ## Requires old version of matrix (< 1.3)
# cds_pr_test_res <- graph_test(cds_from_seurat, neighbor_graph="principal_graph", cores=4)
# pr_deg_ids <- row.names(subset(cds_pr_test_res, q_value < 0.05))
# 
# ## plot genes in pseudotime ##
# p1 <- plot_genes_in_pseudotime(cds_from_seurat,
#                          color_cells_by="clusterName",
#                          min_expr=0.5)
# 
# AFD_genes <- c("ATF3", "KRT19")
# AFD_lineage_cds <- cds_from_seurat[rowData(cds_from_seurat)$gene_short_name %in% AFD_genes,
#                        colData(cds_from_seurat)$cell.type %in% c("AFD")]
# 
# plot_genes_in_pseudotime(AFD_lineage_cds,
#                          color_cells_by="pseudotime",
#                          min_expr=0.5)

## Save single cell object ##
FN <- paste0(
    Obio@parameterList$localWorkDir,
    Obio@parameterList$project_id,
    ".", branchName,
    ".monocle.SCE.rds"
)

saveRDS(cds_from_seurat, FN)
```

```{r , echo=TRUE, eval=TRUE, warning=FALSE, results=F}
###############################################################################
## Visualization                                                             ##
## Load Rds
FN <- paste0(
    Obio@parameterList$localWorkDir,
    Obio@parameterList$project_id,
    ".", branchName,
    ".monocle.SCE.rds"
)

cds_from_seurat <- readRDS(FN)

plotList <- list()
chnkVec <- as.vector(NULL, mode = "character")



## Export Pseudotime to Seurat object ##
# Branch 1
# Clusters Polykeratins (5) > mTecDiff (12) > NEDC_I_NEUROD1 (1) > NEDC_II_NEUROD1 (4) > NEDC_III_SOX2 (2) > NEDC_IV_SOX2 (11)
# branch1 <- c(5, 12, 1, 4, 2, 11)
# Branch 2
# Clusters Polykeratins (5) > cTecDiff (9) > cTECI (0) > cTECIII (6) > cTECII (3)
# branch2 <- c(5, 9, 0, 6,3)
# 
# Branch 3
# Clusters Polykeratins (5) > mTecDiff (12) > mTec MYO (8)
# branch3 <- c(5, 12, 8)

traj.coord<- cds_from_seurat@principal_graph_aux@listData[["UMAP"]][["pseudotime"]]
dfPseudo <- data.frame(cellID = names(traj.coord), Pseudotime_MC = traj.coord)

dfPseudo$cellID <- NULL

names(dfPseudo) <- gsub("Pseudotime_MC", paste0("Pseudotime_MC_", branchName), names(dfPseudo) )

## Add to Seurat object ##
OsC <- biologicToolsSC::addDf2seuratMetaData(
    OsC, 
    dfPseudo
)

OsC@meta.data[is.na(OsC@meta.data)] <- 0

# dfPseudoT2 <- OsC@meta.data[,c("cellID", "seurat_clusters", "Pseudotime_MC")]
# dfPseudoT2[["Pseudotime_MC_Lineage_1"]] <- 0
# dfPseudoT2[dfPseudoT2$seurat_clusters %in% branch1, "Pseudotime_MC_Lineage_1"] <- dfPseudoT2[dfPseudoT2$seurat_clusters %in% branch1, "Pseudotime_MC"]
# 
# 
# dfPseudoT2[["Pseudotime_MC_Lineage_2"]] <- 0
# dfPseudoT2[dfPseudoT2$seurat_clusters %in% branch2, "Pseudotime_MC_Lineage_2"] <- dfPseudoT2[dfPseudoT2$seurat_clusters %in% branch2, "Pseudotime_MC"]
# 
# 
# dfPseudoT2[["Pseudotime_MC_Lineage_3"]] <- 0
# dfPseudoT2[dfPseudoT2$seurat_clusters %in% branch3, "Pseudotime_MC_Lineage_3"] <- dfPseudoT2[dfPseudoT2$seurat_clusters %in% branch3, "Pseudotime_MC"]
# 
# dfPseudoT2$cellID <- NULL 
# dfPseudoT2$seurat_clusters <- NULL 
# dfPseudoT2$Pseudotime_MC <- NULL

# OsC <- biologicToolsSC::addDf2seuratMetaData(
#     OsC, 
#     dfPseudoT2
# )

OsC@meta.data[is.na(OsC@meta.data)] <- 0

save(OsC,
    file = paste0(
         Obio@parameterList$localWorkDir,
         Obio@parameterList$project_id,
        ".Seurat.Robj"
     )
)

## Create three pseudotime branches ##


## Done                                                                      ##
###############################################################################


tag <- paste0("Monocle_Pseudotime", "_", branchName)

plotList[[tag]] <- plot_cells(cds_from_seurat,
    color_cells_by = "pseudotime",
    label_cell_groups=FALSE,
    label_leaves=FALSE,
    label_branch_points=FALSE,
    graph_label_size=1.5
) + ggplot2::theme_bw(
) +  ggplot2::theme(
      axis.text.y   = ggplot2::element_text(size=8),
      axis.text.x   = ggplot2::element_text(size=8),
      axis.title.y  = ggplot2::element_text(size=8),
      axis.title.x  = ggplot2::element_text(size=8),
      axis.line = ggplot2::element_line(colour = "black"),
      panel.border = ggplot2::element_rect(colour = "black", fill=NA, size=1),
      plot.title = ggplot2::element_text(hjust = 0.5, size = 12),
      legend.title = ggplot2::element_blank()
) + ggplot2::guides(col = ggplot2::guide_legend(override.aes = list(shape = 16, size = legendDotSize))
) + ggplot2::ggtitle(paste0("Sample: ", gsub("_", " ", tag))
)

FNbase <- paste0(tag, VersionPdfExt)
FN <- paste0(Obio@parameterList$reportFigDir, FNbase)
FNrel <- paste0("report_figures/", FNbase)

pdf(FN)
    print(plotList[[tag]])
dev.off()
            
if (exists("shinyURL") & !is.null(shinyURL)){
    link <- paste0(
      'An interactive version of this figure with additional viewing options can be found <a href="',shinyURL,'?_inputs_&y_axis=%22UMAP_2%22&x_axis=%22UMAP_1%22&colorBy=%22Pseudotime_MC%22&splitByColumn=%22all%22" target="_blank">here</a>. '
    )
} else {
    link <- ""
}
    
figLegend <- paste0(
    '**Figure ', 
    figureCount, 
    ':** ',
    ' Monocle pseudotime projection on UMAP. Download a pdf of this figure <a href="',FNrel,'" target="_blank">here</a>. ',
     link
)

figureCount <- figureCount + 1

NewChnk <- paste0(
    "#### ", tag,
    "\n```{r, results='asis', echo=F, eval=TRUE, warning=FALSE, fig.cap='",
    figLegend,"'}\n",
    "\n",
    "\n print(plotList[['",tag,"']])",
    "\n cat(  '\n')",
    "\n\n\n```\n"   
)

chnkVec <- c(
    chnkVec,
    NewChnk
)


## Done overview plot                                                        ##
###############################################################################

if (length(plotList) > 2){
    tabVar <- paste0("### Monocle Pseudotime Subtrajectory ",branchName," {.tabset .tabset-fade .tabset-dropdown}")
} else {
    tabVar <- paste0("### Monocle Pseudotime Subtrajectory ",branchName," {.tabset .tabset-fade .tabset-pills}")
}



```

`r tabVar`

```{r , echo=TRUE, eval=TRUE, warning=FALSE, results="asis"} 

cat(paste(knitr::knit(text = chnkVec, quiet = T), collapse = '\n'))

```


```{r, echo=TRUE, eval=TRUE, warning=FALSE, results=F}

###############################################################################
## Find most variable genes in trajectory                                    ##

pseudotimeLineageName <-  mainPTcol
# plotTopNgenes <- 100

###############################################################################
## Subset main seurat object
seurat <- OsC

## subset dataset ##
seurat@meta.data[["Branch"]] <- "Rest"
seurat@meta.data[seurat@meta.data[,branchSelectionCol] %in% branchSelection, "Branch"] <- "Branch"

seurat <- subset(x = seurat, subset = Branch == "Branch")

seurat@meta.data[["Branch"]] <- "Rest"
seurat@meta.data[seurat@meta.data[,mainPTcol] > 0, "Branch"] <- "Branch"

seurat <- subset(x = seurat, subset = Branch == "Branch")
##
###############################################################################

Y <- data.matrix( seurat@assays[["RNA"]]@data)

## Focus on most variable genes in the study

if ( length(Obio@sampleDetailList) > 1 ){
    Y <-  Y[seurat@assays$integrated@var.features,]
} else {
    Y <-  Y[seurat@assays$RNA@var.features,]
}
Y <- Y[rowSums(Y) > 0,]
        
t <- seurat@meta.data[,pseudotimeLineageName]
        
# Fit GAM for each gene using pseudotime as independent variable.
        
gam.pval <- apply(Y, 1, function(z){
    d <- data.frame(z=z, t=t)
    tmp <- gam::gam(z ~ gam::lo(t), data=d)
    p <- summary(tmp)[4][[1]][1,5]
    p
})


gam.pval <- sort(gam.pval, decreasing = FALSE)
gam.pval <- gam.pval[gam.pval < 0.01]
gam.pval <- sort(gam.pval, decreasing=FALSE)


display.gam.pval <- -1*log10(gam.pval)
maxVal <- max(display.gam.pval[display.gam.pval < Inf])
display.gam.pval[display.gam.pval == Inf] <- maxVal

topgenes <- names(gam.pval)[1:plotTopNgenes]

heatmapGeneList <- list(
    "Top_Pseudotime_Variable_Genes" = topgenes
)


###################
## Make Table

dfOut <- data.frame(gene=names(gam.pval), time_variability_gam_lg10_p_value=round(display.gam.pval,3))
dfOut[["Most_time_variable_genes"]] <- ""
dfOut[dfOut$gene %in% topgenes, "Most_time_variable_genes"] <- "+"

## Done
####################

pos <- grep("TFs", names(Obio@dataTableList$referenceList))

if (length(pos > 0)){
    topgenes.TF <- names(sort(gam.pval, decreasing = FALSE))[names(sort(gam.pval, decreasing = FALSE)) %in% Obio@dataTableList[["referenceList"]]$TFs]
    topgenes.TF <- topgenes.TF[1:plotTopNgenes]
    heatmapGeneList[["Top_Pseudotime_Variable_Transcription_Factors"]] <- topgenes.TF
    dfOut[["Most_time_variable_TFs"]] <- ""
    dfOut[dfOut$gene %in% topgenes.TF, "Most_time_variable_TFs"] <- "+"

} else {
    topgenes.TF <- 0
}

###############################################################################
## Add chromatin remodelling                                                 ##

addList <- c(
    "Chromatin_Silencing", 
    "Chromatin_Remodeling", 
    "Chromatin_Organisation"
)

for (i in 1:length(addList)){
    pos <- grep(addList[i], names(Obio@dataTableList$referenceList))

    if (length(pos > 0)){
        topgenes <- names(sort(gam.pval, decreasing = FALSE))[names(sort(gam.pval, decreasing = FALSE)) %in% Obio@dataTableList[["referenceList"]][[addList[i]]]]
        
        if (length(topgenes) > plotTopNgenes){
            topgenes <- topgenes[1:plotTopNgenes]    
        }
        
        
        heatmapGeneList[[paste0("Top_Pseudotime_Variable_", addList[i])]] <- topgenes
      
    }
}


##
###############################################################################


###############################################################################
## Add additional gene sets to heatmapset                                    ##

if (exists("heatmapGeneListAdditions") & (length(heatmapGeneListAdditions) > 0)){
    heatmapGeneList <- do.call(c, list(heatmapGeneList, heatmapGeneListAdditions))
}

##                                                                           ##
###############################################################################


#########################################
## Add average expression column

###############################################################################
## Add percentage expressed genes                                            ##
DefaultAssay(OsC) <- "RNA"
my_genes <- rownames(x = seurat@assays$RNA)

exp <- FetchData(seurat, my_genes)

ExprMatrix <- round(as.matrix(colMeans(exp  > 0)) *100,1)
colnames(ExprMatrix)[1] <- "Percent_cells_expressing"
dfExprMatrix <- data.frame(ExprMatrix)
dfExprMatrix[["gene"]] <- row.names(dfExprMatrix)

dfExprMatrix <- dfExprMatrix[dfExprMatrix$gene %in% dfOut$gene, ]

dfOut <- dplyr::full_join(
    dfOut,
    dfExprMatrix,
    by="gene"
)


##
#########################################

###############################################################################
## Detect peak genes among most variable genes                               ##

## Get data
dfData <- seurat@assays[["RNA"]]@data[names(gam.pval),]

dfData <- dfData[unique(na.omit(c(topgenes, topgenes.TF))), ]

dfPT <- seurat@meta.data[,c("cellID", "Pseudotime_MC")]

first <- TRUE
maxPeakPosition <- as.vector(NULL, mode="numeric")
peakType <- as.vector(NULL, mode="character")
gene <- as.vector(NULL, mode="character")
peakMax <- as.vector(NULL, mode="numeric")

for (i in 1:nrow(dfData)){
    dfTempData <- data.frame(cellID=colnames(dfData), assign(row.names(dfData)[i], as.vector(dfData[i,])))
    names(dfTempData)[2] <- "gene"
    
    dfTempData <- merge(
        dfPT, 
        dfTempData, 
        by.x = "cellID",
        by.y = "cellID"
    )
    smoothing <- 0.1
    loessMod <- loess(gene ~ Pseudotime_MC, data=dfTempData, span=smoothing)
    
    xl <- seq(min(dfTempData$Pseudotime_MC),max(dfTempData$Pseudotime_MC), (max(dfTempData$Pseudotime_MC) - min(dfTempData$Pseudotime_MC))/99)
    yl <- predict(loessMod,xl)
        
    yl[is.na(yl)] <- 0
      
    ## Annotate peak position ##
    if (sum(yl) > 0){
        peakPos <- find_peaks(yl, m=length(yl)/2)  
        
        if (length(peakPos) > 0){
            pos <- grep( max(yl[peakPos]), yl[peakPos])
            peakPos <- peakPos[pos]   
        }
        
        peakMax[i] <- max(yl)
        
        gene[i] <- row.names(dfData)[i]
        
        if (length(peakPos) > 0){
            maxPeakPosition[i] <- peakPos  
            
            if (peakPos <= 15){
            peakType[i] <- "proximal"
        } else if (peakPos >15 & peakPos < 85) {
            peakType[i] <- "middle"
        } else if (peakPos >= 85){
            peakType[i] <- "distal"
        } else {
            "none"
        }
            
        } else {
            maxPeakPosition[i] <- NA
            peakType[i] <- ""
            peakMax[i] <- 0
        }
        
        
        
    }
    
    
        #row_mean <- mean(yl)
        #row_hm <- log2(yl/row_mean)
        #row_hm[row_hm > setMax] = setMax
        #row_hm[row_hm < setMin] = setMin
        
    new.row <- data.frame(t(yl))
    row.names(new.row) <- row.names(dfData)[i]
        
        
    if (first){
        dfRes <- new.row
        first <- FALSE
    } else {
        dfRes <- rbind(
            dfRes, 
            new.row
        )
    }
    
    if (i%%20 == 0){
      print(i)
    }
}

# bs = cr, denoting cubic regression splines
###############################################################################
## Classify peaks                                                            ##

## Classify as peak everything peaking between bin 15 and 85
dfPeak <- data.frame(
    gene, 
    peakType,
    maxPeakPosition,
    peakMax
)

dfPeak <- dfPeak[order(dfPeak$maxPeakPosition, decreasing = F),]

dfOut <- merge(
    dfOut, 
    dfPeak, 
    by.x = "gene",
    by.y = "gene",
    all=TRUE
)

dfOutDisplay <- dfOut[dfOut$Percent_cells_expressing >= 10, ]
## Done                                                                      ##
###############################################################################

##                                                                           ##
###############################################################################

#########################################
## Write to Excel 
if (!dir.exists(Obio@parameterList[["reportTableDir"]])){
  dir.create(Obio@parameterList[["reportTableDir"]])
}

baseFN <- paste0(
   Obio@parameterList$project_id, 
   ".monocle.variability.table.xlsx"
)


outPutFN <- paste0(
     Obio@parameterList$reportTableDir,
     baseFN
)
  
 
FNrel <- paste0("report_tables/", baseFN)

wb <- openxlsx::createWorkbook()

hs1 <- openxlsx::createStyle(
    fontColour = "#ffffff",
    fgFill = "#000000",
    halign = "CENTER",
    textDecoration = "Bold"
)
sheetName <- substr("Lineage_1",1,30)
  
openxlsx::addWorksheet(
    wb, 
    sheetName = sheetName
)
  
openxlsx::freezePane(wb, sheetName ,  firstActiveRow = 2)
sheetN=1
openxlsx::writeData(wb, sheetN, dfOut, startRow = 1, startCol = 1, headerStyle = hs1)
openxlsx::saveWorkbook(
  wb, 
  outPutFN , 
  overwrite = TRUE
)

## Create table download option ##
#FNbase <- paste0(Obio@parameterList$project_id, "_Pseudotime_Variable_Genes.xlsx")
#FN <- paste0(Obio@parameterList$reportTableDir, FNbase)
#FNrel <- paste0("report_tables/", FNbase)
tabDownloadLink <- paste0("This table list all potentially time-variable genes in this trajectory [here](",FNrel,")")
tabLegend = paste0(
    "**Table: ** Time-variable genes in this trajectory. ",
    tabDownloadLink
)
chnkVec <- paste0(
        #"#### ", names(dtList),
        "\n```{r, results='asis', echo=F, eval=TRUE, warning=FALSE, fig.cap='",
        tabLegend,"'}\n",
        "\n",
        "\n DT::datatable(dfOutDisplay,rownames = FALSE,  escape = FALSE)",
        "\n cat(  '\n')",
        "\n\n\n```\n"   
    )
tabVar <- "### Table Time-variable Genes"



##
###############################################################################
```

`r tabVar`
```{r, echo=TRUE, eval=TRUE, warning=FALSE, results="asis"}
    cat(paste(knitr::knit(text = chnkVec, quiet = T), collapse = '\n'))
```

```{r, echo=TRUE, eval=TRUE, warning=FALSE, results=F}
###############################################################################
## Create Heatmap N most variable genes                                      ##

plotList <- list()
chnkVec <- as.vector(NULL, mode = "character")

for (i in 1:length(heatmapGeneList)){
    ## Relative Heatmap
    tag <- paste0(names(heatmapGeneList)[i], "_relative")
    plotList[[tag]] <- createLineageHeatmap(
    seurat,  
    lineageSelection = NULL,
    pseudotimeLineageName = "Pseudotime_MC",
    heatmapGeneVec = heatmapGeneList[[i]],
    clusterRows = TRUE
    )
 
    ## Save to file ##
    FNbase <- paste0(tag, VersionPdfExt)
    FN <- paste0(Obio@parameterList$reportFigDir, FNbase)
    FNrel <- paste0("report_figures/", FNbase)
    
    
    pdf(FN)
        print(plotList[[tag]])
    dev.off()
    
    
    
    ## Create R markdown chunk ##
    figLegend <- paste0(
        '**Figure ', 
        figureCount, 
        '**: Heatmap (relative values) ',tag,
        '. Download a pdf of this figure <a href="',FNrel,'" target="_blank">here</a>. '
    )
    figureCount <- figureCount + 1 
    
    NewChnk <- paste0(
        "\n#### ", tag, 
        "\n```{r, results='asis', echo=F, eval=TRUE, warning=FALSE, fig.cap='",
        figLegend,"'}\n",
        "\n",
        "\n print(plotList[['",tag,"']])",
        "\n cat(  '\n')",
        "\n\n\n```\n"   
    )
    
    chnkVec <- c(
        chnkVec,
        NewChnk
    )
    
    ## Absolute Heatmap
    tag <- paste0(names(heatmapGeneList)[i], "_absolute")
    plotList[[tag]] <- createLineageHeatmap(
        seurat,  
        lineageSelection = NULL,
        pseudotimeLineageName = "Pseudotime_MC",
        heatmapGeneVec = heatmapGeneList[[i]],
        clusterRows = TRUE,
        #plotTopNgenes = 100,
        plotAbsoluteValues = TRUE,  # otherwise: relative
        highColor = "#00008B",
        #midColor = "#fffbbc",
        lowColor = "#d3d3d3"
    )
 
    ## Save to file ##
    FNbase <- paste0(tag, VersionPdfExt)
    FN <- paste0(Obio@parameterList$reportFigDir, FNbase)
    FNrel <- paste0("report_figures/", FNbase)
    
    
    pdf(FN)
        print(plotList[[tag]])
    dev.off()
    
    
    
    ## Create R markdown chunk ##
    figLegend <- paste0(
        '**Figure ', 
        figureCount, 
        '**: Heatmap ',tag,
        '. Download a pdf of this figure <a href="',FNrel,'" target="_blank">here</a>. '
    )
    figureCount <- figureCount + 1 
    
    NewChnk <- paste0(
        "\n#### ", tag, 
        "\n```{r, results='asis', echo=F, eval=TRUE, warning=FALSE, fig.cap='",
        figLegend,"'}\n",
        "\n",
        "\n print(plotList[['",tag,"']])",
        "\n cat(  '\n')",
        "\n\n\n```\n"   
    )
    
    chnkVec <- c(
        chnkVec,
        NewChnk
    )
    
    
    ## Done                                                                      ##
    ###############################################################################
}

###############################################################################
## Add ordered gene lists                                                    ##
if (exists("heatmapGeneListAdditionsOrdered") & (length(heatmapGeneListAdditionsOrdered) > 0)){
    for (i in 1:length(heatmapGeneListAdditionsOrdered)){
        ## Relative Heatmap
        tag <- paste0(names(heatmapGeneListAdditionsOrdered)[i], "_relative")
        plotList[[tag]] <- createLineageHeatmap(
        seurat,  
        lineageSelection = NULL,
        pseudotimeLineageName = "Pseudotime_MC",
        heatmapGeneVec = heatmapGeneListAdditionsOrdered[[i]],
        clusterRows = FALSE
        )
     
        ## Save to file ##
        FNbase <- paste0(tag, VersionPdfExt)
        FN <- paste0(Obio@parameterList$reportFigDir, FNbase)
        FNrel <- paste0("report_figures/", FNbase)
        
        
        pdf(FN)
            print(plotList[[tag]])
        dev.off()
        
        
        
        ## Create R markdown chunk ##
        figLegend <- paste0(
            '**Figure ', 
            figureCount, 
            '**: Heatmap (relative values) ',tag,
            '. Download a pdf of this figure <a href="',FNrel,'" target="_blank">here</a>. '
        )
        figureCount <- figureCount + 1 
        
        NewChnk <- paste0(
            "\n#### ", tag, 
            "\n```{r, results='asis', echo=F, eval=TRUE, warning=FALSE, fig.cap='",
            figLegend,"'}\n",
            "\n",
            "\n print(plotList[['",tag,"']])",
            "\n cat(  '\n')",
            "\n\n\n```\n"   
        )
        
        chnkVec <- c(
            chnkVec,
            NewChnk
        )
        
        ## Absolute Heatmap
        tag <- paste0(names(heatmapGeneListAdditionsOrdered)[i], "_absolute")
        plotList[[tag]] <- createLineageHeatmap(
            seurat,  
            lineageSelection = NULL,
            pseudotimeLineageName = "Pseudotime_MC",
            heatmapGeneVec = heatmapGeneListAdditionsOrdered[[i]],
            clusterRows = FALSE,
            #plotTopNgenes = 100,
            plotAbsoluteValues = TRUE,  # otherwise: relative
            highColor = "#00008B",
            #midColor = "#fffbbc",
            lowColor = "#d3d3d3"
        )
     
        ## Save to file ##
        FNbase <- paste0(tag, VersionPdfExt)
        FN <- paste0(Obio@parameterList$reportFigDir, FNbase)
        FNrel <- paste0("report_figures/", FNbase)
        
        
        pdf(FN)
            print(plotList[[tag]])
        dev.off()
        
        
        
        ## Create R markdown chunk ##
        figLegend <- paste0(
            '**Figure ', 
            figureCount, 
            '**: Heatmap ',tag,
            '. Download a pdf of this figure <a href="',FNrel,'" target="_blank">here</a>. '
        )
        figureCount <- figureCount + 1 
        
        NewChnk <- paste0(
            "\n#### ", tag, 
            "\n```{r, results='asis', echo=F, eval=TRUE, warning=FALSE, fig.cap='",
            figLegend,"'}\n",
            "\n",
            "\n print(plotList[['",tag,"']])",
            "\n cat(  '\n')",
            "\n\n\n```\n"   
        )
        
        chnkVec <- c(
            chnkVec,
            NewChnk
        )
        
        
        ## Done                                                                      ##
        ###############################################################################
    } 
}
##                                                                           ##
###############################################################################


## Done                                                                      ##
###############################################################################
if (length(plotList) > 3){
    tabVar <- ".tabset .tabset-fade .tabset-dropdown"
} else {
    tabVar <- ".tabset .tabset-fade .tabset-pills"
}

```

### Monocle Heatmaps {`r tabVar`}
```{r, echo=TRUE, eval=TRUE, warning=FALSE, results="asis"} 

cat(paste(knitr::knit(text = chnkVec, quiet = T), collapse = '\n'))

```

```{r, echo=TRUE, eval=TRUE, warning=FALSE, results=F}



###############################################################################
if (length(plotList) > 3){
    tabVar <- ".tabset .tabset-fade .tabset-dropdown"
} else {
    tabVar <- ".tabset .tabset-fade .tabset-pills"
}

```
