<!-- Set PArameters Module -->
<!-- Set the chnkPrefix to make all chunks unique in the overall folder -->
```{r partB_pca_plots, echo=TRUE, eval=TRUE, warning=FALSE}
chnkPrefix <- "partB.pca.plots."
VersionPdfExt <- VersionPdfExt <- paste0(".",chnkPrefix,"V", gsub("-", "", Sys.Date()), ".pdf")

```



```{r partB_create_PCA_plots, echo=TRUE, eval=TRUE, warning=FALSE, results=F}
###############################################################################
## Perform integrated analysis                                               ##

if (length(Obio@sampleDetailList) > 1){
    DefaultAssay(OsC) <- "integrated"
} else {
    Obio@parameterList$singleCellClusterString <- gsub("integrated", "RNA", Obio@parameterList$singleCellClusterString)
    DefaultAssay(OsC) <- "RNA"
}


# Run the standard workflow for visualization and clustering
## This will scale on the most variable features only
OsC <- ScaleData(OsC, verbose = FALSE)

OsC <- RunPCA(
    OsC, 
    npcs = Obio@parameterList$singleCellSeuratNpcs4PCA, verbose = FALSE
)
# t-SNE and Clustering

## Add PCA clusters to data collection ##


OsC <- RunUMAP(OsC, reduction = "pca", dims = 1:Obio@parameterList$singleCellSeuratNpcs4PCA)

OsC <- RunTSNE(OsC, reduction = "pca", dims = 1:Obio@parameterList$singleCellSeuratNpcs4PCA)

OsC <- FindNeighbors(OsC, reduction = "pca", dims = 1:Obio@parameterList$singleCellSeuratNpcs4PCA)

OsC <- FindClusters(OsC, resolution = Obio@parameterList$singleCellClusterParameter)

## Rational: Run PCA on variable features, then scale data for heatmaps and other applications

if (length(Obio@sampleDetailList) > 1){
    DefaultAssay(OsC) <- Obio@parameterList$scIntegrationMethod
    allGenes <- rownames(x = OsC@assays[[Obio@parameterList$scIntegrationMethod]])
    OsC <- ScaleData(OsC, verbose = FALSE, features=allGenes)
} 

DefaultAssay(OsC) <- "RNA"
allGenes <- rownames(x = OsC@assays$RNA)
OsC <- ScaleData(OsC, verbose = FALSE, features=allGenes)

## Save minimal Seurat object ##
# save(OsC,
#     file = paste0(
#          Obio@parameterList$localWorkDir,
#          Obio@parameterList$project_id,
#         ".Seurat.Robj"
#      )
# )


###############################################################################
## Add custom cluster annotation if specified                                ##
FNcol <- paste0(cwd, "/design/customClusterAnnotation.txt")
tableValid <- FALSE

if (file.exists(FNcol)){
    dfClusterAnnotation <- read.delim(
        FNcol, 
        header = T, 
        sep = "\t",
        stringsAsFactors = F
    )
    
    ## Check column names ##
    pos1 <- grep("seurat_clusters", names(dfClusterAnnotation))
    pos2 <- grep("clusterName", names(dfClusterAnnotation))
    pos3 <- grep("clusterColor", names(dfClusterAnnotation))
    
    ## Check if clusters match ##
    inClust <- unique(as.character(dfClusterAnnotation$seurat_clusters))
    oClust <- unique(as.character(OsC@meta.data$seurat_clusters))
    
    
    if (length(pos1) != 0 & length(pos2) != 0 & length(pos3) != 0 ){
        ## Remove spaces ##
        dfClusterAnnotation$clusterName <- gsub(" ", "_", dfClusterAnnotation$clusterName)
        dfClusterAnnotation$clusterName <- gsub("\\.", "_", dfClusterAnnotation$clusterName)
        dfClusterAnnotation$clusterName <- gsub("-", "_", dfClusterAnnotation$clusterName)
        dfClusterAnnotation$clusterName <- gsub("__", "_", dfClusterAnnotation$clusterName)
        dfClusterAnnotation$clusterName <- gsub("_$", "", dfClusterAnnotation$clusterName)
        ## Check if clusters match ##
        inClust <- unique(as.character(dfClusterAnnotation$seurat_clusters))
        oClust <- unique(as.character(OsC@meta.data$seurat_clusters))
        if (length(inClust) == length(intersect(inClust, oClust))){
            tableValid <- TRUE
        } else {
            tableValid <- FALSE
        }
          
    } else {
        tableValid <- FALSE
    }
}

if (!file.exists(FNcol) | !tableValid){
    dfClusterAnnotation <- OsC@meta.data[,c("cellID", "seurat_clusters")]
    
    levels <- as.vector(sort(unique(dfClusterAnnotation$seurat_clusters)))
    clusterOrder <- as.numeric(sort(unique(dfClusterAnnotation$seurat_clusters)))
    
    library(scales)
    clusterCols <- hue_pal()(length(levels))
    
    dfClusterAnnotation <- data.frame(
        seurat_clusters = levels,
        clusterName = paste0("C", levels),
        clusterColor = clusterCols,
        clusterOrder = clusterOrder,
        stringsAsFactors = F
    )
    
    #row.names(dfClusterAnnotation) <- dfClusterAnnotation$cellID
    #dfClusterAnnotation$cellID <- NULL
    ## Add sample colors ##
    
    annoDir <- paste0(cwd, "/design")
    
    if (!dir.exists(annoDir)){
        dir.create(annoDir)
    }
    
    

    
    FNcol <- paste0(annoDir, "/clusterAnnotation.txt")
    write.table(
        dfClusterAnnotation,
        FNcol,
        row.names=F,
        sep = "\t"
    ) 
}

## Make sure dfClusterAnnotation has a clusterOrder column
pos <- grep("^clusterOrder$", names(dfClusterAnnotation))

if (length(pos) ==1){
    dfClusterAnnotation <- dfClusterAnnotation[order(dfClusterAnnotation$clusterOrder, decreasing = F),]
    orderVec <- dfClusterAnnotation$clusterName
    Obio@parameterList[["clusterNameOrder"]] <- orderVec
} else {
      ###############################################################################
      ## Order average expression by cluster similarity (most variable genes)      ##
      assay <- NULL
      assay <- assay %||% DefaultAssay(object = OsC)
      
      
      features <- VariableFeatures(object = OsC)
      features <- intersect(x = features, y = rownames(x = OsC))
      data.avg <- AverageExpression(object = OsC, assays = assay, 
      features = features, slot = "data", verbose = T)[[1]]
      
      
      
      if (ncol(data.avg) > 1){
      data.dist <- dist(x = t(x = data.avg[features, ]))
      dforder <- hclust(d = data.dist)
      orderVec <- names(dfAvgExpr)[dforder$order]
      } else {
        orderVec <- names(data.avg)
      }
      
      Obio@parameterList[["clusterNameOrder"]] <- orderVec

}

###############################################################################
## Merge into OsC@meta.data                                                  ##

dfAdd <- OsC@meta.data[,c("seurat_clusters", "cellID")]
dfAdd$seurat_clusters <- as.character(dfAdd$seurat_clusters)
dfClusterAnnotation$seurat_clusters <- as.character(dfClusterAnnotation$seurat_clusters)

dfClusterAnnotation$clusterOrder <- NULL

dfAdd <- merge(
    dfAdd,
    dfClusterAnnotation,
    by.x = "seurat_clusters",
    by.y = "seurat_clusters"
)

dfAdd <- data.frame(dfAdd, stringsAsFactors = F)

row.names(dfAdd) <- dfAdd$cellID
dfAdd$cellID <- NULL
dfAdd$seurat_clusters <- NULL

OsC <- addDf2seuratMetaData(
    obj = OsC, 
    dfAdd = dfAdd
)

Idents(OsC) <- "clusterName"
Idents(OsC) <- factor(Idents(OsC), levels = Obio@parameterList[["clusterNameOrder"]])
#OsC@meta.data$seurat_clusters <- factor(OsC@meta.data$seurat_clusters, levels = c(unique(as.numeric(dfClusterAnnotation$seurat_clusters))))

## Done                                                                      ##
###############################################################################

###############################################################################
## Add custom sample annotation if specified                                 ##
FNsample <- paste0(cwd, "/design/customSampleAnnotation.txt")
tableValid <- FALSE

if (file.exists(FNsample)){
    dfSampleAnnotation <- read.delim(
        FNsample, 
        header = T, 
        sep = "\t",
        stringsAsFactors = F
    )
    
    ## Check column names ##
    pos1 <- grep("sampleID", names(dfSampleAnnotation))
    pos2 <- grep("sampleName", names(dfSampleAnnotation))
    pos3 <- grep("sampleColor", names(dfSampleAnnotation))
   
    
    if (length(pos1) != 0 & length(pos2) != 0 & length(pos3) != 0){
        ## Edit sample annotation ##
        dfSampleAnnotation$sampleName <- gsub(" ", "_", dfSampleAnnotation$sampleName)
        dfSampleAnnotation$sampleName <- gsub("\\.", "_", dfSampleAnnotation$sampleName)
        dfSampleAnnotation$sampleName <- gsub("-", "_", dfSampleAnnotation$sampleName)
        dfSampleAnnotation$sampleName <- gsub("__", "_", dfSampleAnnotation$sampleName)
        dfSampleAnnotation$sampleName <- gsub("_$", "", dfSampleAnnotation$sampleName)
        ## Check if clusters match ##
        inClust <- unique(as.vector(dfSampleAnnotation$sampleID))
        oClust <- unique(as.vector(OsC@meta.data$sampleID))
        if (length(inClust) == length(intersect(inClust, oClust))){
            tableValid <- TRUE
        } else {
            tableValid <- FALSE
        }  
    } else {
        tableValid <- FALSE
    }
}

if (!file.exists(FNsample) | !tableValid){
    dfSampleAnnotation <- OsC@meta.data[,c("cellID", "sampleID")]
    
    levels <- sort(unique(dfSampleAnnotation$sampleID))
    
    library(scales)
    sampleCols <- hue_pal()(length(levels))
    
    dfSampleAnnotation <- data.frame(
        sampleID = levels,
        sampleName = levels,
        sampleColor = sampleCols
    )
    
    #row.names(dfSampleAnnotation) <- dfSampleAnnotation$cellID
    #dfClusterAnnotation$cellID <- NULL
    ## Add sample colors ##
    annoDir <- paste0(cwd, "/design")
    
    if (!dir.exists(annoDir)){
        dir.create(annoDir)
    }
    
    FNsample <- paste0(annoDir, "/sampleAnnotation.txt")

    
    write.table(
        dfSampleAnnotation,
        FNsample,
        row.names=F,
        sep = "\t"
    ) 
}


###############################################################################
## Merge into OsC@meta.data                                                  ##

dfAdd <- OsC@meta.data[,c("cellID", "sampleID")]
row.names(dfAdd) <- dfAdd$cellID

dfAdd <- merge(
    dfAdd,
    dfSampleAnnotation,
    by.x = "sampleID",
    by.y = "sampleID"
)

row.names(dfAdd) <- dfAdd$cellID
dfAdd$cellID <- NULL
dfAdd$sampleID <- NULL

OsC <- addDf2seuratMetaData(
    obj = OsC, 
    dfAdd = dfAdd
)


## Done                                                                      ##
###############################################################################


###############################################################################
## Find all markers                                                          ##
DefaultAssay(OsC) <- "RNA"
Idents(OsC) <- "clusterName"

lgFCthreshold <- 0.25

dfGeneralMarkers <- FindAllMarkers(
    object = OsC, 
    only.pos = FALSE, 
    min.pct = 0.1, 
    logfc.threshold = lgFCthreshold,
    test.use = "roc",
    assay =  "RNA",
    slot = "data"
)

if (nrow(dfGeneralMarkers) == 0 | length(unique(dfGeneralMarkers$cluster)) < 2){
    lgFCthreshold <- 0.00
dfGeneralMarkers <- FindAllMarkers(
    object = OsC, 
    only.pos = FALSE, 
    min.pct = 0.01, 
    logfc.threshold = lgFCthreshold,
    test.use = "roc",
    assay =  "RNA",
    slot = "data"
)
}

if (nrow(dfGeneralMarkers) > 0 & length(unique(dfGeneralMarkers$cluster)) >  2){
    dfGeneralMarkers[["direction"]] <- ""
    dfGeneralMarkers[dfGeneralMarkers$avg_diff >= 0, "direction"] <- "positive"
    dfGeneralMarkers[dfGeneralMarkers$avg_diff < 0, "direction"] <- "negative"
    
    Obio@dataTableList[["dfGeneralMarkers"]] <- data.frame(NULL)
    Obio@dataTableList[["dfGeneralMarkers"]] <- dfGeneralMarkers
    
    dfGeneralMarkersFilt <- dfGeneralMarkers[dfGeneralMarkers$avg_diff > lgFCthreshold | dfGeneralMarkers$avg_diff < -lgFCthreshold,]
    
    Obio@dataTableList[["dfGeneralMarkersFilt"]] <- data.frame(NULL)
    Obio@dataTableList[["dfGeneralMarkersFilt"]] <- dfGeneralMarkersFilt
    
    dfGeneralMarkersPos <- dfGeneralMarkers[dfGeneralMarkers$direction == "positive", ]
    dfTop1 <- data.frame(dfGeneralMarkersPos %>% group_by(cluster) %>% top_n(1, avg_diff))
    dfTop5 <- data.frame(dfGeneralMarkersPos %>% group_by(cluster) %>% top_n(5, avg_diff))
    dfTop10 <- data.frame(dfGeneralMarkersPos %>% group_by(cluster) %>% top_n(10, avg_diff))
    dfTop50 <- data.frame(dfGeneralMarkersPos %>% group_by(cluster) %>% top_n(50, avg_diff))
    
    Obio@dataTableList[["dfGeneralMarkersTop10"]] <- dfTop10
    
    Obio@dataTableList$referenceList[["Top10clusterMarkers"]] <- as.vector(
        unique(
            dfTop10$gene
        )
    )
    
###############################################################################
## Upload general markers                                                    ##
library(tidyverse)

dfDat <- dfGeneralMarkers
dfDat <- unique(dfDat[,c("gene", "cluster")])


if (Obio@parameterList$geneIDcolumn != "hgnc_symbol" & Obio@parameterList$geneIDcolumn != "mgi_symbol"){
    refGeneIDcolumn <- "hgnc_symbol"
    dfAnno <- Obio@dfGeneAnnotation
    dfAnno <- unique(dfAnno[,c("hgnc_symbol",Obio@parameterList$geneIDcolumn )])
    dfAnno <- dfAnno[dfAnno[,Obio@parameterList$geneIDcolumn] %in% dfDat[,"gene"],]
    
    dfDat <- merge(
        dfDat,
        dfAnno,
        by.x = "gene",
        by.y = Obio@parameterList$geneIDcolumn
    )
    dfDat$gene <- NULL
    names(dfDat) <- gsub("hgnc_symbol", "gene",names(dfDat))
    
} else {
    refGeneIDcolumn <- Obio@parameterList$geneIDcolumn
}


if (ncol(dfDat) > 1){
  library(dplyr)
  dfDat <- dfDat %>%
         group_by(cluster) %>% 
         mutate(rn = row_number()) %>%
         ungroup %>%
         pivot_wider(names_from = cluster, values_from = gene, values_fill = "") %>% dplyr::select(-rn)
  
  orderVec <- sort(names(dfDat))
  dfDat <- data.frame(dfDat[,orderVec])
  
  names(dfDat) <- paste0(
      Obio@parameterList$project_id, 
      "_Marker_Genes_Cluster_",
      names(dfDat)
  )
  
  dfDat <- data.frame(dfDat)
  
  ## Insert description row ##
  descriptionRow <- data.frame(dfDat[1,])
  descriptionRow[1,] <- t(names(dfDat))
  descriptionRow[1,] <- paste0(descriptionRow[1,], " from Seurat FindAllMarkers.")
  
  dfDat <- rbind(
    descriptionRow, 
    dfDat
  )
  # dfCatRef <- names(dfCatRef)
  # names(dfCatRef) <- names(dfDat)
  # 
  # dfDat <- rbind(
  #   dfCatRef, 
  #   dfDat
  # )
  
  #######################################################################
  ## Upload/update category by category                                ##
  updatedCatIDs <- as.vector(NULL, mode = "character")
  updatedCatNames <- as.vector(NULL, mode = "character")
          
  for (i in 1:ncol(dfDat)){
      cat.name <- names(dfDat)[i]
      cat_type <- paste0("temp_cluster_marker_", Obio@parameterList$project_id)
              
      cat.description.text <- as.vector(dfDat[1,i])
              
      gene.vec <- as.vector(
          dfDat[,i]
      )[2:nrow(dfDat)]
              
      gene.vec <- gene.vec[gene.vec != ""]
      gene.vec <- sort(na.omit(gene.vec))
              
      ## Determine if cat exists ##
              
              
      catID <- add.category.to.lab.reference.table.hs(
          host = Obio@dbDetailList$host,
          pwd = db.pwd,
          user = Obio@dbDetailList$db.user,
          cat.ref.db = Obio@dbDetailList$ref.cat.db,
          cat.ref.db.table = Obio@parameterList$lab.categories.table,
          gene.vector = gene.vec,
          gene.id = refGeneIDcolumn, #options hgnc_symbol, mgi_symbol
          mm.hs.conversion.file =  paste0(cwd, "/assets/annotation/homologene.data.txt"),
          cat_name = cat.name,
          cat_type = cat_type,
          data_source = paste0(Obio@parameterList$labname, " Lab"),
          comments_1 = "",
          comments_2 = "",
          new.lab.category.table = F,
          cat.description.db  = "internal_categories",
          cat.description.db.table = "category_description",
          cat.description.text = cat.description.text,
          lab.name = Obio@parameterList$labname,
          replaceExistingCatName = T
      ) 
          
              
      updatedCatIDs <- c(
          updatedCatIDs, 
          catID
      )    
      
      updatedCatNames <- c(
        updatedCatNames, 
        cat.name
      )
  } ## End dfDat loop
          
  dfFAMplotIDs <- data.frame(
    cat_id = updatedCatIDs, 
    cat_name = updatedCatNames,
    stringsAsFactors = F
  )    
}
        
## Done uploading general markers                                            ##
###############################################################################

} else {
     Obio@dataTableList[["dfGeneralMarkers"]] <- NULL
}

#############################################################

```


If you wish to get a bit of background on tSNE dimensionality reduction, take a look at 
<a href="https://www.youtube.com/watch?v=NEaUSP4YerM" target="_blank"> this youtube video</a> by Josh Starmer from the University of North Carolina.

If you wish to get a bit of background on UMAP (and other) dimensionality reduction algorithms, take a look at 
<a href="https://www.youtube.com/watch?v=9iol3Lk6kyU" target="_blank"> this youtube video</a> by
recaping a lecture at the PyData 2018 conference.   
```{r data_prep_sample_UMAP_rendering, echo=TRUE, eval=TRUE, warning=FALSE, results=FALSE} 

reductionVec <- c("umap", "tsne")

plotList <- list()
chnkVec <- as.vector(NULL, mode = "character")


###############################################################################
## First UMAP all samples together                                           ##
tag <- paste0("UMAP_sample_level")

dfPlot <- OsC@meta.data
pos <- grep("included", names(dfPlot))
if (length(pos) == 0){
  dfPlot[["included"]] <- "+"
}

pos <- grep("cellID", names(dfPlot))
if (length(pos) == 0){
  dfPlot[["cellID"]] <- row.names(dfPlot)
}

dfPlot$UMAP_1 <- NULL
dfPlot$UMAP_2 <- NULL
            
## Get UMAP coordinates ##
coord <- data.frame(OsC@reductions$umap@cell.embeddings)
coord[["cellID"]] <- row.names(coord)
coord <-coord[coord$cellID %in% dfPlot$cellID, ]
            
dfPlot <- merge(dfPlot, coord, by.x = "cellID", by.y="cellID", all=T)
dfPlot[is.na(dfPlot)] <- 0
dfPlot <- dfPlot[dfPlot$UMAP_1 != 0 & dfPlot$UMAP_2 != 0,]
            
            
## Add cluster colors ##
dfPlot[["Cluster"]] <- dfPlot$sampleName
clusterVec <- as.vector(sort(unique(dfPlot$sampleName)))

maxX <- 1.1*max(dfPlot$UMAP_1, na.rm = T)
minX <- 1.1*min(dfPlot$UMAP_1, na.rm = T)
maxY <- 1.1*max(dfPlot$UMAP_2, na.rm = T)
minY <- 1.1*min(dfPlot$UMAP_2, na.rm = T)            

dfPair <- unique(OsC@meta.data[,c("sampleName","sampleID", "sampleColor")])
row.names(dfPair) <- dfPair$sampleID

#colVec <- dfPair$sampleColor
#names(colVec) <- dfPair$sampleName

dfPlot$Cluster <- factor(dfPlot$Cluster, levels = dfPair$sampleName)

# dotsize  = 1
# if (nrow(dfPlot) > 10000){
#   dotsize  = 0.75
# } else if (nrow(dfPlot) > 20000){
#   dotsize = 0.5
# } else if (nrow(dfPlot) > 50000){
#   dotsize = 0.25
# }

plotList[[tag]] <- ggplot(
    data=dfPlot[dfPlot$included == "+",], 
    aes(UMAP_1, UMAP_2, color=sampleName)
  ) + geom_point( shape=16, size = as.numeric(dotsize)
  ) + xlab("UMAP1") + ylab("UMAP2"
  ) + theme_bw(
  )  +  theme(
      axis.text.y   = element_text(size=8),
      axis.text.x   = element_text(size=8),
      axis.title.y  = element_text(size=8),
      axis.title.x  = element_text(size=8),
      axis.line = element_line(colour = "black"),
      panel.border = element_rect(colour = "black", fill=NA, size=1),
      plot.title = element_text(hjust = 0.5, size = 12),
      legend.title = element_blank()
  ) + guides(col = guide_legend(override.aes = list(shape = 16, size = legendDotSize))
  ) + ggtitle(paste0("Sample: ", gsub("_", " ", tag))
  ) + xlim(minX, maxX) + ylim(minY, maxY
  ) + coord_fixed(ratio=1
  )  


h <- sum(c("sampleName", "sampleColor") %in% names(dfPlot))
if (h ==2){
  dfCol <- unique(dfPlot[,c("sampleName", "sampleColor")])
  colVec <- as.vector(dfCol$sampleColor)
  names(colVec) <- as.vector(dfCol$sampleName)
  plotList[[tag]] <- plotList[[tag]] + scale_colour_manual("Samples" ,values = colVec
      ) + guides(col = guide_legend(override.aes = list(shape = 16, size = legendDotSize))
  )
}
## Add colors if specified ##

            
if (length(unique(dfPlot$Cluster)) > 15){
   plotList[[tag]] <- plotList[[tag]] + theme(legend.position = "none")
}
            FNbase <- paste0(tag, VersionPdfExt)
            FN <- paste0(Obio@parameterList$reportFigDir, FNbase)
            FNrel <- paste0("report_figures/", FNbase)
            
            pdf(FN)
                print(plotList[[tag]])
            dev.off()
            
            link <- paste0('<a href="https://',urlString,'/',Obio@parameterList$project_id,'/pca?x_axis=UMAP_1&y_axis=UMAP_2" target="_blank">here</a>')  
            
            figLegend <- paste0(
                '**Figure ', 
                figureCount, 
                ':** ',
                ' UMAP showing all cells from all samples together. Download a pdf of this figure <a href="',FNrel,'" target="_blank">here</a>.',
                'An interactive version of this figure can be found ', link, '. '
            )
            
            figureCount <- figureCount + 1
            
            NewChnk <- paste0(
                "#### ", tag,
                "\n```{r Sample_UMAP_",
                tag,", results='asis', echo=F, eval=TRUE, warning=FALSE, fig.cap='",
                figLegend,"'}\n",
                "\n",
                "\n print(plotList[['",tag,"']])",
                "\n cat(  '\n')",
                "\n\n\n```\n"   
            )
            
            chnkVec <- c(
                chnkVec,
                NewChnk
            )


## Done first umap all samples                                               ##
###############################################################################
            
###############################################################################
## First tsne all samples together                                           ##
tag <- paste0("tSNE_All_Samples")
dfPlot <- OsC@meta.data
pos <- grep("included", names(dfPlot))
if (length(pos) == 0){
  dfPlot[["included"]] <- "+"
}

pos <- grep("cellID", names(dfPlot))
if (length(pos) == 0){
  dfPlot[["cellID"]] <- row.names(dfPlot)
}



dfPlot$tSNE_1 <- NULL
dfPlot$tSNE_2 <- NULL
            
## Get tsNE coordinates ##
coord <- data.frame(OsC@reductions$tsne@cell.embeddings)
coord[["cellID"]] <- row.names(coord)
coord <-coord[coord$cellID %in% dfPlot$cellID, ]
            
dfPlot <- merge(dfPlot, coord, by.x = "cellID", by.y="cellID", all=T)
dfPlot[is.na(dfPlot)] <- 0
dfPlot <- dfPlot[dfPlot$tSNE_1 != 0 & dfPlot$tSNE_2 != 0,]
            
            
## Add cluster colors ##
dfPlot[["Cluster"]] <- dfPlot$sampleName
clusterVec <- as.vector(unique(sort(dfPlot$sampleName)))

maxX <- 1.1*max(dfPlot$tSNE_1, na.rm = T)
minX <- 1.1*min(dfPlot$tSNE_1, na.rm = T)
maxY <- 1.1*max(dfPlot$tSNE_2, na.rm = T)
minY <- 1.1*min(dfPlot$tSNE_2, na.rm = T)            

# library(scales)
# clusterCols = hue_pal()(length(clusterVec))
# dfPlot$Cluster <- factor(dfPlot$Cluster, levels = clusterVec)

# dotsize  = 1.5
# if (nrow(dfPlot) > 10000){
#   dotsize  = 0.75
# } else if (nrow(dfPlot) > 50000){
#   dotsize = 0.5
# } else {
#   dotsize = 0.25
# }

plotList[[tag]] <- ggplot(data=dfPlot[dfPlot$included == "+",], aes(tSNE_1, tSNE_2, color=sampleName)
            ) + geom_point( shape=16, size = as.numeric(dotsize)
            ) + xlab("tSNE1") + ylab("tSNE2"
            ) + theme_bw(
            )  +  theme(
                axis.text.y   = element_text(size=8),
                axis.text.x   = element_text(size=8),
                axis.title.y  = element_text(size=8),
                axis.title.x  = element_text(size=8),
                axis.line = element_line(colour = "black"),
                panel.border = element_rect(colour = "black", fill=NA, size=1),
                plot.title = element_text(hjust = 0.5, size = 12),
                legend.title = element_blank()
            ) + ggtitle(paste0("Sample: ", tag)
            ) + guides(col = guide_legend(override.aes = list(shape = 16, size = legendDotSize))
            ) + xlim(minX, maxX) + ylim(minY, maxY
            ) + coord_fixed(ratio=1
            ) 

h <- sum(c("sampleName", "sampleColor") %in% names(dfPlot))
if (h ==2){
  dfCol <- unique(dfPlot[,c("sampleName", "sampleColor")])
  colVec <- as.vector(dfCol$sampleColor)
  names(colVec) <- as.vector(dfCol$sampleName)
  plotList[[tag]] <- plotList[[tag]] + scale_colour_manual("Samples" ,values = colVec
      ) + guides(col = guide_legend(override.aes = list(shape = 16, size = legendDotSize))
  )
}
            
if (length(unique(dfPlot$Cluster)) > 15){
   plotList[[tag]] <- plotList[[tag]] + theme(legend.position = "none")
}
            FNbase <- paste0(tag, VersionPdfExt)
            FN <- paste0(Obio@parameterList$reportFigDir, FNbase)
            FNrel <- paste0("report_figures/", FNbase)
            
            pdf(FN)
                print(plotList[[tag]])
            dev.off()
            
            link <- paste0('<a href="https://',urlString,'/',Obio@parameterList$project_id,'/pca?x_axis=tSNE_1&y_axis=tSNE_2" target="_blank">here</a>')  
            
            figLegend <- paste0(
                '**Figure ', 
                figureCount, 
                ':** ',
                ' tSNE showing all cells from all samples together. Download a pdf of this figure <a href="',FNrel,'" target="_blank">here</a>.',
                'An interactive version of this figure can be found ', link, '. '
            )
            
            figureCount <- figureCount + 1
            
            NewChnk <- paste0(
                "#### ", tag,
                "\n```{r Sample_tSNE_",
                tag,", results='asis', echo=F, eval=TRUE, warning=FALSE, fig.cap='",
                figLegend,"'}\n",
                "\n",
                "\n print(plotList[['",tag,"']])",
                "\n cat(  '\n')",
                "\n\n\n```\n"   
            )
            
            chnkVec <- c(
                chnkVec,
                NewChnk
            )


## Done first tsne all samples                                               ##
###############################################################################            
###############################################################################
## Make one UMAP plot per sample                                             ##

sampleVec <- sort(unique(OsC@meta.data$sampleName))

dfPlot <- OsC@meta.data
pos <- grep("included", names(dfPlot))
if (length(pos) == 0){
  dfPlot[["included"]] <- "+"
}

pos <- grep("cellID", names(dfPlot))
if (length(pos) == 0){
  dfPlot[["cellID"]] <- row.names(dfPlot)
}

## Get UMAP coordinates ##
coord <- data.frame(OsC@reductions$umap@cell.embeddings)
coord[["cellID"]] <- row.names(coord)
coord <-coord[coord$cellID %in% dfPlot$cellID, ]
dfPlot$UMAP_1 <- NULL
dfPlot$UMAP_2 <- NULL
            
dfPlot <- merge(dfPlot, coord, by.x = "cellID", by.y="cellID", all=T)
dfPlot[is.na(dfPlot)] <- 0
dfPlot <- dfPlot[dfPlot$UMAP_1 != 0 & dfPlot$UMAP_2 != 0,]
            
            
## Add cluster colors ##
dfPlot[["Cluster"]] <- dfPlot$sampleID
clusterVec <- as.vector(unique(sort(dfPlot$sampleName)))
            
# library(scales)
# clusterCols = hue_pal()(length(clusterVec))
# 
# dfPlot$Cluster <- factor(dfPlot$Cluster, levels = clusterVec)            
            
maxX <- 1.1*max(dfPlot$UMAP_1, na.rm = T)
minX <- 1.1*min(dfPlot$UMAP_1, na.rm = T)
maxY <- 1.1*max(dfPlot$UMAP_2, na.rm = T)
minY <- 1.1*min(dfPlot$UMAP_2, na.rm = T)               
                                   
for (i in 1:length(sampleVec)){
    tag <- paste0("UMAP_plot_by_", sampleVec[i])
    
    dfPlotSel <- dfPlot[dfPlot$sampleName == sampleVec[i], ]
    dfPlotSel$sampleName       
            
            
    plotList[[tag]] <- ggplot(data=dfPlotSel[dfPlotSel$included == "+",], aes(UMAP_1, UMAP_2, color=sampleName)
            ) + geom_point( shape=16, size = as.numeric(dotsize)
            ) + xlab("UMAP1") + ylab("UMAP2"
            ) + theme_bw(
            )  +  theme(
                axis.text.y   = element_text(size=8),
                axis.text.x   = element_text(size=8),
                axis.title.y  = element_text(size=8),
                axis.title.x  = element_text(size=8),
                axis.line = element_line(colour = "black"),
                panel.border = element_rect(colour = "black", fill=NA, size=1),
                plot.title = element_text(hjust = 0.5, size = 12),
                legend.title = element_blank()
            ) + guides(col = guide_legend(override.aes = list(shape = 16, size = legendDotSize))    
            ) + ggtitle(paste0("Sample: ", gsub("_", " ", tag))
            ) + xlim(minX, maxX) + ylim(minY, maxY
            ) + coord_fixed(ratio=1)
            #) + scale_color_manual(values = clusterCols[i]
             
    
            h <- sum(c("sampleName", "sampleColor") %in% names(dfPlotSel))
            if (h ==2){
              dfCol <- unique(dfPlotSel[,c("sampleName", "sampleColor")])
              colVec <- as.vector(dfCol$sampleColor)
              names(colVec) <- as.vector(dfCol$sampleName)
              plotList[[tag]] <- plotList[[tag]] + scale_colour_manual("Samples" ,values = colVec
                  ) + guides(col = guide_legend(override.aes = list(shape = 16, size = legendDotSize))
              )
            }    
    
    if (length(unique(dfPlot$Cluster)) > 15){
   plotList[[tag]] <- plotList[[tag]] + theme(legend.position = "none")
}
            
            FNbase <- paste0(tag, VersionPdfExt)
            FN <- paste0(Obio@parameterList$reportFigDir, FNbase)
            FNrel <- paste0("report_figures/", FNbase)
            
            pdf(FN)
                print(plotList[[tag]])
            dev.off()
            
            figLegend <- paste0(
                '**Figure ', 
                figureCount, 
                ':** ',
                ' Sample-level UMAPs. Download a pdf of this figure <a href="',FNrel,'" target="_blank">here</a>.'
            )
            
            figureCount <- figureCount + 1
            
            NewChnk <- paste0(
                paste("#### ", tag),
                "\n```{r Sample_UMAP_",
                tag,", results='asis', echo=F, eval=TRUE, warning=FALSE, fig.cap='",
                figLegend,"'}\n",
                "\n",
                "\n print(plotList[['",tag,"']])",
                "\n cat(  '\n')",
                "\n\n\n```\n"   
            )
            
            chnkVec <- c(
                chnkVec,
                NewChnk
            )
            
            
    
    
    
    
}

## Done making one umap plot per sample                                      ##
###############################################################################


###############################################################################
## Add cluster dendrogram by sample                                          ##

if (length(unique(OsC@meta.data$sampleID)) > 2){
  library(ggtree)
  Idents(OsC) <- "sampleName"
  OsC <- BuildClusterTree(OsC)
      
  tag <- paste0("Sample_Dendrogram")
      
  OsC@tools$BuildClusterTree$tip.label <- paste0( OsC@tools$BuildClusterTree$tip.label)
      
  plotList[[tag]]  <- ggplot(OsC@tools$BuildClusterTree
      ) + geom_tree(
      ) + theme_tree(
      ) 
  
  h <- sum(c("sampleName", "sampleColor") %in% names(OsC@meta.data))
  if (h ==2){
    dfCol <- unique(OsC@meta.data[,c("sampleName", "sampleColor")])
    colVec <- as.vector(dfCol$sampleColor)
    names(colVec) <- as.vector(dfCol$sampleName)
    plotList[[tag]] <- plotList[[tag]] + geom_tiplab(color=colVec
      ) 
  } else {
    plotList[[tag]] <- plotList[[tag]] + geom_tiplab(
      )   
  }
  
  #plotList[[tag]] <- plotList[[tag]] + geom_tippoint(aes(color=sampleName), size=1.5)
  
  plotList[[tag]] <- plotList[[tag]] + labs(title=tag
      ) + theme(
        panel.border = element_rect(colour = "black", fill=NA, size=1),
        axis.title.x=element_blank(),
        plot.title = element_text(hjust = 0.5, size = 12)
      )  + xlim(0,dendrofactor*max(OsC@tools$BuildClusterTree[[2]]))
 
      
  ## Save to file ##
  FNbase <- paste0(tag,".", VersionPdfExt)
  FN <- paste0(Obio@parameterList$reportFigDir, FNbase)
  FNrel <- paste0("report_figures/", FNbase)
      
  pdf(FN)
      print(plotList[[tag]])
  dev.off()
      
  figLegend <- paste0(
      '**Figure ', 
          figureCount, 
          ':** ',
          ' Clusterplot dendrogram by sample ID. ','A pdf of this figure can be downloaded <a href="',FNrel,'" target="_blank">here</a>.'
      )
      
      
      NewChnk <- paste0(
          "#### SampleID Dendrogram",
          "\n```{r ", tag, "results='asis', echo=F, eval=TRUE, warning=FALSE, fig.cap='",
          figLegend,"'}\n",
          "\n",
          "\n print(plotList[['",tag,"']])",
          "\n cat(  '\n')",
          "\n\n\n```\n"   
      )
      
      chnkVec <- c(
          chnkVec,
          NewChnk
      )
      
      
      figureCount <- figureCount + 1
}

## Done by sample                                                            ##
###############################################################################

if (length(plotList) > 2){
    tabVar <- ".tabset .tabset-fade .tabset-dropdown"
} else {
    tabVar <- ".tabset .tabset-fade .tabset-pills"
}

```

### Dimensionality Reduction Plots by Sample {`r tabVar`}

```{r Plot_tsne_data_plotting, echo=TRUE, eval=TRUE, warning=FALSE, results="asis"} 

cat(paste(knit(text = chnkVec, quiet = T), collapse = '\n'))

```
