<!-- Set PArameters Module -->
<!-- Set the chnkPrefix to make all chunks unique in the overall folder -->
```{r partB_N_cell_barchart, echo=TRUE, eval=TRUE, warning=FALSE}
chnkPrefix <- "partB.N.cell.barchart."
VersionPdfExt <- VersionPdfExt <- paste0(".",chnkPrefix,"V", gsub("-", "", Sys.Date()), ".pdf")

```



```{r make_percent_N_cells_barchart, echo=TRUE, eval=TRUE, warning=FALSE, results="asis"}
###############################################################################
## Create datatable for plotting                                             ##


## This plotting procedure requires three sets: the sets cellTypeIDs, clusterIDs, cellTypeIDs
## level1ID, level2ID, level3ID
dfSample <- unique(OsC@meta.data[,c("sampleName", "sampleColor", "sampleID")])
row.names(dfSample) <- dfSample$sampleID
dfSample <- dfSample[names(Obio@sampleDetailList),]

sampleIDs <- dfSample$sampleName
colVec <- dfSample$sampleColor

clusterIDs <- unique(OsC@meta.data[,"sampleName"])

if (length(grep("cellIdent", names(OsC@meta.data))) == 0){
  OsC@meta.data[["cellIdent"]] <- "All"
}

cellTypeIDs <- unique(OsC@meta.data[,"cellIdent"])

dfTemp <- OsC@meta.data

if (length(grep("^cellIdent$", names(dfTemp))) == 0){
  dfTemp[["cellIdent"]] <- "All"
}

#dfTemp <- dfTemp[dfTemp$percent.mt <= max(Obio@parameterList$singleCellSeuratMtCutoff), ]
dfTemp[["cellID"]] <- row.names(dfTemp)
dfTemp <- unique(dfTemp[,c("cellID", "sampleName", "clusterName", "cellIdent")])
names(dfTemp) <- gsub("clusterName", "Cluster", names(dfTemp) )

 dfTemp <- unique(dfTemp[,c("cellID", "sampleName", "Cluster","cellIdent")])
 
dfRes <- dfTemp
dfRes$cellID <- NULL
row.names(dfRes) <- NULL
dfRes <- unique(dfRes)
dfRes[["N_cells"]] <- 0


for (i in 1:nrow(dfRes)){
  dfRes[i, "N_cells"] <- nrow(dfTemp[dfTemp$sampleName == dfRes[i,"sampleName"] & dfTemp$Cluster == dfRes[i,"Cluster"] & dfTemp$cellIdent == dfRes[i,"cellIdent"], ])
}




## Calculate cluster percentages per celltypeID ##
dfRes[["Perc_cells"]] <- 0
for (i in 1:length(cellTypeIDs)){
  dfResTemp2 <- dfRes[dfRes$cellIdent == cellTypeIDs[i], ]
  tempCluster <- as.vector(unique(dfResTemp2$Cluster))
  
  for (j in 1:length(tempCluster)){
    dfResTemp3 <- dfResTemp2[dfResTemp2$Cluster == tempCluster[j],]
    NclusterTotal <- sum(dfResTemp3[, "N_cells"])
    dfResTemp3[,"Perc_cells"] <- round(dfResTemp3[,"N_cells"]/NclusterTotal, 4)*100
    
    
    if (j ==1){
      dfRes3 <- dfResTemp3
    } else {
      dfRes3 <- rbind(dfResTemp3, dfRes3)
    }
  }
  
  if (i ==1){
    dfRes4 <- dfRes3
  } else {
    dfRes4 <- rbind(dfRes3, dfRes4)
  }
  
}
 
dfRes <- dfRes4

plotList <- list()
chnkVec <- as.vector(NULL, mode = "character")

for (i in 1:length(cellTypeIDs)){
  #############################################################################
  ## Create cell number plot                                                 ##
  tag <- paste0(cellTypeIDs[i], "_Number")
  dfResTemp <- dfRes[dfRes$cellIdent == cellTypeIDs[i], ]
  
  ## Set cluster order large to small ##
  library(tidyverse)

  df <- dfResTemp[,c("Cluster", "N_cells")]
  
  df <- df %>% 
    group_by(Cluster) %>% 
    summarise(N_cells = sum(N_cells)) %>% arrange(desc(N_cells))
  
  levels <- df$Cluster
  dfResTemp$Cluster <- factor(dfResTemp$Cluster, levels = levels)
  
  ## Order ##
   
   plotList[[tag]] <- ggplot(
    ) + geom_bar(aes(y = N_cells, x = Cluster, fill = sampleName), data = dfResTemp, stat="identity"
    ) + labs(title="Cell Numbers Per Cluster", x="", y = "Cell Count"
    ) + theme_bw(
    ) +  theme(
      panel.border = element_rect(colour = "black", fill=NA, size=1),
      plot.title = element_text(hjust = 0.5, size = 12)
    ) + coord_flip() + guides(fill=guide_legend(title="Samples"))
  
  h <- sum(c("sampleName", "sampleColor") %in% names(OsC@meta.data))
  if (h ==2){
      dfCol <- unique(OsC@meta.data[,c("sampleName", "sampleColor")])
      dfCol <- dfCol[dfCol$sampleName %in% unique(dfResTemp$sampleName), ]
      colVec <- as.vector(dfCol$sampleColor)
      names(colVec) <- as.vector(dfCol$sampleName)
      plotList[[tag]] <- plotList[[tag]] + scale_fill_manual("Samples" ,values = colVec
      ) 
  }
  
  ## Calculate percentages for this subset ##
  
 
  
  ###########################################################################
  ## Save plot to file                                                     ##
  FNbase <- paste0(tag,".Ncells", VersionPdfExt)
  FN <- paste0(Obio@parameterList$reportFigDir, FNbase)
  FNrel <- paste0("report_figures/", FNbase)
    
  pdf(FN)
      print(plotList[[tag]])
  dev.off()
  ##                                                                       ##
  ###########################################################################
    
  ###########################################################################
  ## Add to chunk                                                          ##
  figCap <- paste0(
      '**Figure ',
      figureCount,
      'A:** Cell Count in each cluster for ', 
      tag,
      'Download a pdf of this figure <a href="',FNrel,'" target="_blank">here</a>. '
  )
  
  NewChnk <- paste0(
    paste0("#### Barchart_ ", tag),
        "\n```{r Barchart-",tag,", results='asis', echo=F, eval=TRUE, warning=FALSE, fig.cap='",figCap,"'}\n",
        "\n",
        "\n print(plotList[['",tag,"']])",
        "\n cat(  '\n')",
        "\n\n\n```\n"   
  )
    
  chnkVec <- c(
      chnkVec,
      NewChnk
  )
  ## Done adding                                                             ##
  #############################################################################
  
  #############################################################################
  ## Add percentage plot                                                     ##
  tag <- paste0(cellTypeIDs[i], "_Percent")
  plotList[[tag]] <- ggplot(
    ) + geom_bar(aes(x = Cluster, y = Perc_cells, fill = sampleName), data = dfResTemp, stat="identity"
    ) + labs(title="Percent Cells Per Cluster", x="", y = "Percent Cells"
    ) + theme_bw(
    ) +  theme(
      panel.border = element_rect(colour = "black", fill=NA, size=1),
      plot.title = element_text(hjust = 0.5, size = 12)
    ) +  coord_flip() 
  
   h <- sum(c("sampleName", "sampleColor") %in% names(OsC@meta.data))
  if (h ==2){
      dfCol <- unique(OsC@meta.data[,c("sampleName", "sampleColor")])
      dfCol <- dfCol[dfCol$sampleName %in% unique(dfResTemp$sampleName), ]
      colVec <- as.vector(dfCol$sampleColor)
      names(colVec) <- as.vector(dfCol$sampleName)
      plotList[[tag]] <- plotList[[tag]] + scale_fill_manual("Samples" ,values = colVec
      ) 
  }
  
  ###########################################################################
  ## Save plot to file                                                     ##
  FNbase <- paste0(tag, ".percent.cells",VersionPdfExt)
  FN <- paste0(Obio@parameterList$reportFigDir, FNbase)
  FNrel <- paste0("report_figures/", FNbase)
    
  pdf(FN)
      print(plotList[[tag]])
  dev.off()
  ##                                                                       ##
  ###########################################################################
    
  ###########################################################################
  ## Add to chunk                                                          ##
  figCap <- paste0(
      '**Figure ',
      figureCount,
      'B:** Cell percentages in each cluster for ', 
      tag,
      'Download a pdf of this figure <a href="',FNrel,'" target="_blank">here</a>. '
  )
  
  NewChnk <- paste0(
    paste0("#### Barchart_ ", tag),
        "\n```{r Barchart-percent_",tag,", results='asis', echo=F, eval=TRUE, warning=FALSE, fig.cap='",figCap,"'}\n",
        "\n",
        "\n print(plotList[['",tag,"']])",
        "\n cat(  '\n')",
        "\n\n\n```\n"   
  )
    
  chnkVec <- c(
      chnkVec,
      NewChnk
  )
  ## Done adding percentage plot                                             ##
  #############################################################################
  
  
  figureCount <- figureCount + 1
  
  #############################################################################
  ## Order Percent Cells by Similarity
  if (!is.null(Obio@parameterList$clusterNameOrder)){
        #############################################################################
        ## Add percentage plot                                                     ##
        if (sum(unique(dfResTemp$Cluster) %in% Obio@parameterList$clusterNameOrder) == length(Obio@parameterList$clusterNameOrder)){
            dfResTemp$Cluster <- factor(dfResTemp$Cluster, levels = Obio@parameterList$clusterNameOrder)
        }
        
        
        
        tag <- paste0(cellTypeIDs[i], "_Percent_clustered")
        plotList[[tag]] <- ggplot(
          ) + geom_bar(aes(x = Cluster, y = Perc_cells, fill = sampleName), data = dfResTemp, stat="identity"
          ) + labs(title="Percent Cells Per Cluster Clustered", x="", y = "Percent Cells"
          ) + theme_bw(
          ) +  theme(
            panel.border = element_rect(colour = "black", fill=NA, size=1),
            plot.title = element_text(hjust = 0.5, size = 12)
          ) +  coord_flip() 
        
         h <- sum(c("sampleName", "sampleColor") %in% names(OsC@meta.data))
        if (h ==2){
            dfCol <- unique(OsC@meta.data[,c("sampleName", "sampleColor")])
            dfCol <- dfCol[dfCol$sampleName %in% unique(dfResTemp$sampleName), ]
            colVec <- as.vector(dfCol$sampleColor)
            names(colVec) <- as.vector(dfCol$sampleName)
            plotList[[tag]] <- plotList[[tag]] + scale_fill_manual("Samples" ,values = colVec
            ) 
        }
        
        ###########################################################################
        ## Save plot to file                                                     ##
        FNbase <- paste0(tag, ".percent.cells.clustered",VersionPdfExt)
        FN <- paste0(Obio@parameterList$reportFigDir, FNbase)
        FNrel <- paste0("report_figures/", FNbase)
          
        pdf(FN)
            print(plotList[[tag]])
        dev.off()
        ##                                                                       ##
        ###########################################################################
          
        ###########################################################################
        ## Add to chunk                                                          ##
        figCap <- paste0(
            '**Figure ',
            figureCount,
            'C:** Cell percentages in each cluster for ', 
            tag,'. Clustered by cluster similarity.',
            'Download a pdf of this figure <a href="',FNrel,'" target="_blank">here</a>. '
        )
        
        NewChnk <- paste0(
          paste0("#### Barchart_ ", tag),
              "\n```{r Barchart-percent_",tag,", results='asis', echo=F, eval=TRUE, warning=FALSE, fig.cap='",figCap,"'}\n",
              "\n",
              "\n print(plotList[['",tag,"']])",
              "\n cat(  '\n')",
              "\n\n\n```\n"   
        )
          
        chnkVec <- c(
            chnkVec,
            NewChnk
        )
        ## Done adding percentage plot                                             ##
        #############################################################################
        
        
        figureCount <- figureCount + 1
      
  }
  
  
  ##
  #############################################################################
  
}

## Done creating data table                                                  ##
###############################################################################

if (length(plotList) > 3){
    tabVar <- ".tabset .tabset-fade .tabset-dropdown"
} else {
    tabVar <- ".tabset .tabset-fade .tabset-pills"
}

```

### Barchart N cells and Percent in Clusters {`r tabVar`}
if you could prepare a bar-shape graph with the %of cells clusters representing our populations (like in the Nat Med)

```{r plot_barchart, echo=TRUE, eval=TRUE, warning=FALSE, results="asis"}
cat(paste(knit(text = chnkVec, quiet = T), collapse = '\n'))
```
